### 2015-10-20 which_law_2_use.tex
Added discussion and conclusions. Changed a line in the introduction.

% mn2esample.tex
%
% v2.1 released 22nd May 2002 (G. Hutton)
%
% The mnsample.tex file has been amended to highlight
% the proper use of LaTeX2e code with the class file
% and using natbib cross-referencing. These changes
% do not reflect the original paper by A. V. Raveendran.
%
% Previous versions of this sample document were
% compatible with the LaTeX 2.09 style file mn.sty
% v1.2 released 5th September 1994 (M. Reed)
% v1.1 released 18th July 1994
% v1.0 released 28th January 1994

% \documentclass[useAMS,usenatbib,usegraphicx]{mn2e}

\documentclass[a4paper,12pt,useAMS,usenatbib,revtex4]{mn2e}
% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
\usepackage{lineno}
% \linenumbers
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{amssymb}
\usepackage{tabularx, blindtext}
\usepackage{lscape}
\usepackage{url}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[Choosing the right law for minimum bias retrieval of transit parameters from transit lightcurves]
{Limb-darkening and exoplanets II: choosing the right law for minimum bias retrieval of transit parameters from transit lightcurves}
\author[Espinoza \& Jord\'an ]{
N\'estor Espinoza$^{1,2}$\thanks{E-mail:nespino@astro.puc.cl}, 
Andr\'es Jord\'an$^{2,1}$\thanks{E-mail: ajordan@astro.puc.cl}\\ 
$^{1}$Millennium Institute of Astrophysics, Vicu\~na Mackenna 4860, Santiago, Chile\\
$^{2}$Instituto de Astrof\'isica, Pontificia Universidad Cat\'olica de Chile, Vicu\~na Mackenna 
4860, Santiago, Chile}
\begin{document}

\date{}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2015}

\maketitle

\label{firstpage}

\begin{abstract}
It has recently been demonstrated that the parametrization of the limb-darkening effect on a star has a direct impact 
on the parameters retrieved from transit lightcurves such as the exoplanet's radius, scaled semi-major axis and inclination. However, 
studies regarding this issue have only focused on the widely used quadratic limb-darkening law, leaving outside of the analysis 
other proposed laws that in fact are better descriptors of model intensity profiles. In this work, we show that in fact 
laws such as the logarithmic, square-root and three-parameter do a better job at retrieving the mentioned parameters from transit 
lightcurves than the widely used quadratic law and, as such, we recommend using those instead. We also detail when to use each of those, 
which we note has a dependence on both stellar and transit parameters. In addition, we demonstrate that the exponential law should not be 
used as it fundamentally non-physical, typically producing a divergence towards negative intensities at the limb.
\end{abstract}

\begin{keywords}
stellar astrophysics -- limb darkening -- exoplanets: transits.
\end{keywords}

% #################################################################################################################################
% #################################################################################################################################
% #################################################################################################################################
% ############################################# SECTION 1 #########################################################################
% #################################################################################################################################
% #################################################################################################################################
% #################################################################################################################################

\section{Introduction}
In the past decade, the study of transiting exoplanets has been evolving from discovery to very precise characterization of these systems, 
thanks to the exquisit precision allowed mainly by space-based observatories such as the Hubble Space Telescope (HST) and the Kepler mission. 
This in turn has allowed the exoplanet community to study precise mass-radius diagrams \citep[see, e.g.,][and references therein]{wm2014}, and in turn raise 
questions about the possibility of not only obtaining a precise determination of the internal composition of small, rocky exoplanets based on mass-radius
measurements \citep{dorn2015} or of their atmospheric fractions from radius measurements alone \citep{WL2015}, but also has allowed for the determination of
derived parameters of the systems that even allow for the obtention of stellar parameters directly from transit lightcurves through techniques such as asterodensity
profiling \citep{sm2003,kipping2014AP}, or of the detection of atmospheric features in exoplanet atmospheres through the technique of transmission spectroscopy. 
All these studies and techniques rely on the retrieval of precise and accurate transit parameters from transit lightcurves.

In a recent study \citep[][hereafter referred as EJ15]{ej2015}, we showed that the accuracy is actually catching up with the precision 
of these measurements due to our poor understanding of the limb-darkening effect. In particular, we showed that there are important 
biases both when fixing and fitting the limb-darkening coefficients in the light curve fitting process, with the latter arising from the fact 
that the popular and widely used quadratic law is unable to model the complex intensity profile of real stars and the former arising for this 
same reason plus the fact that different methods of fitting the model intensity profiles give rise to different limb-darkening coefficients and 
from the fact that we have an imperfect knowledge of the real intensity profiles of stars. This showed that fixing the limb-darkening coefficients is 
actually the worst option if one is willing to obtain precise \textit{and} accurate transit parameters, because the biases arise from three different sources, 
with the last one (the fact that we do not have a perfect modelling of the stellar intensity profiles of real stars) having an unknown but possibly 
large impact on them.

Given the above, unless the data quality is really poor (and one is willing to sacrifice bias over variance), there is actually no good reason why one would 
actually want to fix the limb-darkening coefficients in the transit fitting process (assuming computational resources are not an issue). However, although fitting the 
limb-darkening coefficients seems to be a good solution to the accuracy problem, this still has the issue of the low flexibility of the quadratic limb-darkening 
law which still causes important biases on the retrieved transit parameters according to EJ15, which can be a large as $\sim 1\%$ for the planet-to-star 
radius ratio $R_p/R_*$, $\sim 2\%$ for the scaled semi-major axis, $a/R_*$, and $2\%$ for the inclination, where $R_p$ is the planetary radius, $R_*$ 
the stellar radius and $a$ the semi-major axis. The importance for missions like Kepler and for future missions like the Transiting Exoplanet Survey 
Satellite \cite[TESS,][]{ricker2014} is evident when looking at the most recent results from the Kepler mission: if we focus on the planet-to-star radius ratio 
alone, which according to EJ15 has an accuracy bias on the order of $\sim 0.2\%$, a query to the Nasa Exoplanet Archive\footnote{\url{http://exoplanetarchive.ipac.caltech.edu/}; query done on 29/09/2015.} shows that out of 3063 planetary candidates, 933 ($26\%$) have precisions better than 
$0.2\%$, and out of 1001 Kepler confirmed exoplanets, 463 (46\%) do too. This means that at least\footnote{It is important to note that this is an 
underestimate of the number of planet candidates with estimation errors, due to the fact that the Kepler pipeline makes use of fixed limb-darkening 
coefficients using the quadratic law \citep{rowe2015}, which as explained here and estimated in EJ15, gives rise to more severe biases than the one used for this 
estimation} $26\%$ of the planet candidates (from which, e.g., population studies, which rely on averaging out \textit{random} and not \textit{systematic} 
uncertainties like the ones introduced by limb-darkening) and almost half of the confirmed exoplanets (from which, e.g., characterization studies are 
based on) have important systematic errors.

An obvious solution to the above mentioned problem if one decides to fit the limb-darkening coefficients is to try to use \textit{other} laws to describe 
the intensity profile of stars. Although the non-linear law proposed by \cite{claret2000} seems to be the most flexible, the fact that it has four free parameters 
does not make it a very attractive choice in this scheme if one is willing to replace the quadratic law. However, laws with fewer parameters have been proposed, 
with the two-parameter laws being the exponential proposed by \cite{claret2003}, the logarithmic proposed by \cite{klinglesmith1970} and the square-root proposed 
by \cite{diazgimenez1992}. In addition, a very flexible three-parameter law was also proposed by \cite{sing2009}. These lower parameter laws seem to be 
very attractive for transit fitting purposes, due to their flexibility at following different intensity profiles \citep[see, e.g., ][for a comparison between the goodness of 
fit to ATLAS model atmospheres of the mentioned two-parameter laws which outperform the linear and quadratic laws in terms of following the intensity 
profiles]{howarth2011} and their low number of parameters.

Despite the attractive nature of the mentioned limb-darkening laws, testing their performance at retrieving transit parameters from transit 
lightcurves was a problem until recently for two reasons. First, there was no published algorithm that 
was capable of efficiently generating fast and accurate transit lightcurves using all of these non-standard laws. However, recently \cite{batman2015} published an 
algorithm that does exactly this called \texttt{batman}, enabling one then to generate transit lightcurves very efficiently with any arbitrary limb-darkening law. 
The second problem was that it was not clear how to sample limb-darkening coefficients in an informative (i.e., sampling all the physically possible parameter 
space) and efficient way for all of these laws. \cite{kipping2015} recently derived an algorithm to sample parameters from the three-parameter law by imposing physically plausible constrains on the intensity profiles which derived in constrains on the limb-darkening coefficients being fitted, while \cite{kipping2013}, using the same principle, derived an algorithmic way of 
doing this for two-parameter laws. However, he found that his algorithm was not applicable to the exponential law and thus no constrains for this law could 
be derived. In addition to this, the form of the logarithmic law used in \cite{kipping2013} differs from the standard one proposed by \cite{klinglesmith1970}, 
which is actually the one used in \texttt{batman}. Thus, in order to sample coefficients from this limb-darkening law, one first has to derive an efficient 
informative sampling scheme for this standard form of the law.

In this work, we aim at testing how well do these non-standard laws perform at retrieving transit parameters from transit lightcurves, and compare them to 
the retrievals done by the standard quadratic limb-darkening law. For this, we first follow \cite{kipping2013} in order to derive an efficient sampling scheme 
for the standard form of the logarithmic and exponential laws, and show that the latter is actually \textit{always} non-physical in the sense proposed by 
\cite{kipping2013}. Then, we simulate transit lightcurves and perform a simulation study similar to the one done in EJ15 using the derived sampling schemes 
for the logarithmic law and the ones detailed in \cite{kipping2013} for the other two-parameter laws and \cite{kipping2015} for the three-parameter law, 
detailing when one law should be preferred over the other.

This work is organised as follows. In \S2, we first revisit the logarithmic and exponential 
laws in order to try to derive an efficient informative sampling strategy following the methods in \cite{kipping2013} for the standard forms of these laws. 
In \S3 we use those results in addition to the ones published by \cite{kipping2013} and \cite{kipping2015} in order to simulate transit lightcurves to test 
how well these laws perform in retrieving transit parameters. In \S4 we present a discussion and conclusions of our work.

% #################################################################################################################################
% #################################################################################################################################
% #################################################################################################################################
% ############################################# SECTION 2 #########################################################################
% #################################################################################################################################
% #################################################################################################################################
% #################################################################################################################################

\section{Efficient sampling of coefficients from the logarithmic and exponential laws revisited}

As explained in the introduction, an informative and efficient sampling of limb-darkening coefficients 
in order to fit them to transit lightcurves is fundamental. Motivated by this, \cite{kipping2013} introduced 
an algorithm which first imposes physically plausible constrains on the intensity profiles, namely, an everywhere 
positive intensity profile ($I(\mu)>0$) and a decreasing intensity profile from center to limb ($\partial I(\mu)/\partial \mu>0$), 
which in turn impose constrains on the parameters of the studied two-parameter law. With these constrains at hand, 
\cite{kipping2013} devised a triangular sampling strategy which only require sampling two uniformly distributed numbers between 
0 and 1, $q_1$ and $q_2$, which through a transformation can be converted in order to sample coefficients that follow the 
derived constrains. This was done in that work for the most popular two-parameter limb-darkening laws with the exception of the 
exponential limb-darkening law, whose derived constrains on the coefficients were not enough 
to use the triangular sampling technique, and for the typical form of the logarithmic law, which is 
different to the one used in \cite{kipping2013}.

We here first derive an informative and efficient sampling strategy for the typical form of the logarithmic law and then 
we study the exponential law, for which we conclude that deriving an efficient sampling strategy is actually 
\textit{impossible}; this implies that the law is fundamentally non-physical and, therefore, should not be used.

\subsection{Efficient sampling from the logarithmic law}
As described in \cite{klinglesmith1970}, the logarithmic law is given by
\begin{eqnarray}
\label{loglaw} I(\mu) = 1 - l_1(1-\mu)-l_2\mu \ln\mu.
\end{eqnarray}
However, \cite{kipping2013} derived the constrains for a law similar (but 
not the same) to the original logarithmic law, given by
\begin{eqnarray*}
I_K(\mu) = 1 - A(1-\mu)-B\mu (1-\ln\mu),
\end{eqnarray*}
which can be viewed as the original logarithmic law with an extra linear term. Given that this 
is not the original law many authors have adopted both to obtain limb-darkening coefficients 
and to model transit lightcurves, we here derive a sampling strategy for the original logarithmic 
limb-darkening law given in eq. (\ref{loglaw}). To do this, we start by imposing 
physically plausible constrains on the intensity profiles. The constrain of an everywhere positive intensity profile implies
\begin{eqnarray*}
 l_1(1-\mu)+l_2\mu \ln\mu < 1  &\forall& 0<\mu<1.
\end{eqnarray*}
In order to ensure this condition, we need to find the extrema of the expression in the 
left-hand side. We note that the maximum of the expression is obtained only if $l_2<0$, 
while the minimum of the expression is obtained if $l_2>0$. In both cases, this happens 
at $\mu_e=\exp [(l_1-l_2)/l_2]$, where we have assumed $l_2 \neq 0$. If $l_2=0$, then 
we obtain the inequality $l_1(1-\mu)<1$, which implies $l_1<1$, constraint we will see 
is valid for all the possible values of $l_2$. In the case $l_2>0$, because 
$\mu_e$ gives a minimum, 
$\mu\to 1$ and $\mu \to 0+$ maximise the expression in the desired range. The first limit 
gives the trivial constrain $1>0$, while the second limit gives the constrain $l_1<1$. In 
the case $l_2<0$, replacing $\mu_e$ in the expression leads to the constrain
\begin{eqnarray*}
\frac{l_1-1}{\mu_e} < l_2,
\end{eqnarray*}  
which, because $l_2<0$, again implies $l_1<1$. The condition 
for a decreasing intensity profile from center to limb, on the other hand, leads to the 
condition
\begin{eqnarray*}
l_1-l_2(1+\ln\mu) > 0  &\forall& 0<\mu<1.
\end{eqnarray*}
The left-hand side has, again, a division depending on the sign of $l_2$. If $l_2>0$, then 
the expression is convex and has no absolute minimum. It can be seen that then the 
expression is always satisfied for $0<\mu < 1$. In the limit $\mu \to 1$, the expression leads 
to the condition $l_1>l_2$. For the $\mu \to 0^+$ limit, however, no condition can be derived 
because the expression diverges. If $l_2<0$, on the other hand, the expression is concave, and 
it does not have an absolute maximum. It can be seen, however, that the expression in the limit 
$\mu \to 1$, leads to $l_1>l_2$ just as in the first case, but in this case the expression is not valid 
for $\mu \to 0^+$, because it goes to $-\infty$. This implies that for $l_2<0$ the inequality will 
never be satisfied in the desired range and, thus, we need $l_2>0$ in order for the profile to be 
everywhere decreasing. In summary, the derived condition for an everywhere positive intensity profile is
\begin{eqnarray*}
l_1<1,
\end{eqnarray*}
while the conditions for an everywhere decreasing intensity profile from center to limb are
\begin{eqnarray*}
l_2>0,\\
l_1>l_2.
\end{eqnarray*}

\begin{figure}
\includegraphics{sampling_simulation_log/triangular_sampling.eps}
\caption{Samples of the logarithmic limb-darkening coefficients that satisfy the derived constrains in 
this section out of $10^6$ uniformly sampled points between $-1<l_1<2$ and $-1<l_2<2$. Only 
$\sim 5\%$ of those samples satisfy such relations, shown here with red dashed lines.}
\label{triangular_sampling}
\end{figure}

Figure \ref{triangular_sampling} show these constrains geometrically. For illustration, $10^6$ points were uniformly sampled 
between $-1<l_1<2$ and $-1<l_2<2$ and a sample of those that satisfy these constrains were plotted. Only $5\%$ of them 
did satisfy such relations which demonstrates, as \cite{kipping2013} showed, the inefficiency of using such sampling strategy 
to draw physically plausible limb-darkening coefficients. This is the reason why we need to use the triangular sampling technique 
described in \cite{kipping2013}.

In order to use the triangular sampling technique, one needs to re-parametrize 
the constrains in order for them to be sampled on a right-angled triangle with this angle posed in the origin. A 
parametrisation that does this is the one with
\begin{eqnarray}
\label{v1}&v_1& = 1-l_1,\\
\label{v2}&v_2& = l_2.
\end{eqnarray}
If we now consider the transformations \citep[see][]{kipping2013}
\begin{eqnarray}
\label{v1q} &v_1& = \sqrt{q_1}q_2,\\
\label{v2q} &v_2& = 1 - \sqrt{q_1},
\end{eqnarray}
sampling $q_1$ and $q_2$ from uniform distributions between $(0,1)$ leads to a sampling with the desired constrains 
between $l_1$ and $l_2$. Replacing the expressions in eqs. (\ref{v1q}) and (\ref{v2q}) in eqs. (\ref{v1}) and (\ref{v2}) gives 
\begin{eqnarray*}
l_1 &=& 1-\sqrt{q_1}q_2\\
l_2 &=& 1-\sqrt{q_1}
\end{eqnarray*}
which leads to the inverse equations
\begin{eqnarray*}
q_1 &=& (1-l_2)^2,\\
q_2 &=& \frac{1-l_1}{1-l_2}.
\end{eqnarray*}
We note that, as expected, these relations return limb-darkening coefficients that are physically plausible for this law (i.e., they follow 
the derived constrains). Furthermore, we note these relations are different to the ones derived in \cite{kipping2013}; these are only applicable 
for his form of the logarithmic law.

\subsection{The exponential law is non-physical}
We now study the exponential limb-darkening law. This law was introduced by \cite{claret2003}, and is given by
\begin{eqnarray*}
I(\mu) &=& 1-e_1(1-\mu)-e_2/(1-e^\mu).
\end{eqnarray*}
\cite{kipping2013} tried to apply the same methods used for the other two-parameter laws in order to 
derive constrains and hence an efficient sampling scheme for the coefficients of this law, but observed that the triangular 
sampling technique was not applicable in this case because the imposed physical constrains were not 
able to yield a sufficient number of relations between the coefficients for it to 
be used. However, apparently overlooked by \cite{kipping2013} is the fact that the exponential law will \textit{never} 
yield physically plausible coefficients for $0<\mu<1$, because the conditions of an everywhere positive and decreasing 
intensity profile from center to limb cannot be satisfied at the same time, as we now show.

We start by imposing an everywhere positive intensity profile for this law. This leads to the relation
\begin{eqnarray*}
e_1(1-\mu)+e_2/(1-e^\mu)<1 &\forall& 0<\mu<1,
\end{eqnarray*}
and the objective is to study the left-hand side. We note that this expression has a minimum if 
$e_2<0$, while it has a maximum when $e_2>0$. We see that in the first case, as $\mu \to 0^+$, 
the expression tends to $\infty$, and therefore the expression is never satisfied; this implies that 
$e_2$ cannot be less than zero in order to have an everywhere positive intensity profile. On the 
other hand, if we impose an everywhere decreasing intensity profile for this law from center to 
limb, one can note this leads to the constrain:
\begin{eqnarray*}
e_1 - e_2 \frac{e^\mu}{(1-e^\mu)^2}>0 &\forall& 0<\mu<1.
\end{eqnarray*}
The form of the left-hand side expression again depends on the value of $e_2$ in the same way 
as before; however, in this case there is no absolute maximum or minimum and, thus, it suffices 
to study the expression at the borders. We note that in order for the expression to be satisfied 
for all the values of $\mu$, $e_2<0$, because only in this case the expression goes to $\infty$ 
when $\mu \to 0^+$. Because in order for the exponential law to have an everywhere positive intensity 
profile this condition was ruled out, this implies that both conditions cannot be met at the 
same time and, thus, there is no combination of coefficients $(e_1,e_2)$ that satisfy the physically 
plausible conditions suggested by \cite{kipping2013} for this law: in this sense, the exponential 
law introduced by \cite{claret2003} is non-physical.

\begin{figure}
\includegraphics{coefficients_check_exp/exponential_ldcs.eps}
\caption{Limb-darkening coefficients for the exponential law obtained using the methods described in 
EJ15 with the Kepler bandpass for all the stars in the ATLAS models with $T_\textnormal{eff}<9000$ K. As 
can be seen, $e_2<0$, which implies that all the fitted intensity profiles are not everywhere positive and, 
thus, non-physical.}
\label{exponential_ldcs}
\end{figure}

We note that typical values obtained by fitting the exponential law to model atmospheres give $e_2<0$, which means that 
most of the profiles fitted to model atmospheres do not have an everywhere positive intensity profile. To illustrate 
this, in Figure \ref{exponential_ldcs} we plot all the coefficients fitted using the exponential law following the methods 
of EJ15 using the Kepler bandpass for stars of interest for exoplanet studies ($T_\textnormal{eff}<9000$ K) obtained with 
the ATLAS models. In order to 
see at which value of $\mu$ the profile starts to be negative, we note that this happens as $\mu \to 0^+$. Here 
$1/(1-e^\mu) \approx -1/\mu$, which gives
\begin{eqnarray*}
I(\mu) &\approx& 1-e_1(1-\mu)+e_2/\mu.
\end{eqnarray*}
The intensity profile then, touches $I(\mu)=0$ around
\begin{eqnarray*}
\mu_0 \approx \frac{e_1-1 \pm \sqrt{(1-e_1)^2 - 4e_1e_2}}{2e_1}
\end{eqnarray*}
According to Figure \ref{exponential_ldcs}, $e_1\sim 0.6$, while $e_2 \sim - 2\times 10^{-3}$, which gives $\mu_0 \sim 0.005$, 
so the law starts giving negative values very close to (but not at) the limb, as we predicted. We note that typical transit observations are capable 
of sampling these points by chance, with high cadence observations as the ones done by the Kepler mission and the ones that will 
be done with the future TESS mission \citep{ricker2014} having an almost certain chance of sampling points inside those ranges. 
Furthermore, as the generation of transit lightcurves for laws like the exponential requiere either numerical integration or the usage 
of clever approximations that usually sample more points close to the limb \citep[which is the case for e.g., the \texttt{batman} code,][]{batman2015}, this law is doomed to produce numerical errors in transit lightcurves due to this fact. Because of these reasons, it is advisable not to use this law in real 
applications.

% #################################################################################################################################
% #################################################################################################################################
% #################################################################################################################################
% ############################################# SECTION 3 #########################################################################
% #################################################################################################################################
% #################################################################################################################################
% #################################################################################################################################

\section{Biases in transit parameters using two-parameter laws}
Having solved the issues regarding the sampling of limb-darkening coefficients from the 
logarithmic and exponential laws, we now turn to the study of the 
biases introduced on retrieved transit parameters in the transit fitting process introduced by using different limb-darkening laws. In 
order to perform this study, we perform a similar study as the one done in EJ15, but now 
(1) using the \texttt{batman} transit code described in \cite{batman2015}, (2) using three different two-parameter 
laws: the quadratic, logarithmic and square-root laws (with the exponential law left out of our analysis because, 
as was shown in \S 2.2, it's fundamentally non-physical) and the three-parameter law and (3) smaller steps in 
the planet-to-star radius ratio, $p=R_p/R_*$, in order to illustrate the evolution of the biases with this parameter 
in a cleaner way: small ratios ($p=0.01$), medium ratios ($p=0.07$) and large ones ($p=0.13$) .

As in EJ15, we simulate transit lightcurves for planets orbiting around host stars with solar metallicity, 
gravity and microturbulent velocity between 3500 K and 9000 K, with the mentioned planet-to-star radius ratios, 
values of the scaled semi-major axis of $a_R = a/R_* = \{3.27, 3.92, 4.87, 6.45, 9.52, 18.18, 200\}$ and different 
impact parameters. The transits are simulated using a non-linear law in order to emulate "real" intensity profiles, 
with the coefficients generated using the ATLAS models and the same methods as the ones used in EJ15 with the 
Kepler bandpass. The transits were then fitted using free limb-darkening coefficients with the mentioned laws.

For the simulations, the applied strategies in this work to sample physically plausible coefficients from two-parameter laws 
are as follows, all of which use numbers $q_1 \in (0,1)$ and $q_2 \in (0,1)$:
\begin{itemize}
\item For the quadratic limb-darkening law, we fit for the numbers $q_1 = (u_1 + u_2)^2$ and $q_2 = u_1/2(u_1+u_2)$. 
To obtain the coefficients from those fitted numbers, we use the relations $u_1 = 2\sqrt{q_1}q_2$ and $u_2 =\sqrt{q_1}(1-2q_2)$, 
which are derived in \cite{kipping2013}.
\item For the square-root law, we fit for the numbers $q_1 = (s_1 + s_2)^2$ and $q_2 = s_2/2(s_1+s_2)$. 
To obtain the coefficients from those fitted numbers, we use the relations $s_1 = \sqrt{q_1}(1-2q_2)$ and $s_2 =2\sqrt{q_1}q_2$, 
which are derived in \cite{kipping2013}.
\item For the logarithmic law, we fit for the numbers $q_1 = (1-l_2)^2$ and $q_2 = (1-l_1)/(1-l_2)$. 
To obtain the coefficients from those fitted numbers, we use the relations $l_1 = 1-\sqrt{q_1}q_2$ and $l_2=1-\sqrt{q_1}$, 
which are derived in \S 2.1.
\end{itemize}
For the three-parameter law, we use the formalism and codes described in \cite{kipping2015}. As explained before, analyses for the 
exponential law were not made as it is fundamentally non-physical. The code used to generate these simulations has been published 
in GitHub\footnote{\url{http://www.github.com/nespinoza/ld-simulations/}}, and can be used to perform analyses in a finer grid to the ones 
published here. 
\subsection{The case of central transits}
\begin{figure*}
\includegraphics[scale=0.8]{bias_transit_params/all_laws/b_0.0/simulation_b_00_float.eps}
\caption{Results of fitting transit lightcurves as described in \S 3.1 with the limb-darkening coefficients as free parameters. We only 
plot the size of the points which represent the input values of $p$.}
\label{central_sims}
\end{figure*}

The results of the simulations for central transits (i.e., $b=0$) are shown in Figure \ref{central_sims}, with the sizes of the points representing the 
input values of $p$. The upper panels showing the biases 
introduced on the planet-to-star radius ratio, $p$, and the lower panels showing the biases introduced on the scaled semi-major axes, $a_R$. From left to right, 
the panels show the biases introduced by using a quadratic law, a logarithmic law, a square-root law and a three-parameter law in the transit fitting 
procedures leaving the corresponding limb-darkening coefficients as free parameters. The dependence with the input values of $a_R$ are 
not shown as the bias seem to be almost independent of this parameter in this case (this can be also seen by looking at the lower panels of Figure 10 in EJ15, which 
give the same results as the ones shown here for the quadratic law, showing a nice agreement between the simulations done with our implementation of 
the \cite{ma2002} codes for the transit light curve generation and the \texttt{batman} code).

As can be seen from the figure, different limb-darkening laws have different behaviours in retrieving $p$ and $a_R$, with a dependence on the input value of 
$p$, and also depending on the temperature of its host star. First, it is interesting to note that the logarithmic law does a very good job at retrieving 
the parameters of small planet-to-star radius ratios, even at the level of the three-parameter law for stars with $T_\textnormal{eff}<6000$ K, and also for medium 
and large planet-to-star radius ratios with host-stars with $T_\textnormal{eff}<4000$ K (which makes this law perfect for present and future transit 
detection and characterisation around M-dwarfs). The quadratic law, on the other hand, is only the best among the options for host-stars between 
$4250<T_\textnormal{eff}<5500$ K, with the logarithmic law being the best in the $5500<T_\textnormal{eff}<6250$ K range, and the square-root law 
being the best for planets around host stars with temperatures between $6250<T_\textnormal{eff}<8000$ K. Hotter than this, the best option in terms 
of accuracy is the three-parameter law.

It is interesting to emphasise that although the biases introduced by the quadratic law might seem to be small, as mentioned in the introduction and in 
EJ15 they are significant for several candidate and confirmed exoplanets. However, choosing the right law in this case can help to achieve the same 
level of accuracy than the level of precision that Kepler achieves for most planets. In this case, for example, accuracies on the order of $\sim 0.01\%$ can 
be achieved for $p$ with a careful selection of a two-parameter law, and exoplanets with precisions better than that according to a query to the Nasa Exoplanet 
Archive\footnote{Query done on 29/09/2015.} form only $0.58\%$ of all candidate exoplanets and $1.2\%$ of the confirmed exoplanets. For the remaining 
exoplanets requiring a better accuracy, a new law might have to be created, as this precision is also the limit of the three-parameter law (which has a precision 
on $p$ around $\sim 0.01\%$ for stars with temperatures larger than $T_\textnormal{eff}=6000$ K). Studying new limb-darkening laws, however, 
is out of the scope of the present work.

\subsection{The case of non-central transits}
\begin{figure*}
\includegraphics[scale=0.8]{bias_transit_params/all_laws/b_0.3/simulation_b_03_float.eps}
\caption{Results of fitting transit lightcurves as described in \S 3.1 with the limb-darkening coefficients as free parameters, but for low impact 
parameter transits ($b=0.3$). The size of the points represent the input values of $p$, while their color represent the input values of $a_R$.}
\label{small_b_sims}
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.8]{bias_transit_params/all_laws/b_0.8/simulation_b_08_float.eps}
\caption{Results of fitting transit lightcurves as described in \S 3.1 with the limb-darkening coefficients as free parameters, but for high impact 
parameter transits ($b=0.8$). The size of the points represent the input values of $p$, while their color represent the input values of $a_R$.}
\label{big_b_sims}
\end{figure*}

Figures \ref{small_b_sims} and \ref{big_b_sims} show the results for low ($b=0.3$) and high ($b=0.8$) input impact parameters respectively. In these cases, 
we see that the biases are in general worse for smaller values of $p$ and $a_R$, i.e., for a given stellar radius, for smaller, close-in planets. We can 
also see that, again, a careful selection of the law to be used can allow one to minimize the biases on the retrieved transit parameters. For example, if 
the objective were to obtain $p$ with minimum bias for a low impact-parameter transit, then for host stars colder than $4000$ K the best option is to use 
either the logarithmic or the three-parameter law, which show biases on the order of $\sim 0.1\%$. In contrast, using the quadratic law for transits around 
those host stars the biases introduced on this parameter are on the order of $\sim 0.75\%$, i.e., almost an order of magnitude improvement in the accuracy.

Overall, as expected, the law that retrieves the parameters with minimum bias in low impact-parameter transits is the three-parameter law. However, for 
high impact-parameter transits of small planets, the logarithmic and square-root law seem to outperform this law in general if the objective is to retrieve 
a minimum bias estimator for $p$. This is due to the fact that the law is so flexible that it allows for small distortions of the transit lightcurve that, 
in this case, mimics variations that were actually attributable to $p$, adding a small but important bias on the retrieved parameter. However, for the other 
parameters ($a_R$ and $i$) this law seems to be the best choice in terms of the achieved accuracy.

\section{Discussion \& Conclusions}
In this work we have explored the different biases on the retrieved transit parameters by the usage of different limb-darkening laws. In particular, we 
explored the biases introduced by using three two-parameter laws (the quadratic, logarithmic and square-root laws) and the three-parameter law, for which 
we showed that a careful selection of the limb-darkening law to be used in a given dataset can allow one to retrieve minimum bias estimators for the transit 
parameters from transit lightcurves. In general, as shown in \S3, these two-parameter laws have ranges in which they perform at the same level or even better 
than the three-parameter law and, because of this, we encourage their use. We also discourage the usage of the exponential law which, as shown in \S2.2 is 
unphysical, and can lead to numerical errors if used on real data where sampling of points close to the limb (where the law diverges) is not uncommon.

The question of \textit{when} to use each of those laws is an important one. In particular, we have explored the relation between the \textit{real}, underlying 
transit parameters, the stellar host properties and the bias on the retrieved transit parameters, but we have stated no specific rule regarding when to use each 
law, but only guidelines based on our simulations. This was made on purpose, as the selection of which law to use has to be done in a case-by-case basis, reason 
by which we provide a code with which one can obtain the results for the same simulations for specific 
cases and with different resolutions\footnote{\url{http://www.github.com/nespinoza/ld-simulations/}}. It is important to note that in this work we have used the 
Kepler bandpass to study the relation between the biases on the retrieved transit parameters and the stellar host properties, but different bandpasses should give 
rise to slightly different functional relations because they give rise to different model intensity profiles, which are used in those simulations to approximate the 
expected intensity profile and the adequacy of each limb-darkening law at following it. As such, limb-darkening coefficients have to be calculated for each 
particular case, which is straightforward to do using the algorithms described in EJ15\footnote{\url{http://www.github.com/nespinoza/limb-darkening/}}.

\section{Acknowledgmenets}

N.E. is supported by CONICYT-PCHA/Doctorado Nacional. A.J. acknowledges 
support from FONDECYT project 1130857, the Ministry
for the Economy, Development, and Tourism Programa Iniciativa
Cient\'ifica Milenio through grant IC 120009, awarded to the
Millennium Institute of Astrophysics (MAS), and from BASAL CATA
PFB-06.

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Claret}{2000}]{claret2000} Claret, A., 2000, A\&A, 363, 1081.
\bibitem[\protect\citeauthoryear{Claret \& Hauschildt}{2003}]{claret2003} Claret, A. \& Hauschildt, P. H., 2003, 
A\&A, 412, 241.
\bibitem[\protect\citeauthoryear{D\'iaz-Cordov\'ez \& Gim\'enez}{1992}]{diazgimenez1992} D\'iaz-Cordov\'ez, J.,
\& Gim\'enez, A., 1992, A\&A, 259, 227.
\bibitem[\protect\citeauthoryear{Dorn et al.}{2015}]{dorn2015} Dorn, C., Khan, A., Heng, K., Alibert, Y., Connolly, J.,
Benz, W. \& Tackley, P., 2015, A\&A, 577, 83.
\bibitem[\protect\citeauthoryear{Kipping}{2013}]{kipping2013} Kipping, D. M., 2013, MNRAS, 435, 2152.
\bibitem[\protect\citeauthoryear{Kipping}{2014}]{kipping2014AP} Kipping, D. M., 2014, MNRAS, 440, 2164.
\bibitem[\protect\citeauthoryear{Kipping}{2015}]{kipping2015} Kipping, D. M., 2015, arXiv:1509.03483.
\bibitem[\protect\citeauthoryear{Klinglesmith \& Sobieski}{1970}]{klinglesmith1970} Klinglesmith, D. A. \&
Sobieski, S., 1970, AJ, 75, 175.
\bibitem[\protect\citeauthoryear{Espinoza \& Jord\'an}{2015}]{ej2015} Espinoza, N. \& Jord\'an, A., 2015, 
MNRAS, 450, 1879.
\bibitem[\protect\citeauthoryear{Howarth}{2011}]{howarth2011} Howarth, I., 2011, 
MNRAS, 413, 1515.
%\bibitem[\protect\citeauthoryear{Hebb et al.}{2009}]{Hebb2009} Hebb et al., 2009, ApJ, 693, 1920.
%\bibitem[\protect\citeauthoryear{Kreidberg et al.}{2013}]{Kreidberg2013} Kreidberg et al., 2013, Nature, 505, 69.
\bibitem[\protect\citeauthoryear{Klinglesmith \& Sobieski}{1970}]{klinglesmith1970} Klinglesmith, D. A. \&
Sobieski, S., 1970, AJ, 75, 175.
\bibitem[\protect\citeauthoryear{Kreidberg}{2015}]{batman2015} Kreidberg, L., 2015, arXiv:1507.08285.
\bibitem[\protect\citeauthoryear{Mandel \& Agol}{2002}]{ma2002} Mandel, K \& Agol, E., 2002, ApJ,
580, L171.
%\bibitem[\protect\citeauthoryear{Mandell et al.}{2013}]{Mandell2013} Mandell et al., 2013, ApJ, 779, 128.
\bibitem[\protect\citeauthoryear{Ricker et al.}{2014}]{ricker2014} Ricker et al., 2014, SPIE, 9143.
\bibitem[\protect\citeauthoryear{Rowe et al.}{2015}]{rowe2015} Rowe et al., 2015, ApJS, 217, 16.

\bibitem[\protect\citeauthoryear{Seager \& Mall\'en-Ornelas}{2003}]{sm2003} Seager, S. \& Mall\'en-Ornelas, G., 2003, ApJ, 585, 1038.
\bibitem[\protect\citeauthoryear{Sing et al.}{2009}]{sing2009} Sing, D. K., D\'esert, J.-M.,
Lecavelier Des Etangs, A., Ballester, G. E., Vidal-Madjar, A., Parmentier, V., Hebrard, G. \& Henry, G. W.,
2009, A\&A, 505, 891.
%\bibitem[\protect\citeauthoryear{Sing et al.}{2013}]{Sing2013} Sing et al., 2013, MNRAS, 436, 2956.
%\bibitem[\protect\citeauthoryear{Stevenson et al.}{2014}]{Stevenson2014} Stevenson et al., 2014, AJ, 147, 161.
%\bibitem[\protect\citeauthoryear{Swain et al.}{2013}]{Swain2013} Swain et al., 2013, Icarus, 225, 432.
\bibitem[\protect\citeauthoryear{Weiss \& Marcy}{2014}]{wm2014} Weiss, L. \& Marcy, G., 2014, ApJ, 783L, 6.
\bibitem[\protect\citeauthoryear{Wolfgang \& Lopez}{2015}]{WL2015} Wolfgang, A. \& Lopez, E., 2015, ApJ, 806, 183.
\end{thebibliography}

%\appendix

%if $e_2<0$, then the profile diverges to $-\infty$ as $\mu\to 0$ (because the term $1-e^\mu$ 
%tends to 0 from the left) thus not being able to fulfil the constrain of an everywhere positive intensity profile, while for 
%$e_2>0$ the profile is strictly \textit{increasing} from center to limb, thus not being able to fulfil the constrain of an 
%everywhere decreasing intensity profile from center to limb.

\bsp

\label{lastpage}

\end{document}

### 2015-11-13 which_law_2_use.tex
revised version to be submitted

@@
 
-\title[Choosing the right law for minimum bias retrieval of transit parameters from transit lightcurves]
-{Limb-darkening and exoplanets II: choosing the right law for minimum bias retrieval of transit parameters from transit lightcurves}
+\title[Choosing the best law for minimum bias retrieval of transit parameters]
+{Limb-darkening and exoplanets II: Choosing the Best Law for Minimum Bias Retrieval of Transit Parameters}
 \author[Espinoza \& Jord\'an ]{
 N\'estor Espinoza$^{1,2}$\thanks{E-mail:nespino@astro.puc.cl}, 
-Andr\'es Jord\'an$^{2,1}$\thanks{E-mail: ajordan@astro.puc.cl}\\ 
-$^{1}$Millennium Institute of Astrophysics, Vicu\~na Mackenna 4860, Santiago, Chile\\
-$^{2}$Instituto de Astrof\'isica, Pontificia Universidad Cat\'olica de Chile, Vicu\~na Mackenna 
-4860, Santiago, Chile}
+Andr\'es Jord\'an$^{1,2}$\thanks{E-mail:ajordan@astro.puc.cl}\\ 
+$^{1}$Instituto de Astrof\'isica, Pontificia Universidad Cat\'olica de Chile, Vicu\~na Mackenna 
+4860, Santiago, Chile
+$^{2}$Millennium Institute of Astrophysics, Santiago, Chile\\
+}
 \begin{document}
@@
 \begin{abstract}
-It has recently been demonstrated that the parametrization of the limb-darkening effect on a star has a direct impact 
-on the parameters retrieved from transit lightcurves such as the exoplanet's radius, scaled semi-major axis and inclination. However, 
-studies regarding this issue have only focused on the widely used quadratic limb-darkening law, leaving outside of the analysis 
-other proposed laws that in fact are better descriptors of model intensity profiles. In this work, we show that in fact 
-laws such as the logarithmic, square-root and three-parameter do a better job at retrieving the mentioned parameters from transit 
-lightcurves than the widely used quadratic law and, as such, we recommend using those instead. We also detail when to use each of those, 
-which we note has a dependence on both stellar and transit parameters. In addition, we demonstrate that the exponential law should not be 
-used as it fundamentally non-physical, typically producing a divergence towards negative intensities at the limb.
+The parametrization of the limb-darkening effect of a star has a direct impact 
+on the parameters retrieved from transit lightcurves such as the exoplanet's radius, scaled semi-major axis and inclination.
+Studies of the effect of limb darkening assumptions on the retrieved parameters have mostly focused on the widely used quadratic limb-darkening law, leaving out
+other proposed laws that are in fact better descriptions of model intensity profiles. In this work, we show that 
+laws such as the logarithmic, square-root and three-parameter laws do a better job at retrieving the mentioned parameters from transit 
+lightcurves than the widely used quadratic law and therefore we recommend using those instead.
+We also provide code to guide the decision of when to use each of the laws,  which we note has a dependence on both stellar and transit parameters.
+Finally, we demonstrate that the so-called exponential law is non-physical as it typically produces negative intensities close to the limb and should therefore not be used.
 \end{abstract}
@@
 \section{Introduction}
-In the past decade, the study of transiting exoplanets has been evolving from discovery to very precise characterization of these systems, 
-thanks to the exquisit precision allowed mainly by space-based observatories such as the Hubble Space Telescope (HST) and the Kepler mission. 
-This in turn has allowed the exoplanet community to study precise mass-radius diagrams \citep[see, e.g.,][and references therein]{wm2014}, and in turn raise 
-questions about the possibility of not only obtaining a precise determination of the internal composition of small, rocky exoplanets based on mass-radius
-measurements \citep{dorn2015} or of their atmospheric fractions from radius measurements alone \citep{WL2015}, but also has allowed for the determination of
-derived parameters of the systems that even allow for the obtention of stellar parameters directly from transit lightcurves through techniques such as asterodensity
+
+In the past decade, the study of transiting exoplanets has evolved from discovery to very precise characterization of these systems, 
+thanks to the exquisite precision allowed mainly by space-based observatories such as the {\em Hubble Space Telescope} ({\em HST}) and the {\em Kepler} mission \citep{koch2010}.
+This has allowed the study of precise mass-radius diagrams \citep[see, e.g.,][and references therein]{wm2014}, and in turn  allow the possibility of not only obtaining a precise determination of the internal composition of small, rocky exoplanets based on mass-radius
+measurements \citep{dorn2015} or of their atmospheric fractions from radius measurements alone \citep{WL2015}, but also of the determination of
+derived parameters of the systems that even allow for the estimation of stellar parameters directly from transit lightcurves through techniques such as asterodensity
 profiling \citep{sm2003,kipping2014AP}, or of the detection of atmospheric features in exoplanet atmospheres through the technique of transmission spectroscopy. 
@@
 
-In a recent study \citep[][hereafter referred as EJ15]{ej2015}, we showed that the accuracy is actually catching up with the precision 
-of these measurements due to our poor understanding of the limb-darkening effect. In particular, we showed that there are important 
-biases both when fixing and fitting the limb-darkening coefficients in the light curve fitting process, with the latter arising from the fact 
-that the popular and widely used quadratic law is unable to model the complex intensity profile of real stars and the former arising for this 
-same reason plus the fact that different methods of fitting the model intensity profiles give rise to different limb-darkening coefficients and 
-from the fact that we have an imperfect knowledge of the real intensity profiles of stars. This showed that fixing the limb-darkening coefficients is 
-actually the worst option if one is willing to obtain precise \textit{and} accurate transit parameters, because the biases arise from three different sources, 
+In a recent study \citep[][hereon EJ15]{ej2015}, we showed that the accuracy is actually catching up with the precision 
+of these measurements due to our imperfect understanding of the limb-darkening effect. In particular, we showed that there are important 
+biases both when fixing and fitting for the limb-darkening coefficients in the light curve fitting process. The biases when fitting for the limb darkening coefficients arise from the fact 
+that the popular and widely used quadratic law is unable to model the complex intensity profile of real stars,  and the biases when fixing the coefficients arise for the
+same reason plus the facts that different methods of fitting the model intensity profiles (transit light curve versus intensity profile fitting) give rise to different limb-darkening coefficients and 
+the fact that we have an imperfect knowledge of the real intensity profiles of stars. We showed that fixing the limb-darkening coefficients is 
+the worst option if one aims to obtain precise \textit{and} accurate transit parameters, because the biases arise from three different sources, 
 with the last one (the fact that we do not have a perfect modelling of the stellar intensity profiles of real stars) having an unknown but possibly 
-large impact on them.
+large impact.
 
-Given the above, unless the data quality is really poor (and one is willing to sacrifice bias over variance), there is actually no good reason why one would 
-actually want to fix the limb-darkening coefficients in the transit fitting process (assuming computational resources are not an issue). However, although fitting the 
-limb-darkening coefficients seems to be a good solution to the accuracy problem, this still has the issue of the low flexibility of the quadratic limb-darkening 
-law which still causes important biases on the retrieved transit parameters according to EJ15, which can be a large as $\sim 1\%$ for the planet-to-star 
+Given the above, unless the data quality is really poor (and one is willing to trade bias for variance), there is actually no good reason to fix the limb-darkening coefficients in the transit fitting process (assuming computational resources are not an issue).
+However, although fitting the
+limb-darkening coefficients seems to be a good solution to the accuracy problem, there remains the issue of the low flexibility of the quadratic limb-darkening 
+law which can cause important biases on the retrieved transit parameters as shown in EJ15. These biases can be a large as $\sim 1\%$ for the planet-to-star 
 radius ratio $R_p/R_*$, $\sim 2\%$ for the scaled semi-major axis, $a/R_*$, and $2\%$ for the inclination, where $R_p$ is the planetary radius, $R_*$ 
-the stellar radius and $a$ the semi-major axis. The importance for missions like Kepler and for future missions like the Transiting Exoplanet Survey 
-Satellite \cite[TESS,][]{ricker2014} is evident when looking at the most recent results from the Kepler mission: if we focus on the planet-to-star radius ratio 
-alone, which according to EJ15 has an accuracy bias on the order of $\sim 0.2\%$, a query to the Nasa Exoplanet Archive\footnote{\url{http://exoplanetarchive.ipac.caltech.edu/}; query done on 29/09/2015.} shows that out of 3063 planetary candidates, 933 ($26\%$) have precisions better than
-$0.2\%$, and out of 1001 Kepler confirmed exoplanets, 463 (46\%) do too. This means that at least\footnote{It is important to note that this is an 
+the stellar radius and $a$ the semi-major axis. The importance for missions like {\em Kepler} and for future missions like the Transiting Exoplanet Survey 
+Satellite \cite[TESS,][]{ricker2014} is evident when looking at the most recent results from the {\em Kepler} mission: if we focus on the planet-to-star radius ratio measurements 
+alone, which according to EJ15 have an accuracy bias on the order of $\sim 0.2\%$, a query to the Nasa Exoplanet Archive\footnote{\url{http://exoplanetarchive.ipac.caltech.edu/}; query done on 29/09/2015.} shows that out of 3063 planetary candidates, 933 ($26\%$) have precisions better than
+$0.2\%$, and out of 1001 {\em Kepler} confirmed exoplanets, 463 (46\%) do too. This means that at least\footnote{It is important to note that this is an 
 underestimate of the number of planet candidates with estimation errors, due to the fact that the Kepler pipeline makes use of fixed limb-darkening 
@@
 uncertainties like the ones introduced by limb-darkening) and almost half of the confirmed exoplanets (from which, e.g., characterization studies are 
-based on) have important systematic errors.
+based on) have significant systematic errors.
 
-An obvious solution to the above mentioned problem if one decides to fit the limb-darkening coefficients is to try to use \textit{other} laws to describe 
+An obvious solution to the issues mentioned above if one decides to fit the limb-darkening coefficients is to try to use alternative laws to describe 
 the intensity profile of stars. Although the non-linear law proposed by \cite{claret2000} seems to be the most flexible, the fact that it has four free parameters 
-does not make it a very attractive choice in this scheme if one is willing to replace the quadratic law. However, laws with fewer parameters have been proposed, 
-with the two-parameter laws being the exponential proposed by \cite{claret2003}, the logarithmic proposed by \cite{klinglesmith1970} and the square-root proposed 
-by \cite{diazgimenez1992}. In addition, a very flexible three-parameter law was also proposed by \cite{sing2009}. These lower parameter laws seem to be 
-very attractive for transit fitting purposes, due to their flexibility at following different intensity profiles \citep[see, e.g., ][for a comparison between the goodness of 
+does not make it a very attractive.
+Several laws with fewer parameters have been proposed.
+Two-parameter laws are the exponential proposed by \cite{claret2003}, the logarithmic proposed by \cite{klinglesmith1970} and the square-root proposed
+by \cite{diazgimenez1992}. In addition, a very flexible three-parameter law was also proposed by \cite{sing2009}. These laws with fewer parameters are potentially 
+very attractive for transit fitting purposes, due to their flexibility at following different intensity profiles  and their low number of parameters \citep[see, e.g., ][for a comparison between the goodness of
 fit to ATLAS model atmospheres of the mentioned two-parameter laws which outperform the linear and quadratic laws in terms of following the intensity 
-profiles]{howarth2011} and their low number of parameters.
+profiles]{howarth2011}.
 
-Despite the attractive nature of the mentioned limb-darkening laws, testing their performance at retrieving transit parameters from transit 
-lightcurves was a problem until recently for two reasons. First, there was no published algorithm that 
-was capable of efficiently generating fast and accurate transit lightcurves using all of these non-standard laws. However, recently \cite{batman2015} published an 
-algorithm that does exactly this called \texttt{batman}, enabling one then to generate transit lightcurves very efficiently with any arbitrary limb-darkening law. 
+Despite the attractive nature of the above mentioned limb-darkening laws, testing their performance at retrieving transit parameters from transit 
+lightcurves was a problem until recently for two reasons.
+First, there was no publicly available code capable of efficiently generating fast and accurate transit lightcurves using all of these non-standard laws.
+However, recently \cite{batman2015} published an
+algorithm that does exactly this called \texttt{batman}, enabling the generation of transit lightcurves very efficiently with any arbitrary limb-darkening law. 
 The second problem was that it was not clear how to sample limb-darkening coefficients in an informative (i.e., sampling all the physically possible parameter 
 space) and efficient way for all of these laws.
-\cite{kipping2015} recently derived an algorithm to sample parameters from the three-parameter law by imposing physically plausible constrains on the intensity profiles which derived in constrains on the limb-darkening coefficients being fitted, while \cite{kipping2013}, using the same principle, derived an algorithmic way of
-doing this for two-parameter laws. However, he found that his algorithm was not applicable to the exponential law and thus no constrains for this law could 
-be derived. In addition to this, the form of the logarithmic law used in \cite{kipping2013} differs from the standard one proposed by \cite{klinglesmith1970}, 
-which is actually the one used in \texttt{batman}. Thus, in order to sample coefficients from this limb-darkening law, one first has to derive an efficient 
-informative sampling scheme for this standard form of the law.
+Recently, \cite{kipping2015} presented an algorithm to sample parameters from the three-parameter law by imposing physically motivated constraints on the intensity profiles which derived in constrains on the limb-darkening coefficients being fitted.
+cite{kipping2013}, using the same principles, derived an algorithmic way of
+doing this for two-parameter laws. He found that his algorithm was not applicable to the exponential law and thus no constrains for this law could 
+be derived. We note that the form of the logarithmic law used in \cite{kipping2013} differs from the standard one proposed by 
+\cite{klinglesmith1970}. Thus, in order to  efficiently sample coefficients from the latter limb-darkening law one has to derive an efficient  informative sampling scheme for it.
 
-In this work, we aim at testing how well do these non-standard laws perform at retrieving transit parameters from transit lightcurves, and compare them to 
-the retrievals done by the standard quadratic limb-darkening law. For this, we first follow \cite{kipping2013} in order to derive an efficient sampling scheme 
+In this work, we extend the work of EJ15 by testing how well these non-standard laws perform at retrieving transit parameters from transit lightcurves, and compare them to 
+the retrievals done by the standard quadratic limb-darkening law. We follow \cite{kipping2013} in order to derive an efficient sampling scheme 
 for the standard form of the logarithmic and exponential laws, and show that the latter is actually \textit{always} non-physical in the sense proposed by 
 \cite{kipping2013}. Then, we simulate transit lightcurves and perform a simulation study similar to the one done in EJ15 using the derived sampling schemes 
-for the logarithmic law and the ones detailed in \cite{kipping2013} for the other two-parameter laws and \cite{kipping2015} for the three-parameter law, 
-detailing when one law should be preferred over the other.
+for the logarithmic law and the sampling schemes detailed in \cite{kipping2013} for the other two-parameter laws and \cite{kipping2015} for the three-parameter law.
+We use our simulations to provide guidance as to when a particular law should be preferred.
 
-This work is organised as follows. In \S2, we first revisit the logarithmic and exponential 
-laws in order to try to derive an efficient informative sampling strategy following the methods in \cite{kipping2013} for the standard forms of these laws. 
+This work is organised as follows. In \S2, we revisit the logarithmic and exponential 
+laws in order to derive an efficient informative sampling strategy following the methods in \cite{kipping2013} for the standard forms of these laws. 
 In \S3 we use those results in addition to the ones published by \cite{kipping2013} and \cite{kipping2015} in order to simulate transit lightcurves to test 
@@
 in order to fit them to transit lightcurves is fundamental. Motivated by this, \cite{kipping2013} introduced 
-an algorithm which first imposes physically plausible constrains on the intensity profiles, namely, an everywhere 
-positive intensity profile ($I(\mu)>0$) and a decreasing intensity profile from center to limb ($\partial I(\mu)/\partial \mu>0$), 
-which in turn impose constrains on the parameters of the studied two-parameter law. With these constrains at hand, 
-\cite{kipping2013} devised a triangular sampling strategy which only require sampling two uniformly distributed numbers between 
-0 and 1, $q_1$ and $q_2$, which through a transformation can be converted in order to sample coefficients that follow the 
-derived constrains. This was done in that work for the most popular two-parameter limb-darkening laws with the exception of the 
-exponential limb-darkening law, whose derived constrains on the coefficients were not enough 
-to use the triangular sampling technique, and for the typical form of the logarithmic law, which is 
+a procedure which first imposes physically motivated constrains on the intensity profiles, namely, an everywhere 
+positive intensity, $I(\mu)>0$,  and a decreasing intensity profile from center to limb, $\partial I(\mu)/\partial \mu>0$, 
+which in turn impose constraints on the two parameters of the law. With these constraints in hand, 
+\cite{kipping2013} devised a triangular sampling strategy which only requires sampling two uniformly distributed numbers between 
+0 and 1, $q_1$ and $q_2$, which through a transformation can be transformed to sample coefficients.
+This was done in that work for the most popular two-parameter limb-darkening laws with the exceptions of the
+exponential limb-darkening law, whose derived constraints on the coefficients were not enough 
+to use the triangular sampling technique, and the typical form of the logarithmic law, which is 
 different to the one used in \cite{kipping2013}.
 
-We here first derive an informative and efficient sampling strategy for the typical form of the logarithmic law and then 
+We now derive an informative and efficient sampling strategy for the more typical form of the logarithmic law and then 
 we study the exponential law, for which we conclude that deriving an efficient sampling strategy is actually 
-\textit{impossible}; this implies that the law is fundamentally non-physical and, therefore, should not be used.
+impossible; this implies that the law is fundamentally non-physical and, therefore, should not be used.
 
 \subsection{Efficient sampling from the logarithmic law}
+
 As described in \cite{klinglesmith1970}, the logarithmic law is given by
@@
 \begin{eqnarray*}
-I_K(\mu) = 1 - A(1-\mu)-B\mu (1-\ln\mu),
+I_K(\mu) = 1 - A(1-\mu)-B\mu (1-\ln\mu).
 \end{eqnarray*}
-which can be viewed as the original logarithmic law with an extra linear term. Given that this 
-is not the original law many authors have adopted both to obtain limb-darkening coefficients 
-and to model transit lightcurves, we here derive a sampling strategy for the original logarithmic 
-limb-darkening law given in eq. (\ref{loglaw}). To do this, we start by imposing 
-physically plausible constrains on the intensity profiles. The constrain of an everywhere positive intensity profile implies
+
+Given that this 
+is not the law many authors have adopted we  derive here a sampling strategy for the original law given in eq. (\ref{loglaw}).  The constrain of an everywhere positive intensity profile implies
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-In order to ensure this condition, we need to find the extrema of the expression in the 
-left-hand side. We note that the maximum of the expression is obtained only if $l_2<0$, 
-while the minimum of the expression is obtained if $l_2>0$. In both cases, this happens 
+In order to ensure this condition, we need to find the extrema of the expression on the 
+left-hand side. We note that a maximum of the expression is obtained only if $l_2<0$, 
+while a minimum of the expression is obtained if $l_2>0$. In both cases, this happens 
 at $\mu_e=\exp [(l_1-l_2)/l_2]$, where we have assumed $l_2 \neq 0$. If $l_2=0$, then 
-we obtain the inequality $l_1(1-\mu)<1$, which implies $l_1<1$, constraint we will see 
+we obtain the inequality $l_1(1-\mu)<1$, which implies $l_1<1$, a constraint we will see 
 is valid for all the possible values of $l_2$. In the case $l_2>0$, because 
@@
 \end{eqnarray*}
-The left-hand side has, again, a division depending on the sign of $l_2$. If $l_2>0$, then 
-the expression is convex and has no absolute minimum. It can be seen that then the 
+The left-hand side has different behaviour depending on the sign of $l_2$. If $l_2>0$, then 
+the expression is convex and has no absolute minimum. It can be seen then that  the 
 expression is always satisfied for $0<\mu < 1$. In the limit $\mu \to 1$, the expression leads 
-to the condition $l_1>l_2$. For the $\mu \to 0^+$ limit, however, no condition can be derived 
-because the expression diverges. If $l_2<0$, on the other hand, the expression is concave, and 
-it does not have an absolute maximum. It can be seen, however, that the expression in the limit 
-$\mu \to 1$, leads to $l_1>l_2$ just as in the first case, but in this case the expression is not valid 
+to the condition $l_1>l_2$. For the $\mu \to 0^+$ limit no condition can be derived 
+because the expression diverges. If $l_2<0$ the expression is concave, and 
+it does not have an absolute maximum in $]0,1[$, the expression in the limit 
+$\mu \to 1$ leads to $l_1>l_2$ just as in the first case, but in this case the expression is not valid 
 for $\mu \to 0^+$, because it goes to $-\infty$. This implies that for $l_2<0$ the inequality will 
@@
 In order to use the triangular sampling technique, one needs to re-parametrize 
-the constrains in order for them to be sampled on a right-angled triangle with this angle posed in the origin. A 
+the constrains in order for them to be sampled on a right-angled triangle with this angle posed at the origin. A 
 parametrisation that does this is the one with
@@
 \end{eqnarray}
-sampling $q_1$ and $q_2$ from uniform distributions between $(0,1)$ leads to a sampling with the desired constrains 
-between $l_1$ and $l_2$. Replacing the expressions in eqs. (\ref{v1q}) and (\ref{v2q}) in eqs. (\ref{v1}) and (\ref{v2}) gives 
+sampling $q_1$ and $q_2$ from uniform distributions between $(0,1)$ leads to a sampling with the desired constrains.
+Replacing the expressions in eqs.
+(\ref{v1q}) and (\ref{v2q}) in eqs.
+(\ref{v1}) and (\ref{v2}) gives
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-We note that, as expected, these relations return limb-darkening coefficients that are physically plausible for this law (i.e., they follow 
-the derived constrains). Furthermore, we note these relations are different to the ones derived in \cite{kipping2013}; these are only applicable 
-for his form of the logarithmic law.
+We note that, as expected by construction, these relations return limb-darkening coefficients that are physically plausible for this law.
+Furthermore, we note these relations are different to the ones derived
+in \cite{kipping2013} as those are only applicable 
+for his adopted form of the logarithmic law.
 
 \subsection{The exponential law is non-physical}
-We now study the exponential limb-darkening law. This law was introduced by \cite{claret2003}, and is given by
+
+We now study the exponential limb-darkening law. This law was 
+introduced by \cite{claret2003}, and is given by
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-\cite{kipping2013} tried to apply the same methods used for the other two-parameter laws in order to 
-derive constrains and hence an efficient sampling scheme for the coefficients of this law, but observed that the triangular 
-sampling technique was not applicable in this case because the imposed physical constrains were not 
-able to yield a sufficient number of relations between the coefficients for it to 
-be used. However, apparently overlooked by \cite{kipping2013} is the fact that the exponential law will \textit{never} 
+\cite{kipping2013} tried to apply the same methods used for the other two-parameter laws but observed that the triangular 
+sampling technique was not applicable in this case because the physical constraints imposed were not 
+able to yield a sufficient number of relations between the coefficients. However, apparently overlooked by \cite{kipping2013} is the fact that the exponential law will never
 yield physically plausible coefficients for $0<\mu<1$, because the conditions of an everywhere positive and decreasing 
@@
 
-We start by imposing an everywhere positive intensity profile for this law. This leads to the relation
+We start by imposing an everywhere positive intensity profile for this law, which leads to the relation
 \begin{eqnarray*}
@@
 and the objective is to study the left-hand side. We note that this expression has a minimum if 
-$e_2<0$, while it has a maximum when $e_2>0$. We see that in the first case, as $\mu \to 0^+$, 
-the expression tends to $\infty$, and therefore the expression is never satisfied; this implies that 
-$e_2$ cannot be less than zero in order to have an everywhere positive intensity profile. On the 
+$e_2<0$, while it has a maximum if $e_2>0$. We see that in the first case, 
+as $\mu \to 0^+$, 
+the expression tends to $+\infty$, and therefore the expression cannot be satisfied for all $\mu$; this implies that 
+$e_2$ cannot be less than zero. On the 
 other hand, if we impose an everywhere decreasing intensity profile for this law from center to 
-limb, one can note this leads to the constrain:
+limb, this leads to the constraint
 \begin{eqnarray*}
@@
 The form of the left-hand side expression again depends on the value of $e_2$ in the same way 
-as before; however, in this case there is no absolute maximum or minimum and, thus, it suffices 
+as before, however, in this case there is no absolute maximum or minimum in $]0,1[$] and, thus, it suffices 
 to study the expression at the borders. We note that in order for the expression to be satisfied 
@@
 same time and, thus, there is no combination of coefficients $(e_1,e_2)$ that satisfy the physically 
-plausible conditions suggested by \cite{kipping2013} for this law: in this sense, the exponential 
+plausible conditions suggested by \cite{kipping2013} for this law. This implies that the exponential 
 law introduced by \cite{claret2003} is non-physical.
@@
 most of the profiles fitted to model atmospheres do not have an everywhere positive intensity profile. To illustrate 
-this, in Figure \ref{exponential_ldcs} we plot all the coefficients fitted using the exponential law following the methods 
-of EJ15 using the Kepler bandpass for stars of interest for exoplanet studies ($T_\textnormal{eff}<9000$ K) obtained with 
+this, in Figure~\ref{exponential_ldcs} we plot all the coefficients fitted using the exponential law following the methods 
+of EJ15 using the {\em Kepler} bandpass for model atmospheres with $T_\textnormal{eff}<9000$ K from  
 the ATLAS models. In order to 
@@
 \end{eqnarray*}
-According to Figure \ref{exponential_ldcs}, $e_1\sim 0.6$, while $e_2 \sim - 2\times 10^{-3}$, which gives $\mu_0 \sim 0.005$, 
+As shown Figure~\ref{exponential_ldcs}, $e_1\sim 0.6$, while $e_2 \sim - 2\times 10^{-3}$, which gives $\mu_0 \sim 0.005$, 
 so the law starts giving negative values very close to (but not at) the limb, as we predicted. We note that typical transit observations are capable 
-of sampling these points by chance, with high cadence observations as the ones done by the Kepler mission and the ones that will 
-be done with the future TESS mission \citep{ricker2014} having an almost certain chance of sampling points inside those ranges. 
+of sampling these points with high cadence observations as the ones done by the {\em Kepler} mission and the ones that will 
+be done with the future TESS mission \citep{ricker2014}, which will have an almost certain chance of sampling points with $\mu\approx 1$. 
 Furthermore, as the generation of transit lightcurves for laws like the exponential requiere either numerical integration or the usage 
-of clever approximations that usually sample more points close to the limb \citep[which is the case for e.g., the \texttt{batman} code,][]{batman2015}, this law is doomed to produce numerical errors in transit lightcurves due to this fact.
-Because of these reasons, it is advisable not to use this law in real
-applications.
+of  approximations that usually sample more points close to the limb \citep[which is the case for e.g., the \texttt{batman} code,][]{batman2015}, this law is doomed to produce numerical errors in transit lightcurves due to this fact.
+Because of these reasons, we advise not to use this law.
 
@@
 \section{Biases in transit parameters using two-parameter laws}
-Having solved the issues regarding the sampling of limb-darkening coefficients from the 
+
+Having dealt with the sampling of limb-darkening coefficients from the 
 logarithmic and exponential laws, we now turn to the study of the 
-biases introduced on retrieved transit parameters in the transit fitting process introduced by using different limb-darkening laws. In 
-order to perform this study, we perform a similar study as the one done in EJ15, but now 
+biases introduced on retrieved transit parameters in the transit fitting process introduced by using different limb-darkening laws. We perform a similar study as the one done in EJ15, but now 
 (1) using the \texttt{batman} transit code described in \cite{batman2015}, (2) using three different two-parameter 
-laws: the quadratic, logarithmic and square-root laws (with the exponential law left out of our analysis because, 
-as was shown in \S 2.2, it's fundamentally non-physical) and the three-parameter law and (3) smaller steps in 
+laws: the quadratic, logarithmic and square-root laws, and the three-parameter law and (3) smaller steps in 
 the planet-to-star radius ratio, $p=R_p/R_*$, in order to illustrate the evolution of the biases with this parameter 
-in a cleaner way: small ratios ($p=0.01$), medium ratios ($p=0.07$) and large ones ($p=0.13$) .
+in a cleaner way: small ratios ($p=0.01$), medium ratios ($p=0.07$) and large ones ($p=0.13$).
 
-As in EJ15, we simulate transit lightcurves for planets orbiting around host stars with solar metallicity, 
-gravity and microturbulent velocity between 3500 K and 9000 K, with the mentioned planet-to-star radius ratios, 
-values of the scaled semi-major axis of $a_R = a/R_* = \{3.27, 3.92, 4.87, 6.45, 9.52, 18.18, 200\}$ and different 
-impact parameters. The transits are simulated using a non-linear law in order to emulate "real" intensity profiles, 
+As in EJ15, we simulate transit lightcurves for planets orbiting host stars with solar metallicity, 
+gravity and microturbulent velocity, and $T_{\rm eff}$ between 3500 K and 9000 K, with the mentioned planet-to-star radius ratios, 
+values of the scaled semi-major axis of 
+$a_R = a/R_* = \{3.27, 3.92, 4.87, 6.45, 9.52, 18.18, 200\}$ and different 
+impact parameters. The transits are simulated using a non-linear law in order to emulate ``real" intensity profiles, 
 with the coefficients generated using the ATLAS models and the same methods as the ones used in EJ15 with the 
-Kepler bandpass. The transits were then fitted using free limb-darkening coefficients with the mentioned laws.
+{\em Kepler} bandpass. The transits were then fitted using free limb-darkening coefficients.
 
-For the simulations, the applied strategies in this work to sample physically plausible coefficients from two-parameter laws 
+For the simulations, the applied strategies to sample physically plausible coefficients from two-parameter laws 
 are as follows, all of which use numbers $q_1 \in (0,1)$ and $q_2 \in (0,1)$:
@@
 \end{itemize}
-For the three-parameter law, we use the formalism and codes described in \cite{kipping2015}. As explained before, analyses for the 
-exponential law were not made as it is fundamentally non-physical. The code used to generate these simulations has been published 
-in GitHub\footnote{\url{http://www.github.com/nespinoza/ld-simulations/}}, and can be used to perform analyses in a finer grid to the ones 
+For the three-parameter law, we use the formalism and code described in \cite{kipping2015}.  The code used to generate our simulations is available
+in GitHub\footnote{\url{http://www.github.com/nespinoza/ld-simulations/}}, and can be used to perform analyses in a finer grid than the ones 
 published here.
+
 \subsection{The case of central transits}
@@
 \includegraphics[scale=0.8]{bias_transit_params/all_laws/b_0.0/simulation_b_00_float.eps}
-\caption{Results of fitting transit lightcurves as described in \S 3.1 with the limb-darkening coefficients as free parameters. We only 
-plot the size of the points which represent the input values of $p$.}
+\caption{Results of fitting transit lightcurves as described in \S 3.1 with the limb-darkening coefficients as free parameters. The size of the points is proportional to the the input values of $p$.}
 \label{central_sims}
@@
 
-The results of the simulations for central transits (i.e., $b=0$) are shown in Figure \ref{central_sims}, with the sizes of the points representing the 
-input values of $p$. The upper panels showing the biases 
-introduced on the planet-to-star radius ratio, $p$, and the lower panels showing the biases introduced on the scaled semi-major axes, $a_R$. From left to right, 
-the panels show the biases introduced by using a quadratic law, a logarithmic law, a square-root law and a three-parameter law in the transit fitting 
-procedures leaving the corresponding limb-darkening coefficients as free parameters. The dependence with the input values of $a_R$ are 
-not shown as the bias seem to be almost independent of this parameter in this case (this can be also seen by looking at the lower panels of Figure 10 in EJ15, which 
-give the same results as the ones shown here for the quadratic law, showing a nice agreement between the simulations done with our implementation of 
-the \cite{ma2002} codes for the transit light curve generation and the \texttt{batman} code).
+The results of the simulations for central transits (i.e., $b=0$) are shown in Figure~\ref{central_sims}, with the sizes of the points proportional to the 
+input values of $p$. The upper panels show the biases 
+introduced on the planet-to-star radius ratio, $p$, and the lower panels show the biases introduced on the scaled semi-major axes, $a_R$. From left to right, 
+the panels show the biases introduced by using a quadratic law, a logarithmic law, a square-root law and a three-parameter law. The dependence with the input values of $a_R$ are 
+not shown as the bias seems to be almost independent of this parameter in this case (this can be also seen by looking at the lower panels of Figure~10 in EJ15, which 
+give the same results as the ones shown here for the quadratic law. We note that this implies good agreement between the simulations done with our implementation of 
+the \cite{ma2002} codes for the transit light curve generation and the 
+\texttt{batman} code).
 
 As can be seen from the figure, different limb-darkening laws have different behaviours in retrieving $p$ and $a_R$, with a dependence on the input value of 
-$p$, and also depending on the temperature of its host star. First, it is interesting to note that the logarithmic law does a very good job at retrieving 
+$p$, and also depending on the temperature of the host star. First, it is interesting to note that the logarithmic law does a very good job at retrieving 
 the parameters of small planet-to-star radius ratios, even at the level of the three-parameter law for stars with $T_\textnormal{eff}<6000$ K, and also for medium 
-and large planet-to-star radius ratios with host-stars with $T_\textnormal{eff}<4000$ K (which makes this law perfect for present and future transit 
+and large planet-to-star radius ratios with host-stars with $T_\textnormal{eff}<4000$ K (which makes this law a good choice for present and future transit 
 detection and characterisation around M-dwarfs). The quadratic law, on the other hand, is only the best among the options for host-stars between 
@@
 It is interesting to emphasise that although the biases introduced by the quadratic law might seem to be small, as mentioned in the introduction and in 
-EJ15 they are significant for several candidate and confirmed exoplanets. However, choosing the right law in this case can help to achieve the same 
-level of accuracy than the level of precision that Kepler achieves for most planets. In this case, for example, accuracies on the order of $\sim 0.01\%$ can 
+EJ15 they are significant for several candidate and confirmed exoplanets. Choosing the right law  can help to achieve the same 
+level of accuracy than the level of precision that {\em Kepler} achieves for most planets. For example, accuracies on the order of $\sim 0.01\%$ can 
 be achieved for $p$ with a careful selection of a two-parameter law, and exoplanets with precisions better than that according to a query to the Nasa Exoplanet 
@@
 
-Figures \ref{small_b_sims} and \ref{big_b_sims} show the results for low ($b=0.3$) and high ($b=0.8$) input impact parameters respectively. In these cases, 
+Figures~\ref{small_b_sims} and \ref{big_b_sims} show the results for low ($b=0.3$) and high ($b=0.8$) input impact parameters respectively. In these cases, 
 we see that the biases are in general worse for smaller values of $p$ and $a_R$, i.e., for a given stellar radius, for smaller, close-in planets. We can 
@@
 either the logarithmic or the three-parameter law, which show biases on the order of $\sim 0.1\%$. In contrast, using the quadratic law for transits around 
-those host stars the biases introduced on this parameter are on the order of $\sim 0.75\%$, i.e., almost an order of magnitude improvement in the accuracy.
+those host stars the biases introduced on this parameter are on the order of $\sim 0.75\%$, i.e., almost an order of magnitude larger.
 
 Overall, as expected, the law that retrieves the parameters with minimum bias in low impact-parameter transits is the three-parameter law. However, for 
-high impact-parameter transits of small planets, the logarithmic and square-root law seem to outperform this law in general if the objective is to retrieve 
-a minimum bias estimator for $p$. This is due to the fact that the law is so flexible that it allows for small distortions of the transit lightcurve that, 
-in this case, mimics variations that were actually attributable to $p$, adding a small but important bias on the retrieved parameter. However, for the other 
-parameters ($a_R$ and $i$) this law seems to be the best choice in terms of the achieved accuracy.
+high impact-parameter transits of small planets, the logarithmic and square-root law seem to outperform the three parameter law in general if the objective is to retrieve 
+a minimum bias estimator for $p$. This is due to the fact that the three-parameter law is so flexible that it allows for small distortions of the transit lightcurve that, 
+in this case, can mimic variations that were actually attributable to $p$, adding a small but important bias on the retrieved parameter. However, for the other 
+parameters ($a_R$ and $i$) the three parameter law seems to be the best choice in terms of accuracy.
 
 \section{Discussion \& Conclusions}
-In this work we have explored the different biases on the retrieved transit parameters by the usage of different limb-darkening laws. In particular, we 
-explored the biases introduced by using three two-parameter laws (the quadratic, logarithmic and square-root laws) and the three-parameter law, for which 
-we showed that a careful selection of the limb-darkening law to be used in a given dataset can allow one to retrieve minimum bias estimators for the transit 
-parameters from transit lightcurves. In general, as shown in \S3, these two-parameter laws have ranges in which they perform at the same level or even better 
+
+In this work we have explored the different biases on retrieved transit parameters incurred by the usage of different limb-darkening laws. In particular, we 
+explored the biases introduced by using three two-parameter laws (the quadratic, logarithmic and square-root laws) and the three-parameter law of \citet{sing2009}. 
+We showed that a careful selection of the limb-darkening law to be used in a given dataset can allow one to retrieve minimum bias estimators for the transit 
+parameters from transit lightcurves. In general, as shown in \S3, two-parameter laws have ranges in which they perform at the same level or even better 
 than the three-parameter law and, because of this, we encourage their use. We also discourage the usage of the exponential law which, as shown in \S2.2 is 
@@
 
-The question of \textit{when} to use each of those laws is an important one. In particular, we have explored the relation between the \textit{real}, underlying 
-transit parameters, the stellar host properties and the bias on the retrieved transit parameters, but we have stated no specific rule regarding when to use each 
-law, but only guidelines based on our simulations. This was made on purpose, as the selection of which law to use has to be done in a case-by-case basis, reason 
-by which we provide a code with which one can obtain the results for the same simulations for specific 
+The question of when to use each of those laws is an important one. In particular, we have explored the relation between the real, underlying 
+transit parameters, the stellar host properties and the bias on the retrieved transit parameters. We have stated no specific rule regarding when to use each 
+law, but rather provided only guidelines based on our simulations.
+This is a choice made on purpose, as the selection of which law to use has to be done in a case-by-case basis, reason for which we provide a code with which one can obtain the results of the same simulations for specific
 cases and with different resolutions\footnote{\url{http://www.github.com/nespinoza/ld-simulations/}}. It is important to note that in this work we have used the 
-Kepler bandpass to study the relation between the biases on the retrieved transit parameters and the stellar host properties, but different bandpasses should give 
-rise to slightly different functional relations because they give rise to different model intensity profiles, which are used in those simulations to approximate the 
-expected intensity profile and the adequacy of each limb-darkening law at following it. As such, limb-darkening coefficients have to be calculated for each 
+{\em Kepler} bandpass to study the relation between the biases on the retrieved transit parameters and the stellar host properties, but different bandpasses should give 
+rise to  different functional relations because they give rise to different model intensity profiles, which are used in those simulations to approximate the 
+expected intensity profile and the adequacy of each limb-darkening law at following it. Limb-darkening coefficients have to be calculated for each 
 particular case, which is straightforward to do using the algorithms described in EJ15\footnote{\url{http://www.github.com/nespinoza/limb-darkening/}}.
@@
 MNRAS, 413, 1515.
-%\bibitem[\protect\citeauthoryear{Hebb et al.}{2009}]{Hebb2009} Hebb et al., 2009, ApJ, 693, 1920.
-%\bibitem[\protect\citeauthoryear{Kreidberg et al.}{2013}]{Kreidberg2013} Kreidberg et al., 2013, Nature, 505, 69.
 \bibitem[\protect\citeauthoryear{Klinglesmith \& Sobieski}{1970}]{klinglesmith1970} Klinglesmith, D. A. \&
 Sobieski, S., 1970, AJ, 75, 175.
+\bibitem[\protect\citeauthoryear{Koch et~al.}{2010}]{koch2010} Koch et~al. 2010, ApJ, 713, L79
 \bibitem[\protect\citeauthoryear{Kreidberg}{2015}]{batman2015} Kreidberg, L., 2015, arXiv:1507.08285.
@@
 580, L171.
-%\bibitem[\protect\citeauthoryear{Mandell et al.}{2013}]{Mandell2013} Mandell et al., 2013, ApJ, 779, 128.
 \bibitem[\protect\citeauthoryear{Ricker et al.}{2014}]{ricker2014} Ricker et al., 2014, SPIE, 9143.
@@
 2009, A\&A, 505, 891.
-%\bibitem[\protect\citeauthoryear{Sing et al.}{2013}]{Sing2013} Sing et al., 2013, MNRAS, 436, 2956.
-%\bibitem[\protect\citeauthoryear{Stevenson et al.}{2014}]{Stevenson2014} Stevenson et al., 2014, AJ, 147, 161.
-%\bibitem[\protect\citeauthoryear{Swain et al.}{2013}]{Swain2013} Swain et al., 2013, Icarus, 225, 432.
 \bibitem[\protect\citeauthoryear{Weiss \& Marcy}{2014}]{wm2014} Weiss, L. \& Marcy, G., 2014, ApJ, 783L, 6.
@@
 \end{thebibliography}
-
-%\appendix
-
-%if $e_2<0$, then the profile diverges to $-\infty$ as $\mu\to 0$ (because the term $1-e^\mu$ 
-%tends to 0 from the left) thus not being able to fulfil the constrain of an everywhere positive intensity profile, while for 
-%$e_2>0$ the profile is strictly \textit{increasing} from center to limb, thus not being able to fulfil the constrain of an 
-%everywhere decreasing intensity profile from center to limb.
 

### 2015-11-13 which_law_2_use.tex
Added small changes to the final revised version.

@@
 $^{1}$Instituto de Astrof\'isica, Pontificia Universidad Cat\'olica de Chile, Vicu\~na Mackenna 
-4860, Santiago, Chile
+4860, Santiago, Chile\\
 $^{2}$Millennium Institute of Astrophysics, Santiago, Chile\\
@@
 that the popular and widely used quadratic law is unable to model the complex intensity profile of real stars,  and the biases when fixing the coefficients arise for the
-same reason plus the facts that different methods of fitting the model intensity profiles (transit light curve versus intensity profile fitting) give rise to different limb-darkening coefficients and 
+same reason plus the facts that different methods of fitting the model intensity profiles (including transit light curve versus intensity profile fitting) give rise to different limb-darkening coefficients and
 the fact that we have an imperfect knowledge of the real intensity profiles of stars. We showed that fixing the limb-darkening coefficients is 
@@
 limb-darkening coefficients seems to be a good solution to the accuracy problem, there remains the issue of the low flexibility of the quadratic limb-darkening 
-law which can cause important biases on the retrieved transit parameters as shown in EJ15. These biases can be a large as $\sim 1\%$ for the planet-to-star 
+law which can cause important biases on the retrieved transit parameters as shown in EJ15. These biases can be as large as $\sim 1\%$ for the planet-to-star 
 radius ratio $R_p/R_*$, $\sim 2\%$ for the scaled semi-major axis, $a/R_*$, and $2\%$ for the inclination, where $R_p$ is the planetary radius, $R_*$ 
@@
 the intensity profile of stars. Although the non-linear law proposed by \cite{claret2000} seems to be the most flexible, the fact that it has four free parameters 
-does not make it a very attractive.
+does not make it a very attractive one.
 Several laws with fewer parameters have been proposed.
@@
 Recently, \cite{kipping2015} presented an algorithm to sample parameters from the three-parameter law by imposing physically motivated constraints on the intensity profiles which derived in constrains on the limb-darkening coefficients being fitted.
-cite{kipping2013}, using the same principles, derived an algorithmic way of
+\cite{kipping2013}, using the same principles, derived an algorithmic way of
 doing this for two-parameter laws. He found that his algorithm was not applicable to the exponential law and thus no constrains for this law could 
@@
 of sampling these points with high cadence observations as the ones done by the {\em Kepler} mission and the ones that will 
-be done with the future TESS mission \citep{ricker2014}, which will have an almost certain chance of sampling points with $\mu\approx 1$. 
+be done with the future TESS mission \citep{ricker2014}, which will have an almost certain chance of sampling points with $\mu\lesssim \mu_0$. 
 Furthermore, as the generation of transit lightcurves for laws like the exponential requiere either numerical integration or the usage 
@@
 (1) using the \texttt{batman} transit code described in \cite{batman2015}, (2) using three different two-parameter 
-laws: the quadratic, logarithmic and square-root laws, and the three-parameter law and (3) smaller steps in 
+laws: the quadratic, logarithmic and square-root laws, and the three-parameter law and (3) smaller number of steps in 
 the planet-to-star radius ratio, $p=R_p/R_*$, in order to illustrate the evolution of the biases with this parameter 

### 2016-01-08 first_response_to_referee.txt
Started to write the response to the referee.

Bella Lock (Mrs) 
Assistant Editor, Royal Astronomical Society

Dear Mrs. Bella,

 I am resubmitting the manuscript MNRAS/MN-15-3639-MJ:

 "Limb-darkening and exoplanets II: Choosing the Best 
  Law for Minimum Bias Retrieval of Transit Parameters"

 Authors: Nestor Espinoza & Andres Jordan

 We thank the referee for his/her careful reading of the manuscript. 
 You will find below our detailed response to the referee's comments 
 as indented text after each of his/her comments.

 Besides the changes made in response to the referee's comments we have:

     - Corrected minor typos on the manuscript.

########################################################################################
>> My main suggestion is that the paper would benefit from a more quantitative 
>> description of the trade-off between precision and accuracy. This work indicates 
>> that fitting for two limb darkening coefficients with a judiciously chosen model 
>> can significantly reduce bias. In practice, however, many light curves are not 
>> sufficiently precise to tightly constrain more than one limb darkening parameter. 
>> Adding an additional degree of freedom with a second limb darkening coefficient 
>> may cause the uncertainty on other important parameters, particularly the transit 
>> depth, to blow up. The resulting loss in accuracy may not be worth the improvement 
>> in precision due to choosing a two-parameter model over fitting for  a linear limb 
>> darkening coefficient.
>>
>> One way to address this question is to give guidelines about how precise a 
>> light curve must be to merit adding a second limb darkening parameter to the 
>> model. This could be discussed for a few select examples (e.g., a hot Jupiter 
>> transiting a Sun-like star).  I leave it up to the authors whether/how to address 
>> this point.

RESPONSE

>> It would also be helpful to investigate how much bias is introduced by using a linear 
>> limb darkening law, since this model is commonly used in practice. Again, the authors 
>> can address this at their discretion.

RESPONSE

>> I would recommend adding a few sentences to the abstract to give a little more context 
>> for the paper. For example, something to the effect of: "Very precise measurements of 
>> exoplanet transit light curves enable limb darkening parameters to be fitted empirically, 
>> rather than fixed on theoretical model predictions that may have unknown systematic errors. 
>> However, even fitting for the limb darkening coefficients can introduce bias in the measured 
>> transit parameters depending on the chosen limb darkening model parameterization." I recommend 
>> adding this because because fitting for the coefficients directly is still a relatively new 
>> approach in this field, and it may not be obvious to everyone why you're not just using the 
>> standard nonlinear law.

RESPONSE

>> There are several cases of very precise transit light curves where the limb darkening coefficients 
>> predicted from theoretical models does not provide a good fit to the data (Knutson et al. 2007, ApJ, 
>> 655, 564; Kreidberg et al. 2015, ApJ, 814, 66).  Please cite these in the introduction.

RESPONSE

>> State in the text what time sampling you use for your model light curves, and how sensitive your 
>> results are to the choice of time sampling.

RESPONSE

>> There are a few uneccessary lines in the code run_ld_exosim.py that should be removed:
>>      import pymc
>>      sys.path.append('../utilities/')

RESPONSE

### 2016-01-08 first_response_to_referee.txt
Added responses to some of the referees comments.

@@
 
-RESPONSE
+We thank the referee for this suggestion. We have rewritten the first few sentences in the abstract 
+in order to provide the suggested context to the paper.
 
@@
 
-RESPONSE
+We have added the suggested cites to the discussion in the introduction.
 
@@
 
-RESPONSE
+We thank the referee for catching this typo in the code. The lines have been removed from the code.

### 2016-01-08 which_law_2_use.tex
Added responses to some of the referees comments.

@@
 \begin{abstract}
-The parametrization of the limb-darkening effect of a star has a direct impact 
-on the parameters retrieved from transit lightcurves such as the exoplanet's radius, scaled semi-major axis and inclination.
-Studies of the effect of limb darkening assumptions on the retrieved parameters have mostly focused on the widely used quadratic limb-darkening law, leaving out
-other proposed laws that are in fact better descriptions of model intensity profiles. In this work, we show that 
-laws such as the logarithmic, square-root and three-parameter laws do a better job at retrieving the mentioned parameters from transit 
-lightcurves than the widely used quadratic law and therefore we recommend using those instead.
-We also provide code to guide the decision of when to use each of the laws,  which we note has a dependence on both stellar and transit parameters.
-Finally, we demonstrate that the so-called exponential law is non-physical as it typically produces negative intensities close to the limb and should therefore not be used.
+With the advent of very precise measurements of exoplanet transit lightcurves both from ground and space based observatories, it has been 
+shown that it is now possible to fit the limb-darkening coefficients in the transit-fitting procedure rather than fix them to theoretical values. In 
+addition, this strategy has been shown to give better results as fixing the coefficients to theoretical values can give rise to important yet unknown systematic 
+errors, which directly impact the physical properties of the system derived from such lightcurves such as the exoplanet's radius, scaled 
+semi-major axis and inclination. However, studies of the effect of limb darkening assumptions on the retrieved parameters 
+have mostly focused on the widely used quadratic limb-darkening law, leaving out other proposed laws that are in fact better descriptions 
+of model intensity profiles, which in principle could diminish the bias even further. In this work, we show that laws such as the logarithmic, 
+square-root and three-parameter do a better job in general at retrieving the mentioned parameters from transit lightcurves than the widely 
+used quadratic law and therefore we recommend using those instead. We also provide code to guide the decision of when to use each of 
+the laws,  which we note has a dependence on both stellar and transit parameters. Finally, we demonstrate that the so-called exponential 
+law is non-physical as it typically produces negative intensities close to the limb and should therefore not be used.
 \end{abstract}
@@
 of these measurements due to our imperfect understanding of the limb-darkening effect. In particular, we showed that there are important 
-biases both when fixing and fitting for the limb-darkening coefficients in the light curve fitting process. The biases when fitting for the limb darkening coefficients arise from the fact 
-that the popular and widely used quadratic law is unable to model the complex intensity profile of real stars,  and the biases when fixing the coefficients arise for the
+biases both when fixing and fitting for the limb-darkening coefficients in the light curve fitting process. The biases when fitting for the 
+limb darkening coefficients arise from the fact that the popular and widely used quadratic law is unable to model the complex intensity profile 
+of real stars \citep[which has also been seen on other studies, see, e.g.,][]{knutson2007, kreidberg2015},  and the biases when fixing the coefficients arise for the
 same reason plus the facts that different methods of fitting the model intensity profiles (including transit light curve versus intensity profile fitting) give rise to different limb-darkening coefficients and
@@
 For the three-parameter law, we use the formalism and code described in \cite{kipping2015}.  The code used to generate our simulations is available
-in GitHub\footnote{\url{http://www.github.com/nespinoza/ld-simulations/}}, and can be used to perform analyses in a finer grid than the ones 
+in GitHub\footnote{\url{http://www.github.com/nespinoza/ld-exosim/}}, and can be used to perform analyses in a finer grid than the ones 
 published here.
@@
 This is a choice made on purpose, as the selection of which law to use has to be done in a case-by-case basis, reason for which we provide a code with which one can obtain the results of the same simulations for specific
-cases and with different resolutions\footnote{\url{http://www.github.com/nespinoza/ld-simulations/}}. It is important to note that in this work we have used the 
+cases and with different resolutions\footnote{\url{http://www.github.com/nespinoza/ld-exosim/}}. It is important to note that in this work we have used the 
 {\em Kepler} bandpass to study the relation between the biases on the retrieved transit parameters and the stellar host properties, but different bandpasses should give 
@@
 Sobieski, S., 1970, AJ, 75, 175.
-\bibitem[\protect\citeauthoryear{Koch et~al.}{2010}]{koch2010} Koch et~al. 2010, ApJ, 713, L79
+\bibitem[\protect\citeauthoryear{Knutson et al.}{2007}]{knutson2007} Knutson, H., Charbonneau, D., Noyes, R., et al., 2007, ApJ, 655, 564.
+
+\bibitem[\protect\citeauthoryear{Koch et~al.}{2010}]{koch2010} Koch et~al. 2010, ApJ, 713, L79.
+\bibitem[\protect\citeauthoryear{Kreidberg et al.}{2015}]{kreidberg2015} Kreidberg, L., Line, M., Bean, J., et al., 2015, ApJ, 814, 66.
 \bibitem[\protect\citeauthoryear{Kreidberg}{2015}]{batman2015} Kreidberg, L., 2015, arXiv:1507.08285.

### 2016-01-11 first_response_to_referee.txt
Added additional response. Now working on the rest.

@@
 
-We have added the suggested cites to the discussion in the introduction.
+We have added the suggested citations to the discussion in the introduction.
 
@@
 
-RESPONSE
+We have added the following at the end of the second paragraph in Section 3:
+
+"$1000$ in-transit points and $400$ out-of-transit points were simulated per lightcurve, with the initial 
+times perturbed by a small amount in order for the results to be independent of the exact points at which the lightcurve is sampled 
+(which anyways our simulations show has a negligible effect given the large amount of sampled points)."
 
@@
 
-We thank the referee for catching this typo in the code. The lines have been removed from the code.
+We thank the referee for catching this typo in the code. The lines have been removed from it.

### 2016-01-11 which_law_2_use.tex
Added additional response. Now working on the rest.

@@
 With the advent of very precise measurements of exoplanet transit lightcurves both from ground and space based observatories, it has been 
-shown that it is now possible to fit the limb-darkening coefficients in the transit-fitting procedure rather than fix them to theoretical values. In 
-addition, this strategy has been shown to give better results as fixing the coefficients to theoretical values can give rise to important yet unknown systematic 
+shown that it is now possible to fit the limb-darkening coefficients in the transit-fitting procedure rather than fix them to theoretical values. 
+This strategy has been shown to give better results as fixing the coefficients to theoretical values can give rise to important yet unknown systematic 
 errors, which directly impact the physical properties of the system derived from such lightcurves such as the exoplanet's radius, scaled 
@@
 logarithmic and exponential laws, we now turn to the study of the 
-biases introduced on retrieved transit parameters in the transit fitting process introduced by using different limb-darkening laws. We perform a similar study as the one done in EJ15, but now 
+biases introduced on retrieved transit parameters in the transit fitting process 
+introduced by using different limb-darkening laws. We perform a similar study as the one done in EJ15, but now 
 (1) using the \texttt{batman} transit code described in \cite{batman2015}, (2) using three different two-parameter 
@@
 As in EJ15, we simulate transit lightcurves for planets orbiting host stars with solar metallicity, 
-gravity and microturbulent velocity, and $T_{\rm eff}$ between 3500 K and 9000 K, with the mentioned planet-to-star radius ratios, 
-values of the scaled semi-major axis of 
-$a_R = a/R_* = \{3.27, 3.92, 4.87, 6.45, 9.52, 18.18, 200\}$ and different 
+gravity and microturbulent velocity, and $T_{\rm eff}$ between 3500 K and 9000 K, with the mentioned planet-to-star 
+radius ratios, values of the scaled semi-major axis of $a_R = a/R_* = \{3.27, 3.92, 4.87, 6.45, 9.52, 18.18, 200\}$ and different 
 impact parameters. The transits are simulated using a non-linear law in order to emulate ``real" intensity profiles, 
 with the coefficients generated using the ATLAS models and the same methods as the ones used in EJ15 with the 
-{\em Kepler} bandpass. The transits were then fitted using free limb-darkening coefficients.
+{\em Kepler} bandpass. $1000$ in-transit points and $400$ out-of-transit points were simulated per lightcurve, with the initial 
+times perturbed by a small amount in order for the results to be independent of the exact points at which the lightcurve is sampled 
+(which anyways our simulations show has a negligible effect given the large amount of sampled points). The transits were then fitted 
+using free limb-darkening coefficients.
 

### 2016-01-15 first_response_to_referee.txt
Finished response to the referee. Added two new simulations: one with the linear law, and one on the bias/variance trade-off. Edits and comments are welcome.

@@
 
+     - Changed the title of the manuscript to reflect the additional study 
+       proposed by the referee on the precision of the retrieved transit 
+       parameters, which implies we now not only help to decide the law 
+       that provide minimum bias, but also the one that provides the 
+       best precision. This in turn means that we help to decide the 
+       optimal law, which is a statistical jargon for "lowest bias, 
+       lowest variance" model.
+
+     - Added extra text on the Abstract, Introduction and Section 3 to reflect 
+       these changes in the study. This includes a change of the name of Section 3, 
+       and an additional sub-section explaining the procedures used to study the 
+       bias/variance trade-off.
+
+     - Modified the Acknowledgments.
+
 ########################################################################################
@@
 
-RESPONSE
+We thank the referee for this very insightful suggestion. We have made a whole suit of 
+simulations which exactly answers this question, and provide code so future researchers 
+can decide which is the best law both in terms of bias and precision for their specific 
+application; in this way, researchers can decide the optimal limb-darkening law for the 
+lightcurve at hand. These simulations are shown and discussed both on Section 3.4 and 
+Section 4.
 
@@
 
-RESPONSE
+We thank the referee for making this suggestion. We have added simulations that provide 
+the results for the linear law. As expected, the bias is larger than for any of the other 
+laws, and this is now discussed both in the abstract and in Sections 3 and 4.
 
@@
 
-"$1000$ in-transit points and $400$ out-of-transit points were simulated per lightcurve, with the initial 
-times perturbed by a small amount in order for the results to be independent of the exact points at which the lightcurve is sampled 
-(which anyways our simulations show has a negligible effect given the large amount of sampled points)."
+"$1000$ in-transit points and $400$ out-of-transit points were simulated per 
+lightcurve, with the initial times perturbed by a small amount in order for 
+the results to be independent of the exact points at which the lightcurve is sampled 
+(which anyways our simulations show has a negligible effect given the large amount of 
+sampled points)."
 

### 2016-01-15 which_law_2_use.tex
Finished response to the referee. Added two new simulations: one with the linear law, and one on the bias/variance trade-off. Edits and comments are welcome.

@@
 
-\title[Choosing the best law for minimum bias retrieval of transit parameters]
-{Limb-darkening and exoplanets II: Choosing the Best Law for Minimum Bias Retrieval of Transit Parameters}
+\title[Choosing the best law for optimal retrieval of transit parameters]
+{Limb-darkening and exoplanets II: Choosing the Best Law for Optimal Retrieval of Transit Parameters}
 \author[Espinoza \& Jord\'an ]{
@@
 semi-major axis and inclination. However, studies of the effect of limb darkening assumptions on the retrieved parameters 
-have mostly focused on the widely used quadratic limb-darkening law, leaving out other proposed laws that are in fact better descriptions 
-of model intensity profiles, which in principle could diminish the bias even further. In this work, we show that laws such as the logarithmic, 
-square-root and three-parameter do a better job in general at retrieving the mentioned parameters from transit lightcurves than the widely 
-used quadratic law and therefore we recommend using those instead. We also provide code to guide the decision of when to use each of 
-the laws,  which we note has a dependence on both stellar and transit parameters. Finally, we demonstrate that the so-called exponential 
-law is non-physical as it typically produces negative intensities close to the limb and should therefore not be used.
+have mostly focused on the widely used quadratic limb-darkening law, leaving out other proposed laws that are either simpler (e.g., the linear law) or 
+in fact better descriptions of model intensity profiles, which in principle could diminish the bias even further. In this work, we show that laws such as the 
+logarithmic, square-root and three-parameter do a better job in general at retrieving the mentioned parameters from transit lightcurves both in terms of 
+bias and precision than the widely used quadratic and linear laws and therefore we recommend using those instead. We also provide code to guide the 
+decision of when to use each of these laws,  which we note has a dependence on both stellar and transit parameters. Finally, we demonstrate that the 
+so-called exponential law is non-physical as it typically produces negative intensities close to the limb and should therefore not be used.
 \end{abstract}
@@
 of real stars \citep[which has also been seen on other studies, see, e.g.,][]{knutson2007, kreidberg2015},  and the biases when fixing the coefficients arise for the
-same reason plus the facts that different methods of fitting the model intensity profiles (including transit light curve versus intensity profile fitting) give rise to different limb-darkening coefficients and
-the fact that we have an imperfect knowledge of the real intensity profiles of stars. We showed that fixing the limb-darkening coefficients is 
-the worst option if one aims to obtain precise \textit{and} accurate transit parameters, because the biases arise from three different sources, 
+same reason plus the facts that different methods of fitting the model intensity profiles (including transit light curve versus intensity profile fitting) give rise to 
+different limb-darkening coefficients and the fact that we have an imperfect knowledge of the real intensity profiles of stars. We showed that fixing the limb-darkening 
+coefficients is the worst option if one aims to obtain precise \textit{and} accurate transit parameters, because the biases arise from three different sources, 
 with the last one (the fact that we do not have a perfect modelling of the stellar intensity profiles of real stars) having an unknown but possibly 
@@
 
-Given the above, unless the data quality is really poor (and one is willing to trade bias for variance), there is actually no good reason to fix the limb-darkening coefficients in the transit fitting process (assuming computational resources are not an issue).
-However, although fitting the
+Given the above, unless the data quality is really poor (and one is willing to trade bias for variance), there is actually no good reason to fix the limb-darkening coefficients 
+in the transit fitting process (assuming computational resources are not an issue). However, although fitting the 
 limb-darkening coefficients seems to be a good solution to the accuracy problem, there remains the issue of the low flexibility of the quadratic limb-darkening 
@@
 An obvious solution to the issues mentioned above if one decides to fit the limb-darkening coefficients is to try to use alternative laws to describe 
-the intensity profile of stars. Although the non-linear law proposed by \cite{claret2000} seems to be the most flexible, the fact that it has four free parameters 
-does not make it a very attractive one.
-Several laws with fewer parameters have been proposed.
-Two-parameter laws are the exponential proposed by \cite{claret2003}, the logarithmic proposed by \cite{klinglesmith1970} and the square-root proposed
-by \cite{diazgimenez1992}. In addition, a very flexible three-parameter law was also proposed by \cite{sing2009}. These laws with fewer parameters are potentially 
-very attractive for transit fitting purposes, due to their flexibility at following different intensity profiles  and their low number of parameters \citep[see, e.g., ][for a comparison between the goodness of
-fit to ATLAS model atmospheres of the mentioned two-parameter laws which outperform the linear and quadratic laws in terms of following the intensity 
-profiles]{howarth2011}.
+the intensity profile of stars. Although the non-linear law proposed by \cite{claret2000} seems to be the most flexible, the fact that it has four free 
+parameters does not make it a very attractive one. Several laws with fewer parameters 
+have been proposed. Two-parameter laws are the exponential proposed by \cite{claret2003}, the logarithmic proposed by \cite{klinglesmith1970} and 
+the square-root proposed by \cite{diazgimenez1992}. In addition, a very flexible three-parameter law was also proposed by \cite{sing2009}. These laws 
+with fewer parameters are potentially very attractive for transit fitting purposes, due to their flexibility at following different intensity profiles and their low 
+number of parameters \citep[see, e.g., ][for a comparison between the goodness of fit to ATLAS model atmospheres of the mentioned two-parameter laws 
+which outperform the linear and quadratic laws in terms of following the intensity profiles]{howarth2011}.
 
 Despite the attractive nature of the above mentioned limb-darkening laws, testing their performance at retrieving transit parameters from transit 
-lightcurves was a problem until recently for two reasons.
-First, there was no publicly available code capable of efficiently generating fast and accurate transit lightcurves using all of these non-standard laws.
-However, recently \cite{batman2015} published an
+lightcurves was a problem until recently for two reasons. First, there was no publicly available code capable of efficiently generating fast and accurate 
+transit lightcurves using all of these non-standard laws. However, recently \cite{batman2015} published an 
 algorithm that does exactly this called \texttt{batman}, enabling the generation of transit lightcurves very efficiently with any arbitrary limb-darkening law. 
 The second problem was that it was not clear how to sample limb-darkening coefficients in an informative (i.e., sampling all the physically possible parameter 
-space) and efficient way for all of these laws.
-Recently, \cite{kipping2015} presented an algorithm to sample parameters from the three-parameter law by imposing physically motivated constraints on the intensity profiles which derived in constrains on the limb-darkening coefficients being fitted.
-\cite{kipping2013}, using the same principles, derived an algorithmic way of
-doing this for two-parameter laws. He found that his algorithm was not applicable to the exponential law and thus no constrains for this law could 
-be derived. We note that the form of the logarithmic law used in \cite{kipping2013} differs from the standard one proposed by 
+space) and efficient way for all of these laws. Recently, \cite{kipping2015} presented an algorithm to sample parameters from the three-parameter law by imposing 
+physically motivated constraints on the intensity profiles which derived in constrains on the limb-darkening coefficients being fitted. \cite{kipping2013}, using the 
+same principles, derived an algorithmic way of doing this for two-parameter laws. He found that his algorithm was not applicable to the exponential law and thus 
+no constrains for this law could be derived. We note that the form of the logarithmic law used in \cite{kipping2013} differs from the standard one proposed by 
 \cite{klinglesmith1970}. Thus, in order to  efficiently sample coefficients from the latter limb-darkening law one has to derive an efficient  informative sampling scheme for it.
 
-In this work, we extend the work of EJ15 by testing how well these non-standard laws perform at retrieving transit parameters from transit lightcurves, and compare them to 
-the retrievals done by the standard quadratic limb-darkening law. We follow \cite{kipping2013} in order to derive an efficient sampling scheme 
-for the standard form of the logarithmic and exponential laws, and show that the latter is actually \textit{always} non-physical in the sense proposed by 
-\cite{kipping2013}. Then, we simulate transit lightcurves and perform a simulation study similar to the one done in EJ15 using the derived sampling schemes 
-for the logarithmic law and the sampling schemes detailed in \cite{kipping2013} for the other two-parameter laws and \cite{kipping2015} for the three-parameter law.
-We use our simulations to provide guidance as to when a particular law should be preferred.
+In this work, we test how well these non-standard laws perform at retrieving transit parameters from transit lightcurves. We follow \cite{kipping2013} in order to 
+derive an efficient sampling scheme for the standard form of the logarithmic and exponential laws, and show that the latter is actually \textit{always} non-physical 
+in the sense proposed by \cite{kipping2013}. Then, we simulate transit lightcurves and perform simulations studies which extend the one done in EJ15 in several ways. 
+First, we study not only the accuracy problem but also the precision issue on the retrieved parameters. Second, we study the mentioned non-standard limb-darkening laws by 
+using the derived sampling schemes for the logarithmic law derived in this work, the sampling schemes detailed in \cite{kipping2013} for the other two-parameter laws 
+and \cite{kipping2015} for the three-parameter law. In addition, we also study the performance of the linear law, which has been used in recent years by several authors 
+to parametrize the limb-darkening effect. We use our simulations to provide guidance as to when a particular law should be preferred, and provide code which, given the 
+precision of a given transit lightcurve and a set of transit and stellar parameters, helps to decide which law is the optimal (i.e., with the best bias/variance trade-off) one to use.
 
-This work is organised as follows. In \S2, we revisit the logarithmic and exponential 
-laws in order to derive an efficient informative sampling strategy following the methods in \cite{kipping2013} for the standard forms of these laws. 
-In \S3 we use those results in addition to the ones published by \cite{kipping2013} and \cite{kipping2015} in order to simulate transit lightcurves to test 
-how well these laws perform in retrieving transit parameters. In \S4 we present a discussion and conclusions of our work.
+This work is organised as follows. In \S2, we revisit the logarithmic and exponential laws in order to derive an efficient informative sampling strategy following the methods 
+in \cite{kipping2013} for the standard forms of these laws. In \S3 we use those results in addition to the ones published by \cite{kipping2013} and \cite{kipping2015} in order 
+to simulate transit lightcurves to test how well these laws perform in retrieving transit parameters both in terms of accuracy and precision. In \S4 we present a discussion and 
+conclusions of our work.
 
@@
 Furthermore, as the generation of transit lightcurves for laws like the exponential requiere either numerical integration or the usage 
-of  approximations that usually sample more points close to the limb \citep[which is the case for e.g., the \texttt{batman} code,][]{batman2015}, this law is doomed to produce numerical errors in transit lightcurves due to this fact.
-Because of these reasons, we advise not to use this law.
+of  approximations that usually sample more points close to the limb \citep[which is the case for e.g., the \texttt{batman} code,][]{batman2015}, this 
+law is doomed to produce numerical errors in transit lightcurves due to this fact. Because of these reasons, we advise not to use this law.
 
@@
 
-\section{Biases in transit parameters using two-parameter laws}
+\section{Optimal selection of limb-darkening laws}
+Having dealt with the sampling of limb-darkening coefficients from the 
+logarithmic and exponential laws, we are now ready to turn to the study of the performance 
+of the most popular limb-darkening laws (i.e., the linear, quadratic, logarithmic, square-root and 
+three-parameter laws) both in terms of bias and precision in the 
+retrieval of transit parameters. In particular, we focus on the performance of the retrieval of the planet-to-star 
+radius ratio, $p=R_p/R_*$, the scaled semi-major axis, $a_R = a/R_*$ and the inclination, $i$, from transit lightcurves. 
+In this section, we first study the biases introduced by using different limb-darkening laws, and then we study the 
+bias-variance trade-off between different laws.
 
-Having dealt with the sampling of limb-darkening coefficients from the 
-logarithmic and exponential laws, we now turn to the study of the 
-biases introduced on retrieved transit parameters in the transit fitting process 
-introduced by using different limb-darkening laws. We perform a similar study as the one done in EJ15, but now 
-(1) using the \texttt{batman} transit code described in \cite{batman2015}, (2) using three different two-parameter 
-laws: the quadratic, logarithmic and square-root laws, and the three-parameter law and (3) smaller number of steps in 
-the planet-to-star radius ratio, $p=R_p/R_*$, in order to illustrate the evolution of the biases with this parameter 
-in a cleaner way: small ratios ($p=0.01$), medium ratios ($p=0.07$) and large ones ($p=0.13$).
+\subsection{Biases in the retrieval of transit parameters}
+In order to study the biases introduced by different parametrizations of the limb-darkening effect, we perform a similar study 
+as the one done in EJ15, but now (1) using the \texttt{batman} transit code described in \cite{batman2015}, (2) using the 
+linear law, three different two-parameter laws (the quadratic, logarithmic and square-root laws) and the three-parameter 
+law and (3) using a smaller number of steps in the planet-to-star radius ratio, in order to illustrate the evolution of the biases 
+with this parameter in a cleaner way: we choose to study small ratios ($p=0.01$), medium ratios ($p=0.07$) and large ones 
+($p=0.13$).
 
@@
 gravity and microturbulent velocity, and $T_{\rm eff}$ between 3500 K and 9000 K, with the mentioned planet-to-star 
-radius ratios, values of the scaled semi-major axis of $a_R = a/R_* = \{3.27, 3.92, 4.87, 6.45, 9.52, 18.18, 200\}$ and different 
+radius ratios, values of the scaled semi-major axis of $a_R = \{3.27, 3.92, 4.87, 6.45, 9.52, 18.18, 200\}$ and different 
 impact parameters. The transits are simulated using a non-linear law in order to emulate ``real" intensity profiles, 
 with the coefficients generated using the ATLAS models and the same methods as the ones used in EJ15 with the 
-{\em Kepler} bandpass. $1000$ in-transit points and $400$ out-of-transit points were simulated per lightcurve, with the initial 
-times perturbed by a small amount in order for the results to be independent of the exact points at which the lightcurve is sampled 
-(which anyways our simulations show has a negligible effect given the large amount of sampled points). The transits were then fitted 
-using free limb-darkening coefficients.
+{\em Kepler} bandpass. As in this previous study, $1000$ in-transit points and $400$ out-of-transit points were simulated per 
+lightcurve, with the initial times perturbed by a small amount in order for the results to be independent of the exact points at 
+which the lightcurve is sampled (which anyways our simulations show has a negligible effect given the large amount of sampled 
+points). The transits were then fitted using free limb-darkening coefficients with the different laws mentioned above.
 
@@
 \end{itemize}
-For the three-parameter law, we use the formalism and code described in \cite{kipping2015}.  The code used to generate our simulations is available
-in GitHub\footnote{\url{http://www.github.com/nespinoza/ld-exosim/}}, and can be used to perform analyses in a finer grid than the ones 
-published here.
+For the three-parameter law, we use the formalism and code described in \cite{kipping2015}, while for the linear law we simply 
+sample coefficients between $0$ and $1$, which give intensity profiles which are both always positive and which show a strictly 
+decreasing intensity profiles from center to limb.  The code used to generate our simulations is available in GitHub\footnote{\url{http://www.github.com/nespinoza/ld-exosim/}}, 
+and can be used to perform analyses in a finer grid than the ones published here.
 
-\subsection{The case of central transits}
+\subsubsection{The case of central transits}
 \begin{figure*}
-\includegraphics[scale=0.8]{bias_transit_params/all_laws/b_0.0/simulation_b_00_float.eps}
-\caption{Results of fitting transit lightcurves as described in \S 3.1 with the limb-darkening coefficients as free parameters. The size of the points is proportional to the the input values of $p$.}
+\includegraphics[scale=0.67]{bias_transit_params/all_laws/b_0.0/simulation_b_00_float.eps}
+\caption{Results of fitting transit lightcurves as described in \S 3.1 with the limb-darkening coefficients as free parameters. Note that the scale shown for the linear law is different 
+than the one used in the figures for the other laws. The size of the points is proportional to the the input values of $p$.}
 \label{central_sims}
@@
 The results of the simulations for central transits (i.e., $b=0$) are shown in Figure~\ref{central_sims}, with the sizes of the points proportional to the 
-input values of $p$. The upper panels show the biases 
-introduced on the planet-to-star radius ratio, $p$, and the lower panels show the biases introduced on the scaled semi-major axes, $a_R$. From left to right, 
-the panels show the biases introduced by using a quadratic law, a logarithmic law, a square-root law and a three-parameter law. The dependence with the input values of $a_R$ are 
-not shown as the bias seems to be almost independent of this parameter in this case (this can be also seen by looking at the lower panels of Figure~10 in EJ15, which 
-give the same results as the ones shown here for the quadratic law. We note that this implies good agreement between the simulations done with our implementation of 
-the \cite{ma2002} codes for the transit light curve generation and the 
-\texttt{batman} code).
+input values of $p$. The upper panels show the biases introduced on the planet-to-star radius ratio, $p$, and the lower panels show the biases introduced 
+on the scaled semi-major axes, $a_R$. From left to right, the panels show the biases introduced by using a linear law, a quadratic law, a logarithmic law, a 
+square-root law and a three-parameter law. The dependence with the input values of $a_R$ are not shown as the bias seems to be almost independent of 
+this parameter in this case (this can be also seen by looking at the lower panels of Figure~10 in EJ15, which give the same results as the ones shown here for 
+the quadratic law. We note that this implies good agreement between the simulations done with our implementation of the \cite{ma2002} codes for the transit light 
+curve generation and the \texttt{batman} code).
 
 As can be seen from the figure, different limb-darkening laws have different behaviours in retrieving $p$ and $a_R$, with a dependence on the input value of 
-$p$, and also depending on the temperature of the host star. First, it is interesting to note that the logarithmic law does a very good job at retrieving 
-the parameters of small planet-to-star radius ratios, even at the level of the three-parameter law for stars with $T_\textnormal{eff}<6000$ K, and also for medium 
+$p$, and also depending on the temperature of the host star. First, it is interesting to note that the linear law is by far the worst of the laws in terms of bias. As 
+expected from its very simple form, the biases on the retrieved transit parameters are larger than the ones observed on the two and three-parameter laws for 
+almost all the stellar temperatures except for $T_\textnormal{eff}\sim 4500$, where the profile seems to be a decent (yet poorer than the ones provided by the 
+other laws) approximation to the real intensity profile. A second feature to note on our results is that the logarithmic law does a very good job at retrieving the 
+parameters of small planet-to-star radius ratios, even at the level of the three-parameter law for stars with $T_\textnormal{eff}<6000$ K, and also for medium 
 and large planet-to-star radius ratios with host-stars with $T_\textnormal{eff}<4000$ K (which makes this law a good choice for present and future transit 
@@
 Archive\footnote{Query done on 29/09/2015.} form only $0.58\%$ of all candidate exoplanets and $1.2\%$ of the confirmed exoplanets. For the remaining 
-exoplanets requiring a better accuracy, a new law might have to be created, as this precision is also the limit of the three-parameter law (which has a precision 
+exoplanets requiring a better accuracy, a new law might have to be created, as this is also the limit of the three-parameter law (which has an accuracy 
 on $p$ around $\sim 0.01\%$ for stars with temperatures larger than $T_\textnormal{eff}=6000$ K). Studying new limb-darkening laws, however, 
@@
 
-\subsection{The case of non-central transits}
+\subsubsection{The case of non-central transits}
 \begin{figure*}
-\includegraphics[scale=0.8]{bias_transit_params/all_laws/b_0.3/simulation_b_03_float.eps}
+\includegraphics[scale=0.67]{bias_transit_params/all_laws/b_0.3/simulation_b_03_float.eps}
 \caption{Results of fitting transit lightcurves as described in \S 3.1 with the limb-darkening coefficients as free parameters, but for low impact 
-parameter transits ($b=0.3$). The size of the points represent the input values of $p$, while their color represent the input values of $a_R$.}
+parameter transits ($b=0.3$). Note that the scale shown for the linear law is different than the one used in the figures for the other laws. The 
+size of the points represent the input values of $p$, while their color represent the input values of $a_R$.}
 \label{small_b_sims}
@@
 \begin{figure*}
-\includegraphics[scale=0.8]{bias_transit_params/all_laws/b_0.8/simulation_b_08_float.eps}
+\includegraphics[scale=0.67]{bias_transit_params/all_laws/b_0.8/simulation_b_08_float.eps}
 \caption{Results of fitting transit lightcurves as described in \S 3.1 with the limb-darkening coefficients as free parameters, but for high impact 
-parameter transits ($b=0.8$). The size of the points represent the input values of $p$, while their color represent the input values of $a_R$.}
+parameter transits ($b=0.8$). Note that the scale shown for the linear law is different than the one used in the figures for the other laws. The size 
+of the points represent the input values of $p$, while their color represent the input values of $a_R$.}
 \label{big_b_sims}
@@
 we see that the biases are in general worse for smaller values of $p$ and $a_R$, i.e., for a given stellar radius, for smaller, close-in planets. We can 
-also see that, again, a careful selection of the law to be used can allow one to minimize the biases on the retrieved transit parameters. For example, if 
-the objective were to obtain $p$ with minimum bias for a low impact-parameter transit, then for host stars colder than $4000$ K the best option is to use 
-either the logarithmic or the three-parameter law, which show biases on the order of $\sim 0.1\%$. In contrast, using the quadratic law for transits around 
-those host stars the biases introduced on this parameter are on the order of $\sim 0.75\%$, i.e., almost an order of magnitude larger.
+also see that, again, the worst law to choose in terms of accuracy is the linear, which can give rise to biases on the order of $\sim 3\%$ for small planet-to-star 
+radius ratios. However, it is evident from the results that a careful selection of the law to be used can allow one to minimize the biases on the retrieved transit 
+parameters. For example, if the objective were to obtain $p$ with minimum bias for a low impact-parameter transit, then for host stars colder than $4000$ K 
+the best option is to use either the logarithmic or the three-parameter law, which show biases on the order of $\sim 0.1\%$. In contrast, using the quadratic law 
+for transits around those host stars can give rise to biases on the order of $\sim 0.75\%$, i.e., almost an order of magnitude larger.
 
@@
 
+\subsection{The bias-variance trade-off}
+From the results on the past sub-section, one can see that for a given set of stellar and transit parameters, a law can be chosen in order to minimise the 
+biases in the retrieved transit parameters from the transit light curve. However, an interesting question is whether the precision of a given lightcurve can 
+actually provide one with enough precision in order to use a more complex parametrization of the limb-darkening effect and, depending on the answer, what is 
+the cost. Fitting a complex law to a noisy light curve will definitely lower the precision on the retrieved transit parameters due to the high flexibility of the 
+model (i.e., the large parameter space that it can explore), while fitting a law that is too simple for a very precise lightcurve will most definitely lead to larger 
+biases, due to the strictness of the chosen model. This problem is known as the bias-variance trade-off, i.e., the problem of choosing the right amount of bias 
+and variance for a given dataset. Probabilistically, for a given estimator $\hat{\theta}$ of the parameter $\theta$, we will be interested in its variance (whose 
+square-root defines the precision), $\textnormal{Var}[\hat{\theta}]$, while the bias of the estimator is defined as $\mathbb{E}[\hat{\theta}]-\theta$, where 
+$\mathbb{E}[\cdot]$ defines the expectation value. In this subsection, we will 
+be interested in the ratio of the \textit{absolute value} of the bias over the precision, which we define as
+\begin{eqnarray*}
+\textnormal{Bias/Precision} = \frac{|\mathbb{E}[\hat{\theta}]-\theta|}{\sqrt{\textnormal{Var}[\hat{\theta}]}}
+\end{eqnarray*}
+
+\begin{figure*}
+\includegraphics[scale=0.9]{which_law_to_use/bias_variance_tradeoff.eps}
+\caption{Results of our lightcurve fits to noisy lightcurves of a typical Hot-Jupiter in order to study the bias-variance trade-off of different limb-darkening laws on the planet-to-star radius 
+ratio for lightcurves with $100$ in-transit points. The ratio of the bias to the square-root of the variance (i.e., the precision) of each estimate for different laws is 
+shown as a function of the lightcurve noise level. The line of equal bias and precision is shown as a dashed gray line.}
+\label{biasvariance}
+\end{figure*}
+
+Given that the study of this ratio is complex from a mathematical point of view in this case, we study it through simulations similar to the ones done in the past sub-section, 
+but this time also adding different amounts of noise to the lightcurves. As a case study, we take that of a typical Hot-Jupiter ($p=0.1$, $a_R = 10$) around a Solar-type 
+star ($T_\textnormal{eff}= 5500$ K) on a low impact-parameter orbit ($b=0.3$), and we focus specifically on the retrieval of the planet-to-star radius ratio, which is 
+one of the most interesting parameters retrieved from transit lightcurves. We simulate a suite of lightcurves with noise levels ranging from $10$ ppm to 
+$3000$ ppm with different amount of in-transit points; here, however, we show our results for $N=100$ in-transit points for clarity, which is a worst-case scenario for 
+typical \textit{Kepler} lightcurves, and is a typical case for transit lightcurves obtained from ground-based observatories. For each case, $300$ lightcurves are generated, 
+and all of them are fitted in the same way as it was done for their noiseless counterparts in the past sub-section. From the fit to each of the $300$ lightcurves on each case, 
+the precision of the planet-to-star radius ratio is estimated by calculating the square-root of the variance of all the retrieved planet-to-star radius ratio of each of the $300$ lightcurves. 
+The results of our simulations are shown on Figure \ref{biasvariance}, where we plot the ratio of the absolute value of the bias (estimated in the previous sub-section) over the precision 
+(the square-root of the variance of the estimator) as a function of the noise in the simulated lightcurves.
+
+In our results, the line of equal bias and precision marks the limit at which one should switch to a more complex law. For example, in our simulation, the linear law touches this line at 
+$\sim 500$ ppm, which means that for more precise lightcurves the bias on the planet-to-star radius ratio is larger than the precision (e.g., for a lightcurve with a precision of $\sim 200$ 
+ppm, the bias is $\sim 2$ times larger than the precision on the parameter) and, therefore, one should switch to a more complex law. To which law should one switch? From Figure \ref{biasvariance}, 
+it can be seen that between $\sim 50-500$ ppm, the best law in terms of bias/variance trade-off is the square-root law which, among all the laws that are below the equal bias and precision line, 
+provides the best precision. For lightcurve precisions better than $\sim 50$ ppm, it can be seen that the square-root law crosses this line and therefore another law must be used, which can be 
+selected in the same way as before (in this case, between $\sim 30-50$ ppm, the optimal decision would be to use the logarithmic law). For this specific case, it can be seen that the 
+three-parameter law is only optimal for precision better than $\sim 20$ ppm. Of course, if one increases the number of in-transit points, the precisions at which each law crosses the equal bias 
+and precision line are lower. For example, we find that for $N=500$, the linear law touches this line at $\sim 800$ ppm, while for $N=1000$, 
+the linear law touches this line at $\sim 1000$ ppm.
+
+From our case study, it can be seen that the selection of the optimal limb-darkening law (i.e., the one that provides the best precision among the ones that avoid biases larger than it) can be 
+estimated by simple simulation. We provide code at Github with which this can be easily done for a given set of transit and stellar parameters, along with a given lightcurve noise level and number of 
+in-transit points.
+
 \section{Discussion \& Conclusions}
 
-In this work we have explored the different biases on retrieved transit parameters incurred by the usage of different limb-darkening laws. In particular, we 
-explored the biases introduced by using three two-parameter laws (the quadratic, logarithmic and square-root laws) and the three-parameter law of \citet{sing2009}. 
-We showed that a careful selection of the limb-darkening law to be used in a given dataset can allow one to retrieve minimum bias estimators for the transit 
-parameters from transit lightcurves. In general, as shown in \S3, two-parameter laws have ranges in which they perform at the same level or even better 
-than the three-parameter law and, because of this, we encourage their use. We also discourage the usage of the exponential law which, as shown in \S2.2 is 
-unphysical, and can lead to numerical errors if used on real data where sampling of points close to the limb (where the law diverges) is not uncommon.
+In this work we have explored the different biases and precisions on retrieved transit parameters incurred by the usage of different limb-darkening laws. In particular, we 
+explored the biases introduced by using the linear law, three two-parameter laws (the quadratic, logarithmic and square-root laws) and the three-parameter law of \citet{sing2009}, 
+and defined a way to select the optimal law for a given lightcurve precision and number of in-transit points. We showed that a careful selection of the limb-darkening law to be 
+used in a given dataset can allow one to retrieve optimal estimators for the transit parameters from transit lightcurves. In general, as shown in \S3, two-parameter laws have ranges 
+in which they perform at the same level or even better than the three-parameter law and, because of this, we encourage their use. We also discourage the usage of the exponential 
+law which, as shown in \S2.2 is unphysical, and can lead to numerical errors if used on real data where sampling of points close to the limb (where the law diverges) is not uncommon.
 
 The question of when to use each of those laws is an important one. In particular, we have explored the relation between the real, underlying 
-transit parameters, the stellar host properties and the bias on the retrieved transit parameters. We have stated no specific rule regarding when to use each 
-law, but rather provided only guidelines based on our simulations.
-This is a choice made on purpose, as the selection of which law to use has to be done in a case-by-case basis, reason for which we provide a code with which one can obtain the results of the same simulations for specific
+transit parameters, the stellar host properties and the bias/variance on the retrieved transit parameters. We have stated no specific rule regarding when to use each 
+law, but rather provided only guidelines based on our simulations. This is a choice made on purpose, as the selection of which law to use has to be done in a 
+case-by-case basis, reason for which we provide code with which one can obtain the results of the same simulations performed on our work for specific 
 cases and with different resolutions\footnote{\url{http://www.github.com/nespinoza/ld-exosim/}}. It is important to note that in this work we have used the 
-{\em Kepler} bandpass to study the relation between the biases on the retrieved transit parameters and the stellar host properties, but different bandpasses should give 
+{\em Kepler} bandpass to study the relation between the biases/variances on the retrieved transit parameters and the stellar host properties, but different bandpasses should give 
 rise to  different functional relations because they give rise to different model intensity profiles, which are used in those simulations to approximate the 

### 2016-01-15 bias_transit_params/all_laws/b_0.0/old_plot_simulation_data.py

@@ -28,10 +28,6 @@ p_show = [0.01,0.07,0.13]
 fit_option = 'float'
 
 # Get the results:
-grid_num_tpl, p_tpl, a_tpl, input_teff_tpl, p_fixed_tpl, sigma_p_fixed_tpl, p_float_tpl, sigma_p_float_tpl, \
-                a_fixed_tpl, sigma_a_fixed_tpl, a_float_tpl, sigma_a_float_tpl,i_fixed_tpl, sigma_i_fixed_tpl, i_float_tpl, sigma_i_float_tpl \
-                = np.loadtxt('threeparam_results/final_results.dat',unpack=True)
-
 grid_num_log, p_log, a_log, input_teff_log, p_fixed_log, sigma_p_fixed_log, p_float_log, sigma_p_float_log, \
                 a_fixed_log, sigma_a_fixed_log, a_float_log, sigma_a_float_log,i_fixed_log, sigma_i_fixed_log, i_float_log, sigma_i_float_log \
                 = np.loadtxt('logarithmic_results/final_results.dat',unpack=True)
@@ -44,10 +40,6 @@ grid_num_quad, p_quad, a_quad, input_teff_quad, p_fixed_quad, sigma_p_fixed_quad
                 a_fixed_quad, sigma_a_fixed_quad, a_float_quad, sigma_a_float_quad,i_fixed_quad, sigma_i_fixed_quad, i_float_quad, sigma_i_float_quad \
                 = np.loadtxt('quadratic_results/final_results.dat',unpack=True)
 
-grid_num_lin, p_lin, a_lin, input_teff_lin, p_fixed_lin, sigma_p_fixed_lin, p_float_lin, sigma_p_float_lin, \
-                a_fixed_lin, sigma_a_fixed_lin, a_float_lin, sigma_a_float_lin,i_fixed_lin, sigma_i_fixed_lin, i_float_lin, sigma_i_float_lin \
-                = np.loadtxt('linear_results/final_results.dat',unpack=True)
-
 # Order the results from largest to smallest p (in order to have the smallest points on top of larger ones):
 variables = ['grid_num_', 'p_', 'a_', 'input_teff_', 'p_'+fit_option+'_', 'sigma_p_'+fit_option+'_', 
                                 'a_'+fit_option+'_', 'sigma_a_'+fit_option+'_', 'i_'+fit_option+'_', 'sigma_i_'+fit_option+'_']
[…]

### 2016-01-15 bias_transit_params/all_laws/b_0.3/old_plot_simulation_data.py

@@ -20,10 +20,10 @@ def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
     x0,y0 = g.pos(x_coord, y_coord)
     g.text(x0,y0,text_input,textattrs)
 
-b = 0.0
-ytext = 0.35
+b = 0.3
+ytext = 0.65
 p_scale = 0.1
-p_scale2 = 2.5
+p_scale2 = 3.
 p_show = [0.01,0.07,0.13]
 fit_option = 'float'
 
@@ -44,10 +44,6 @@ grid_num_quad, p_quad, a_quad, input_teff_quad, p_fixed_quad, sigma_p_fixed_quad
                 a_fixed_quad, sigma_a_fixed_quad, a_float_quad, sigma_a_float_quad,i_fixed_quad, sigma_i_fixed_quad, i_float_quad, sigma_i_float_quad \
                 = np.loadtxt('quadratic_results/final_results.dat',unpack=True)
 
-grid_num_lin, p_lin, a_lin, input_teff_lin, p_fixed_lin, sigma_p_fixed_lin, p_float_lin, sigma_p_float_lin, \
-                a_fixed_lin, sigma_a_fixed_lin, a_float_lin, sigma_a_float_lin,i_fixed_lin, sigma_i_fixed_lin, i_float_lin, sigma_i_float_lin \
-                = np.loadtxt('linear_results/final_results.dat',unpack=True)
-
 # Order the results from largest to smallest p (in order to have the smallest points on top of larger ones):
 variables = ['grid_num_', 'p_', 'a_', 'input_teff_', 'p_'+fit_option+'_', 'sigma_p_'+fit_option+'_', 
                                 'a_'+fit_option+'_', 'sigma_a_'+fit_option+'_', 'i_'+fit_option+'_', 'sigma_i_'+fit_option+'_']
@@ -56,9 +52,9 @@ variables = ['grid_num_', 'p_', 'a_', 'input_teff_', 'p_'+fit_option+'_', 'sigma
 # Now plot. First, some options:
 pheight = 3#5
 pwidth = 4#6.5
-delta_x = 5.0/1.2#9
+delta_x = 5.0#9
 delta_y = 1.0
-unit.set(xscale = 1.0)
+unit.set(xscale = 0.8)
 text.set(mode="latex")
 text.preamble(r"\usepackage{color}")
[…]

### 2016-01-15 bias_transit_params/all_laws/b_0.3/plot_simulation_data.py

@@ -44,6 +44,10 @@ grid_num_quad, p_quad, a_quad, input_teff_quad, p_fixed_quad, sigma_p_fixed_quad
                 a_fixed_quad, sigma_a_fixed_quad, a_float_quad, sigma_a_float_quad,i_fixed_quad, sigma_i_fixed_quad, i_float_quad, sigma_i_float_quad \
                 = np.loadtxt('quadratic_results/final_results.dat',unpack=True)
 
+grid_num_lin, p_lin, a_lin, input_teff_lin, p_fixed_lin, sigma_p_fixed_lin, p_float_lin, sigma_p_float_lin, \
+                a_fixed_lin, sigma_a_fixed_lin, a_float_lin, sigma_a_float_lin,i_fixed_lin, sigma_i_fixed_lin, i_float_lin, sigma_i_float_lin \
+                = np.loadtxt('linear_results/final_results.dat',unpack=True)
+
 # Order the results from largest to smallest p (in order to have the smallest points on top of larger ones):
 variables = ['grid_num_', 'p_', 'a_', 'input_teff_', 'p_'+fit_option+'_', 'sigma_p_'+fit_option+'_', 
                                 'a_'+fit_option+'_', 'sigma_a_'+fit_option+'_', 'i_'+fit_option+'_', 'sigma_i_'+fit_option+'_']
@@ -52,9 +56,9 @@ variables = ['grid_num_', 'p_', 'a_', 'input_teff_', 'p_'+fit_option+'_', 'sigma
 # Now plot. First, some options:
 pheight = 3#5
 pwidth = 4#6.5
-delta_x = 5.0#9
+delta_x = 5.0/1.2#9
 delta_y = 1.0
-unit.set(xscale = 0.8)
+unit.set(xscale = 1.0)
 text.set(mode="latex")
 text.preamble(r"\usepackage{color}")
 text.preamble(r"\usepackage{wasysym}")
@@ -65,11 +69,17 @@ xaxis = r'Host star $T_{\rm{eff}}$ (K)'
 min_x = 3200.0
 max_x = 9000.0
 min_y_p = -0.5#-10
-max_y_p = 1#1
-min_y_a = -3.3#-2
-max_y_a = 2.3#15
-min_y_i = -2.3
-max_y_i = 1.3
+max_y_p = 3.5#1
[…]

### 2016-01-15 bias_transit_params/all_laws/b_0.8/plot_simulation_data.py

@@ -44,6 +44,10 @@ grid_num_quad, p_quad, a_quad, input_teff_quad, p_fixed_quad, sigma_p_fixed_quad
                 a_fixed_quad, sigma_a_fixed_quad, a_float_quad, sigma_a_float_quad,i_fixed_quad, sigma_i_fixed_quad, i_float_quad, sigma_i_float_quad \
                 = np.loadtxt('quadratic_results/final_results.dat',unpack=True)
 
+grid_num_lin, p_lin, a_lin, input_teff_lin, p_fixed_lin, sigma_p_fixed_lin, p_float_lin, sigma_p_float_lin, \
+                a_fixed_lin, sigma_a_fixed_lin, a_float_lin, sigma_a_float_lin,i_fixed_lin, sigma_i_fixed_lin, i_float_lin, sigma_i_float_lin \
+                = np.loadtxt('linear_results/final_results.dat',unpack=True)
+
 # Order the results from largest to smallest p (in order to have the smallest points on top of larger ones):
 variables = ['grid_num_', 'p_', 'a_', 'input_teff_', 'p_'+fit_option+'_', 'sigma_p_'+fit_option+'_', 
                                 'a_'+fit_option+'_', 'sigma_a_'+fit_option+'_', 'i_'+fit_option+'_', 'sigma_i_'+fit_option+'_']
@@ -52,9 +56,9 @@ variables = ['grid_num_', 'p_', 'a_', 'input_teff_', 'p_'+fit_option+'_', 'sigma
 # Now plot. First, some options:
 pheight = 3#5
 pwidth = 4#6.5
-delta_x = 5.0#9
+delta_x = 5.0/1.2#9
 delta_y = 1.0
-unit.set(xscale = 0.8)
+unit.set(xscale = 1.0)
 text.set(mode="latex")
 text.preamble(r"\usepackage{color}")
 text.preamble(r"\usepackage{wasysym}")
@@ -65,11 +69,17 @@ xaxis = r'Host star $T_{\rm{eff}}$ (K)'
 min_x = 3200.0
 max_x = 9000.0
 min_y_p = -1.0#-10
-max_y_p = 0.5#1
-min_y_a = -2.0#-2
-max_y_a = 0.5#15
-min_y_i = -0.5
+max_y_p = 3.2#1
+max_y_p_2 = 0.5
[…]

### 2016-01-15 which_law_to_use/analysis.py

@@ -1,0 +1,130 @@
+# -*- coding: utf-8 -*-
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+import numpy as np
+from pyx import text as pyx_text
+from pyx import trafo
+def text_pyx(g, x_coord, y_coord, text_input, text_size = -2, color = None, rotation = 0.):
+    """
+    Function that draws text in a given plot
+    INPUTS:
+        g       (Object) A graph-type object to which you want to add the text
+        x_coord     (Double) x-coordinate (in plot units) at which you want to place
+                the text
+        y_coord     (Double) y-coordinate (in plot units) at which you want to place
+                the text
+        text_input  (String) Text that you want to add.
+        text_size   (int, optional) Text size of the text added to the plot. Default is -2.
+        color       (instance) Color instance that defines the color that you want the 
+                text to have. Default is black.
+    """
+
+    # First define the text attributes:
+    textattrs = [pyx_text.size(text_size),pyx_text.halign.center, pyx_text.vshift.middlezero, trafo.rotate(rotation)]
+
+    # Now convert plot positions to pyx's:
+    x0,y0 = g.pos(x_coord, y_coord)
+
+    # If no color is given, draw black text. If color is given, draw text with the input color:
+    if color is None:
+        g.text(x0,y0,text_input,textattrs)
+    else:
+        # First, check which was the input color palette:
+        color_dict = color.color
+        if len(color_dict.keys()) == 4:
+            color_string = str(color_dict['c'])+','+str(color_dict['m'])+','+str(color_dict['y'])+','+str(color_dict['k'])
+            color_palette = 'cmyk'
+        else:
+                        color_string = str(color_dict['r'])+','+str(color_dict['g'])+','+str(color_dict['b'])
+                        color_palette = 'rgb'
+        # Now draw the text:
+        g.text(x0, y0, r"\textcolor["+color_palette+"]{"+color_string+"}{"+text_input+"}",textattrs)
+
+from pyx import *
+results = '/Users/nespinoza/github/ld-exosim/results/sic/'
+ld_laws = ['linear','quadratic','squareroot','logarithmic','three-param']
[…]

### 2016-01-17 which_law_2_use.tex
Added an extra plot at the bias-variance trade-off discussion, along with the N = 1000 line on the simulation plot. Extra discussions regarding those plots were added too.

@@
 \subsection{The bias-variance trade-off}
+\begin{figure}
+\includegraphics[scale=0.73]{which_law_to_use/bias_variance_plot.eps}
+\caption{Sketch of each of the terms that define the bias and the precision of a given estimator. The probability density of the estimator $\hat{theta}$ of 
+the parameter $\theta$ is depicted in red, while the real, underlying value of the parameter $\theta$ is depicted with a black solid line. Ideally, one would 
+want a low bias, high precision estimator.}
+\label{bias-variance-plot}
+\end{figure}
+
 From the results on the past sub-section, one can see that for a given set of stellar and transit parameters, a law can be chosen in order to minimise the 
@@
 and variance for a given dataset. Probabilistically, for a given estimator $\hat{\theta}$ of the parameter $\theta$, we will be interested in its variance (whose 
-square-root defines the precision), $\textnormal{Var}[\hat{\theta}]$, while the bias of the estimator is defined as $\mathbb{E}[\hat{\theta}]-\theta$, where 
-$\mathbb{E}[\cdot]$ defines the expectation value. In this subsection, we will 
-be interested in the ratio of the \textit{absolute value} of the bias over the precision, which we define as
+square-root defines the precision), $\textnormal{Var}[\hat{\theta}]$, and its bias, defined as $\mathbb{E}[\hat{\theta}]-\theta$, where 
+$\mathbb{E}[\cdot]$ defines the expectation value and $\textnormal{Var}[\cdot]$ is the variance operator. Intuitively, one would want a low-bias and 
+high-precision (i.e., low variance) estimator for a given parameter; Figure \ref{bias-variance-plot} sketches each of those terms graphically. In this subsection, 
+we will be interested in the ratio of the \textit{absolute value} of the bias over the precision, which we define as
 \begin{eqnarray*}
-\textnormal{Bias/Precision} = \frac{|\mathbb{E}[\hat{\theta}]-\theta|}{\sqrt{\textnormal{Var}[\hat{\theta}]}}
+\textnormal{Bias/Precision} = \frac{|\mathbb{E}[\hat{\theta}]-\theta|}{\sqrt{\textnormal{Var}[\hat{\theta}]}}.
 \end{eqnarray*}
@@
 Given that the study of this ratio is complex from a mathematical point of view in this case, we study it through simulations similar to the ones done in the past sub-section, 
-but this time also adding different amounts of noise to the lightcurves. As a case study, we take that of a typical Hot-Jupiter ($p=0.1$, $a_R = 10$) around a Solar-type 
-star ($T_\textnormal{eff}= 5500$ K) on a low impact-parameter orbit ($b=0.3$), and we focus specifically on the retrieval of the planet-to-star radius ratio, which is 
-one of the most interesting parameters retrieved from transit lightcurves. We simulate a suite of lightcurves with noise levels ranging from $10$ ppm to 
-$3000$ ppm with different amount of in-transit points; here, however, we show our results for $N=100$ in-transit points for clarity, which is a worst-case scenario for 
-typical \textit{Kepler} lightcurves, and is a typical case for transit lightcurves obtained from ground-based observatories. For each case, $300$ lightcurves are generated, 
+but this time also adding different amounts of noise to the lightcurves. In this sense, we take a Monte Carlo approach in order to study this ratio. As a case study, we take that 
+of a typical Hot-Jupiter ($p=0.1$, $a_R = 10$) around a Solar-type star ($T_\textnormal{eff}= 5500$ K) on a low impact-parameter orbit ($b=0.3$), and we focus specifically 
+on the retrieval of the planet-to-star radius ratio, which is one of the most interesting parameters retrieved from transit lightcurves. We simulate a suite of lightcurves with noise 
+levels ranging from $10$ ppm to $3000$ ppm with different amount of in-transit points; here, however, we show our results for $N=100$ and $N=1000$ in-transit points for clarity, 
+which span a range of possible scenarios for both space based (e.g., \textit{Kepler}) and ground-based observations. For each case, $300$ lightcurves are generated, 
 and all of them are fitted in the same way as it was done for their noiseless counterparts in the past sub-section. From the fit to each of the $300$ lightcurves on each case, 
-the precision of the planet-to-star radius ratio is estimated by calculating the square-root of the variance of all the retrieved planet-to-star radius ratio of each of the $300$ lightcurves. 
-The results of our simulations are shown on Figure \ref{biasvariance}, where we plot the ratio of the absolute value of the bias (estimated in the previous sub-section) over the precision 
+we take all the estimated planet-to-star radius ratios and estimate the precision by calculating the square-root of the variance of the sample. The results of our simulations are shown 
+on Figure \ref{biasvariance}, where we plot the ratio of the absolute value of the bias (estimated in the previous sub-section) over the precision 
 (the square-root of the variance of the estimator) as a function of the noise in the simulated lightcurves.
 
-In our results, the line of equal bias and precision marks the limit at which one should switch to a more complex law. For example, in our simulation, the linear law touches this line at 
-$\sim 500$ ppm, which means that for more precise lightcurves the bias on the planet-to-star radius ratio is larger than the precision (e.g., for a lightcurve with a precision of $\sim 200$ 
+In our results, the line of equal bias and precision marks the limit at which one should switch to a more complex law. For example, in our simulation, for $N=100$ in-transit points, the 
+linear law touches this line at $\sim 500$ ppm, which means that for more precise lightcurves the bias on the planet-to-star radius ratio is larger than the precision (e.g., for a lightcurve with a precision of $\sim 200$
 ppm, the bias is $\sim 2$ times larger than the precision on the parameter) and, therefore, one should switch to a more complex law. To which law should one switch? From Figure \ref{biasvariance}, 
-it can be seen that between $\sim 50-500$ ppm, the best law in terms of bias/variance trade-off is the square-root law which, among all the laws that are below the equal bias and precision line, 
-provides the best precision. For lightcurve precisions better than $\sim 50$ ppm, it can be seen that the square-root law crosses this line and therefore another law must be used, which can be 
-selected in the same way as before (in this case, between $\sim 30-50$ ppm, the optimal decision would be to use the logarithmic law). For this specific case, it can be seen that the 
-three-parameter law is only optimal for precision better than $\sim 20$ ppm. Of course, if one increases the number of in-transit points, the precisions at which each law crosses the equal bias 
-and precision line are lower. For example, we find that for $N=500$, the linear law touches this line at $\sim 800$ ppm, while for $N=1000$, 
-the linear law touches this line at $\sim 1000$ ppm.
+it can be seen that between $\sim 50-500$ ppm, the best law in terms of bias/variance trade-off for this number of in-transit points is the square-root law which, among all the laws that are below 
+the equal bias and precision line, provides the best precision.
+For lightcurve precisions better than $\sim 50$ ppm, it can be seen that the square-root law crosses this line and therefore another law
+must be used, which can be selected in the same way as before (in this case, between $\sim 30-50$ ppm, the optimal decision would be to use the logarithmic law).
+For this specific case, it can be seen that the
+three-parameter law is only optimal for precision better than $\sim 20$ ppm.
+Of course, as can be seen from the plot, if one increases the number of in-transit points, the precisions at which each law crosses the
+equal bias and precision line are lower.
+For example, for $N=1000$, it can be seen that the linear law touches this line at $\sim 1500$ ppm, meaning that in this case even with a very noisy lightcurve one has to
+switch to a better limb-darkening law if one wants to keep the bias below the precision level.
 

### 2016-01-17 which_law_to_use/analysis.py

@@ -106,6 +106,18 @@ g.plot(graph.data.values(x=[1.,1e4],y=[1.,1.], title = None),\
                              styles = [graph.style.line([color.cmyk.Grey,\
                                        style.linestyle.dashed,\
                                        style.linewidth.thin])])
+
+# Plot fake lines to put labels:
+g.plot(graph.data.values(x=[5000,10000],y=[1,1], title = '100 in-transit points'),\
+                styles = [graph.style.line([color.cmyk.Black,\
+                style.linestyle.solid,\
+                style.linewidth.THick])])
+
+g.plot(graph.data.values(x=[5000,10000],y=[1,1], title = '1000 in-transit points'),\
+                styles = [graph.style.line([color.cmyk.Black,\
+                style.linestyle.dashed,\
+                style.linewidth.thick])])
+
 for i in range(len(ld_laws)):
     ld_law = ld_laws[i]
     g.plot(graph.data.values(x=precisions,y=np.abs(data[ld_law]['100']['bias_p']/data[ld_law]['100']['precision_p']), title = None),\
@@ -120,10 +132,10 @@ for i in range(len(ld_laws)):
     #                                   style.linestyle.dashed,\
     #                                   style.linewidth.thick])])
 
-    #g.plot(graph.data.values(x=precisions,y=np.abs(data[ld_law]['1000']['bias_p']/data[ld_law]['1000']['precision_p']), title = None),\
-    #                         styles = [graph.style.line([colors[i],\
-    #                                   style.linestyle.dashed,\
-    #                                   style.linewidth.thick])])
+    g.plot(graph.data.values(x=precisions,y=np.abs(data[ld_law]['1000']['bias_p']/data[ld_law]['1000']['precision_p']), title = None),\
+                             styles = [graph.style.line([colors[i],\
+                                       style.linestyle.dashed,\
+                                       style.linewidth.thick])])
 
 #text_pyx(g, , 2000., names[i])
 c.writeEPSfile(outname,write_mesh_as_bitmap = True,write_mesh_as_bitmap_resolution=5)

### 2016-01-17 which_law_to_use/bias_variance_plot.py

@@ -1,0 +1,119 @@
+# -*- coding: utf-8 -*-
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+import numpy as np
+from pyx import text as pyx_text
+from pyx import trafo
+def text_pyx(g, x_coord, y_coord, text_input, text_size = -2, color = None, rotation = 0.):
+    """
+    Function that draws text in a given plot
+    INPUTS:
+        g       (Object) A graph-type object to which you want to add the text
+        x_coord     (Double) x-coordinate (in plot units) at which you want to place
+                the text
+        y_coord     (Double) y-coordinate (in plot units) at which you want to place
+                the text
+        text_input  (String) Text that you want to add.
+        text_size   (int, optional) Text size of the text added to the plot. Default is -2.
+        color       (instance) Color instance that defines the color that you want the 
+                text to have. Default is black.
+    """
+
+    # First define the text attributes:
+    textattrs = [pyx_text.size(text_size),pyx_text.halign.center, pyx_text.vshift.middlezero, trafo.rotate(rotation)]
+
+    # Now convert plot positions to pyx's:
+    x0,y0 = g.pos(x_coord, y_coord)
+
+    # If no color is given, draw black text. If color is given, draw text with the input color:
+    if color is None:
+        g.text(x0,y0,text_input,textattrs)
+    else:
+        # First, check which was the input color palette:
+        color_dict = color.color
+        if len(color_dict.keys()) == 4:
+            color_string = str(color_dict['c'])+','+str(color_dict['m'])+','+str(color_dict['y'])+','+str(color_dict['k'])
+            color_palette = 'cmyk'
+        else:
+                        color_string = str(color_dict['r'])+','+str(color_dict['g'])+','+str(color_dict['b'])
+                        color_palette = 'rgb'
+        # Now draw the text:
[…]

### 2016-01-18 which_law_2_use.tex
Modified draft in order to reflect the usage of the MSE metric.

@@
 in fact better descriptions of model intensity profiles, which in principle could diminish the bias even further. In this work, we show that laws such as the 
-logarithmic, square-root and three-parameter do a better job in general at retrieving the mentioned parameters from transit lightcurves both in terms of 
-bias and precision than the widely used quadratic and linear laws and therefore we recommend using those instead. We also provide code to guide the 
-decision of when to use each of these laws,  which we note has a dependence on both stellar and transit parameters. Finally, we demonstrate that the 
+logarithmic, square-root and three-parameter do a better job at retrieving the mentioned parameters from transit lightcurves both in terms of 
+bias and precision for a wide range of situations than the widely used quadratic and linear laws and therefore we recommend to study which one to 
+use on a case-by-case basis. We also provide code to guide the decision of when to use each of these laws and select the optimal one in a 
+mean-square error sense, which we note has a dependence on both stellar and transit parameters. Finally, we demonstrate that the 
 so-called exponential law is non-physical as it typically produces negative intensities close to the limb and should therefore not be used.
@@
 \includegraphics[scale=0.73]{which_law_to_use/bias_variance_plot.eps}
-\caption{Sketch of each of the terms that define the bias and the precision of a given estimator. The probability density of the estimator $\hat{theta}$ of 
+\caption{Sketch of each of the terms that define the bias and the precision of a given estimator. The probability density of the estimator $\hat{\theta}$ of 
 the parameter $\theta$ is depicted in red, while the real, underlying value of the parameter $\theta$ is depicted with a black solid line. Ideally, one would 
@@
 
-From the results on the past sub-section, one can see that for a given set of stellar and transit parameters, a law can be chosen in order to minimise the 
+From the results on the past sub-section, one can see that for a given set of stellar and transit parameters, a law can be chosen in order to minimize the 
 biases in the retrieved transit parameters from the transit light curve. However, an interesting question is whether the precision of a given lightcurve can 
@@
 square-root defines the precision), $\textnormal{Var}[\hat{\theta}]$, and its bias, defined as $\mathbb{E}[\hat{\theta}]-\theta$, where 
-$\mathbb{E}[\cdot]$ defines the expectation value and $\textnormal{Var}[\cdot]$ is the variance operator. Intuitively, one would want a low-bias and 
-high-precision (i.e., low variance) estimator for a given parameter; Figure \ref{bias-variance-plot} sketches each of those terms graphically. In this subsection, 
-we will be interested in the ratio of the \textit{absolute value} of the bias over the precision, which we define as
+$\mathbb{E}[\cdot]$ defines the expectation value and $\textnormal{Var}[\cdot]$ is the variance operator. The bias, on one hand, defines how far on average is 
+the estimator from the parameters' true value, while the variance defines the spread around the expected value of the estimator (see Figure \ref{bias-variance-plot}). 
+In this sense, one would ideally want a low-bias and high-precision (i.e. low variance) estimator, which is both close to the real value of the parameter on average and, 
+at the same time, has a low spread around such value. The problem is that in real applications one has the possibility to choose from various estimators with different 
+ammounts of bias and variance, and thus choosing among them is, at first, not trivial. This is when the mean-squared error metric comes in handy. The mean-squared 
+error (MSE) of an estimator $\hat{\theta}$ of the parameter $\theta$ is defined as
 \begin{eqnarray*}
-\textnormal{Bias/Precision} = \frac{|\mathbb{E}[\hat{\theta}]-\theta|}{\sqrt{\textnormal{Var}[\hat{\theta}]}}.
+\textnormal{MSE} &=& \mathbb{E}[(\theta - \hat{\theta})^2].
 \end{eqnarray*}
+From the definition of the MSE, it can be seen that it is a measure of the distance from the estimator to the parameters' ``true" value. As such, this provides an 
+excellent metric among a given suite of estimators for a given parameter: for a given set of estimators, the one that gives the minimum mean-squared error 
+provides, on average, the one that is closer to the underlying ``true" value on a mean-square sense. Furthermore, it is easy to shown that the MSE can be written 
+as
+\begin{eqnarray*}
+\textnormal{MSE} &=& \mathbb{E}[(\theta - \hat{\theta})^2], \\
+&=& (\mathbb{E}[\hat{\theta}]-\theta)^2 + \textnormal{Var}[\hat{\theta}],\\
+&=& \textnormal{Bias}^2 + \textnormal{Variance}.
+\end{eqnarray*}
+This implies that given the bias and the variance of an estimator, the MSE can be easily calculated. In our specific application, in the past sub-section we have already 
+shown and studied the biases that each limb-darkening law (i.e., different estimators) imply on the retrieved transit parameters through simulation. We now estimate 
+the variances implied by those limb-darkening laws.
 
 \begin{figure*}
-\includegraphics[scale=0.9]{which_law_to_use/bias_variance_tradeoff.eps}
+\includegraphics[scale=0.9]{which_law_to_use/bias_variance_tradeoff_mse.eps}
 \caption{Results of our lightcurve fits to noisy lightcurves of a typical Hot-Jupiter in order to study the bias-variance trade-off of different limb-darkening laws on the planet-to-star radius 
-ratio for lightcurves with $100$ in-transit points. The ratio of the bias to the square-root of the variance (i.e., the precision) of each estimate for different laws is 
-shown as a function of the lightcurve noise level. The line of equal bias and precision is shown as a dashed gray line.}
+ratio for lightcurves with $100$ and $1000$ in-transit points. The MSE for different laws is shown as a function of the lightcurve noise level.}
 \label{biasvariance}
@@
 
-Given that the study of this ratio is complex from a mathematical point of view in this case, we study it through simulations similar to the ones done in the past sub-section, 
-but this time also adding different amounts of noise to the lightcurves. In this sense, we take a Monte Carlo approach in order to study this ratio. As a case study, we take that 
-of a typical Hot-Jupiter ($p=0.1$, $a_R = 10$) around a Solar-type star ($T_\textnormal{eff}= 5500$ K) on a low impact-parameter orbit ($b=0.3$), and we focus specifically 
-on the retrieval of the planet-to-star radius ratio, which is one of the most interesting parameters retrieved from transit lightcurves. We simulate a suite of lightcurves with noise 
-levels ranging from $10$ ppm to $3000$ ppm with different amount of in-transit points; here, however, we show our results for $N=100$ and $N=1000$ in-transit points for clarity, 
-which span a range of possible scenarios for both space based (e.g., \textit{Kepler}) and ground-based observations. For each case, $300$ lightcurves are generated, 
+Given that the study of the mean-squared error is complex from a mathematical point of view in this case, we study it through simulations similar to the ones done in the past sub-section, 
+but this time also adding different amounts of noise to the lightcurves in order to estimate the variances of the estimators. In this sense, we take a Monte Carlo approach in order to study 
+the MSE. As a case study, we take that of a typical Hot-Jupiter ($p=0.1$, $a_R = 10$) around a Solar-type star ($T_\textnormal{eff}= 5500$ K) on a low impact-parameter orbit ($b=0.3$), 
+and we focus specifically on the retrieval of the planet-to-star radius ratio, which is one of the most interesting parameters retrieved from transit lightcurves. We simulate a suite of 
+lightcurves with noise levels ranging from $10$ ppm to $3000$ ppm with different amount of in-transit points; here, however, we show our results for $N=100$ and $N=1000$ in-transit 
+points for clarity, which span a range of possible scenarios for both space based (e.g., \textit{Kepler}) and ground-based observations. For each case, $300$ lightcurves are generated, 
 and all of them are fitted in the same way as it was done for their noiseless counterparts in the past sub-section. From the fit to each of the $300$ lightcurves on each case, 
-we take all the estimated planet-to-star radius ratios and estimate the precision by calculating the square-root of the variance of the sample. The results of our simulations are shown 
-on Figure \ref{biasvariance}, where we plot the ratio of the absolute value of the bias (estimated in the previous sub-section) over the precision 
-(the square-root of the variance of the estimator) as a function of the noise in the simulated lightcurves.
+we take all the estimated planet-to-star radius ratios and estimate the variance of the sample. The results of our simulations are shown on Figure \ref{biasvariance}, where we plot the 
+MSE as a function of the noise in the simulated lightcurves.
 
-In our results, the line of equal bias and precision marks the limit at which one should switch to a more complex law. For example, in our simulation, for $N=100$ in-transit points, the 
-linear law touches this line at $\sim 500$ ppm, which means that for more precise lightcurves the bias on the planet-to-star radius ratio is larger than the precision (e.g., for a lightcurve with a precision of $\sim 200$
-ppm, the bias is $\sim 2$ times larger than the precision on the parameter) and, therefore, one should switch to a more complex law. To which law should one switch? From Figure \ref{biasvariance}, 
-it can be seen that between $\sim 50-500$ ppm, the best law in terms of bias/variance trade-off for this number of in-transit points is the square-root law which, among all the laws that are below 
-the equal bias and precision line, provides the best precision.
-For lightcurve precisions better than $\sim 50$ ppm, it can be seen that the square-root law crosses this line and therefore another law
-must be used, which can be selected in the same way as before (in this case, between $\sim 30-50$ ppm, the optimal decision would be to use the logarithmic law).
-For this specific case, it can be seen that the
-three-parameter law is only optimal for precision better than $\sim 20$ ppm.
-Of course, as can be seen from the plot, if one increases the number of in-transit points, the precisions at which each law crosses the
-equal bias and precision line are lower.
-For example, for $N=1000$, it can be seen that the linear law touches this line at $\sim 1500$ ppm, meaning that in this case even with a very noisy lightcurve one has to
-switch to a better limb-darkening law if one wants to keep the bias below the precision level.
+In our results, it can be seen that the optimal law in terms of the MSE at each noise level can be selected easily. For example, in our simulation, for $N=100$ in-transit points, 
+the logarithmic law is the best for the retrieval of the planet-to-star radius ratio in a MSE sense from lightcurves with noise levels of $\sim3000$ ppm up to $\sim 1000$ ppm. 
+At this last noise level, it can be seen that the square-root law crosses the line of the logarithmic law, and this law attains the lowest MSE until $\sim 200$ ppm, where the line 
+quadratic law starts to get the lowest MSE. The quadratic law is thus the best law to use from $\sim 200$ ppm until lightcurves with precisions of $\sim25$ ppm, precision at 
+which the three-parameter law takes over and attains the lowest MSE. Note that the number of in-transit points changes where the transition among different limb-darkening 
+laws occur. For example, the transition between the quadratic and three-parameter laws occurs with lower precision lightcurves for the case of $1000$ in-transit points 
+(at $\sim 75$ ppm).
 
-From our case study, it can be seen that the selection of the optimal limb-darkening law (i.e., the one that provides the best precision among the ones that avoid biases larger than it) can be 
-estimated by simple simulation. We provide code at Github with which this can be easily done for a given set of transit and stellar parameters, along with a given lightcurve noise level and number of 
-in-transit points.
+From our case study, it can be seen that the selection of the optimal limb-darkening law in a MSE sense can be estimated by simple simulation; however, we note that different 
+transit geometries will give rise to different optimal limb-darkening laws at a given lightcurve precision and, thus, these simulations must be performed on a case-by-case basis. 
+We provide code at Github with which this can be easily done for a given set of transit and stellar parameters, along with a given lightcurve noise level and number of in-transit points.
 

### 2016-01-18 which_law_to_use/analysis_mse.py

@@ -1,0 +1,138 @@
+# -*- coding: utf-8 -*-
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+import numpy as np
+from pyx import text as pyx_text
+from pyx import trafo
+def text_pyx(g, x_coord, y_coord, text_input, text_size = -2, color = None, rotation = 0.):
+    """
+    Function that draws text in a given plot
+    INPUTS:
+        g       (Object) A graph-type object to which you want to add the text
+        x_coord     (Double) x-coordinate (in plot units) at which you want to place
+                the text
+        y_coord     (Double) y-coordinate (in plot units) at which you want to place
+                the text
+        text_input  (String) Text that you want to add.
+        text_size   (int, optional) Text size of the text added to the plot. Default is -2.
+        color       (instance) Color instance that defines the color that you want the 
+                text to have. Default is black.
+    """
+
+    # First define the text attributes:
+    textattrs = [pyx_text.size(text_size),pyx_text.halign.center, pyx_text.vshift.middlezero, trafo.rotate(rotation)]
+
+    # Now convert plot positions to pyx's:
+    x0,y0 = g.pos(x_coord, y_coord)
+
+    # If no color is given, draw black text. If color is given, draw text with the input color:
+    if color is None:
+        g.text(x0,y0,text_input,textattrs)
+    else:
+        # First, check which was the input color palette:
+        color_dict = color.color
+        if len(color_dict.keys()) == 4:
+            color_string = str(color_dict['c'])+','+str(color_dict['m'])+','+str(color_dict['y'])+','+str(color_dict['k'])
+            color_palette = 'cmyk'
+        else:
+                        color_string = str(color_dict['r'])+','+str(color_dict['g'])+','+str(color_dict['b'])
+                        color_palette = 'rgb'
+        # Now draw the text:
+        g.text(x0, y0, r"\textcolor["+color_palette+"]{"+color_string+"}{"+text_input+"}",textattrs)
+
+from pyx import *
+results = '/Users/nespinoza/github/ld-exosim/results/sic/'
[…]

### 2016-01-18 which_law_2_use.tex
Added extra discussion to explain MSE results.

@@
 thanks to the exquisite precision allowed mainly by space-based observatories such as the {\em Hubble Space Telescope} ({\em HST}) and the {\em Kepler} mission \citep{koch2010}.
-This has allowed the study of precise mass-radius diagrams \citep[see, e.g.,][and references therein]{wm2014}, and in turn  allow the possibility of not only obtaining a precise determination of the internal composition of small, rocky exoplanets based on mass-radius
+This has allowed the study of precise mass-radius diagrams \citep[see, e.g.,][]{wm2014,dressing2015,WL2015b}, and in turn  allow the possibility of not only obtaining a precise determination of the internal composition of small, rocky exoplanets based on mass-radius
 measurements \citep{dorn2015} or of their atmospheric fractions from radius measurements alone \citep{WL2015}, but also of the determination of
@@
 \end{eqnarray*}
-From the definition of the MSE, it can be seen that it is a measure of the distance from the estimator to the parameters' ``true" value. As such, this provides an 
+From the definition of the MSE, it can be seen that it is a measure of the square of the distance from the estimator to the parameters' ``true" value. As such, this provides an 
 excellent metric among a given suite of estimators for a given parameter: for a given set of estimators, the one that gives the minimum mean-squared error 
-provides, on average, the one that is closer to the underlying ``true" value on a mean-square sense. Furthermore, it is easy to shown that the MSE can be written 
+provides, on average, the one that is closer to the underlying ``true" value on a mean-square sense. Furthermore, it is easy to show that the MSE can be written 
 as
@@
 This implies that given the bias and the variance of an estimator, the MSE can be easily calculated. In our specific application, in the past sub-section we have already 
-shown and studied the biases that each limb-darkening law (i.e., different estimators) imply on the retrieved transit parameters through simulation. We now estimate 
-the variances implied by those limb-darkening laws.
+shown and studied the biases that each limb-darkening law (i.e., different estimators) imply on the retrieved transit parameters through simulation. In this sense, we have 
+calculated the floor of the MSE for each law, and it only remains to study the variances implied by those limb-darkening laws, which is a function of the noise of the lightcurve 
+used to retrieve the transit parameters.
 
@@
 we take all the estimated planet-to-star radius ratios and estimate the variance of the sample. The results of our simulations are shown on Figure \ref{biasvariance}, where we plot the 
-MSE as a function of the noise in the simulated lightcurves.
+MSE as a function of the noise in the simulated lightcurves for each limb-darkening law used to retrieve the parameter.
 
-In our results, it can be seen that the optimal law in terms of the MSE at each noise level can be selected easily. For example, in our simulation, for $N=100$ in-transit points, 
+In our results, it is evident how the MSE evolves from being variance-dominated for low-precision lightcurves (rightmost part of the plot) to bias-dominated for high-precision 
+lightcurves (leftmost part of the plot). This evolution is most evident for the linear law: for $N=100$ in-transit points, for example, the linear law attains the bias floor around 
+$\sim100$ ppm. From here and for more precise lightcurves, the MSE of this law attains the constant value $\sim 10^{-6}$, which corresponds to the bias floor of 
+$10^{-3}$, which for $p=0.1$ corresponds to the $1\%$ bias observed on our simulations on the past sub-section (Figure \ref{small_b_sims}). 
+Note that from this plot, the optimal law in terms of the MSE at each noise level can be selected easily. For example, in our simulation, for $N=100$ in-transit points, 
 the logarithmic law is the best for the retrieval of the planet-to-star radius ratio in a MSE sense from lightcurves with noise levels of $\sim3000$ ppm up to $\sim 1000$ ppm. 
-At this last noise level, it can be seen that the square-root law crosses the line of the logarithmic law, and this law attains the lowest MSE until $\sim 200$ ppm, where the line 
+At this last noise level, it can be seen that the square-root law crosses the line of the logarithmic law, and this law attains the lowest MSE until $\sim 200$ ppm, where the 
 quadratic law starts to get the lowest MSE. The quadratic law is thus the best law to use from $\sim 200$ ppm until lightcurves with precisions of $\sim25$ ppm, precision at 
 which the three-parameter law takes over and attains the lowest MSE. Note that the number of in-transit points changes where the transition among different limb-darkening 
-laws occur. For example, the transition between the quadratic and three-parameter laws occurs with lower precision lightcurves for the case of $1000$ in-transit points 
-(at $\sim 75$ ppm).
+laws occur due to the fact that the bias floor is attained faster due to the increased number of points. For example, the transition between the quadratic and three-parameter 
+laws occurs with lower precision lightcurves for the case of $1000$ in-transit points (at $\sim 75$ ppm).
 
-From our case study, it can be seen that the selection of the optimal limb-darkening law in a MSE sense can be estimated by simple simulation; however, we note that different 
-transit geometries will give rise to different optimal limb-darkening laws at a given lightcurve precision and, thus, these simulations must be performed on a case-by-case basis. 
-We provide code at Github with which this can be easily done for a given set of transit and stellar parameters, along with a given lightcurve noise level and number of in-transit points.
+From our case study, it can be seen that the selection of the optimal limb-darkening law in a MSE sense can be estimated by simple simulation: simply calculate the MSE obtained 
+by all the laws and select the one that gives the minimum MSE. However, we note that different transit geometries will give rise to different optimal limb-darkening laws at a given 
+lightcurve precision and, thus, these simulations must be performed on a case-by-case basis. Of course, for this case-by-case study a set of transit parameters are needed as 
+inputs, which might be strange as this is what we are trying to extract from a transit lightcurve. However, as we learned from our results on this and the past sub-sections, it is important 
+to remember that the functional relation of the transit parameters and the biases/variances is smooth and slow; (i.e., small changes on the retrieved transit parameters give rise to 
+similar biases and variances). As such, one might first one to fit with one favourites' law, obtain a set of transit parameters and use these as inputs in order to calculate the MSE of 
+different limb-darkening laws in order to retrieve the final transit parameters from the law that gives the lowest MSE. We provide code at Github with which this can be easily done 
+for a given set of transit and stellar parameters, along with a given lightcurve noise level and number of in-transit points.
 
@@
 Benz, W. \& Tackley, P., 2015, A\&A, 577, 83.
+\bibitem[\protect\citeauthoryear{Dressing et al.}{2015}]{dressing2015} Dressing, C. D., Charbonneau, D., Dumusque, X., et al., 2015, ApJ, 800, 135.
 \bibitem[\protect\citeauthoryear{Kipping}{2013}]{kipping2013} Kipping, D. M., 2013, MNRAS, 435, 2152.
@@
 \bibitem[\protect\citeauthoryear{Wolfgang \& Lopez}{2015}]{WL2015} Wolfgang, A. \& Lopez, E., 2015, ApJ, 806, 183.
+\bibitem[\protect\citeauthoryear{Wolfgang, Rogers \& Ford}{2015}]{WL2015b} Wolfgang, A., Rogers, L. \& Ford, E., 2015, eprint arXiv:1504.07557.
 \end{thebibliography}

### 2016-01-19 which_law_2_use.tex
Addes acknowledgments to address the referees comments.
first pass of edits, tbd on fig 6

--- 2016-01-18 which_law_2_use.tex
@@
 \begin{abstract}
-With the advent of very precise measurements of exoplanet transit lightcurves both from ground and space based observatories, it has been 
-shown that it is now possible to fit the limb-darkening coefficients in the transit-fitting procedure rather than fix them to theoretical values. 
-This strategy has been shown to give better results as fixing the coefficients to theoretical values can give rise to important yet unknown systematic 
+Very precise measurements of exoplanet transit lightcurves both from ground and space based observatories make it now possible to fit the limb-darkening coefficients in the transit-fitting procedure rather than fix them to theoretical values.
+This strategy has been shown to give better results, as fixing the coefficients to theoretical values can give rise to important systematic 
 errors, which directly impact the physical properties of the system derived from such lightcurves such as the exoplanet's radius, scaled 
@@
 have mostly focused on the widely used quadratic limb-darkening law, leaving out other proposed laws that are either simpler (e.g., the linear law) or 
-in fact better descriptions of model intensity profiles, which in principle could diminish the bias even further. In this work, we show that laws such as the 
-logarithmic, square-root and three-parameter do a better job at retrieving the mentioned parameters from transit lightcurves both in terms of 
-bias and precision for a wide range of situations than the widely used quadratic and linear laws and therefore we recommend to study which one to 
-use on a case-by-case basis. We also provide code to guide the decision of when to use each of these laws and select the optimal one in a 
+better descriptions of model intensity profiles. In this work, we show that laws such as the 
+logarithmic, square-root and three-parameter law do a better job that the quadratic and linear laws when deriving parameters from transit lightcurves, both in terms of 
+bias and precision, for a wide range of situations. We therefore recommend to study which law to 
+use on a case-by-case basis. We provide code to guide the decision of when to use each of these laws and select the optimal one in a 
 mean-square error sense, which we note has a dependence on both stellar and transit parameters. Finally, we demonstrate that the 
@@
 thanks to the exquisite precision allowed mainly by space-based observatories such as the {\em Hubble Space Telescope} ({\em HST}) and the {\em Kepler} mission \citep{koch2010}.
-This has allowed the study of precise mass-radius diagrams \citep[see, e.g.,][and references therein]{wm2014}, and in turn  allow the possibility of not only obtaining a precise determination of the internal composition of small, rocky exoplanets based on mass-radius
-measurements \citep{dorn2015} or of their atmospheric fractions from radius measurements alone \citep{WL2015}, but also of the determination of
+This has allowed the study of precise mass-radius diagrams \citep[see, e.g.,][]{wm2014,dressing2015,WL2015b}, and in turn  allow the possibility of  obtaining a precise determination of the internal composition of small, rocky exoplanets based on mass-radius
+measurements \citep{dorn2015} and of their atmospheric fractions from radius measurements alone \citep{WL2015}. In addition, precise transit lightcurves enable the determination of
 derived parameters of the systems that even allow for the estimation of stellar parameters directly from transit lightcurves through techniques such as asterodensity
-profiling \citep{sm2003,kipping2014AP}, or of the detection of atmospheric features in exoplanet atmospheres through the technique of transmission spectroscopy. 
-All these studies and techniques rely on the retrieval of precise and accurate transit parameters from transit lightcurves.
+profiling \citep{sm2003,kipping2014AP}, and the detection of atmospheric features in exoplanet atmospheres through the technique of transmission spectroscopy. 
+All these studies and techniques rely on the retrieval of {\em precise and accurate} transit parameters from transit lightcurves.
 
@@
 of real stars \citep[which has also been seen on other studies, see, e.g.,][]{knutson2007, kreidberg2015},  and the biases when fixing the coefficients arise for the
-same reason plus the facts that different methods of fitting the model intensity profiles (including transit light curve versus intensity profile fitting) give rise to 
-different limb-darkening coefficients and the fact that we have an imperfect knowledge of the real intensity profiles of stars. We showed that fixing the limb-darkening 
+same reason plus the facts that (1) different methods of fitting the model intensity profiles (including transit light curve versus intensity profile fitting) give rise to 
+different limb-darkening coefficients and (2) that we have an imperfect knowledge of the real intensity profiles of stars. We showed that fixing the limb-darkening 
 coefficients is the worst option if one aims to obtain precise \textit{and} accurate transit parameters, because the biases arise from three different sources, 
@@
 the intensity profile of stars. Although the non-linear law proposed by \cite{claret2000} seems to be the most flexible, the fact that it has four free 
-parameters does not make it a very attractive one. Several laws with fewer parameters 
+parameters does not make it a very attractive one given its high complexity. Several laws with fewer parameters 
 have been proposed. Two-parameter laws are the exponential proposed by \cite{claret2003}, the logarithmic proposed by \cite{klinglesmith1970} and 
 the square-root proposed by \cite{diazgimenez1992}. In addition, a very flexible three-parameter law was also proposed by \cite{sing2009}. These laws 
-with fewer parameters are potentially very attractive for transit fitting purposes, due to their flexibility at following different intensity profiles and their low 
+with fewer parameters are potentially very attractive for transit fitting purposes, due to their flexibility at following different center to limb stellar intensity profiles and their low 
 number of parameters \citep[see, e.g., ][for a comparison between the goodness of fit to ATLAS model atmospheres of the mentioned two-parameter laws 
@@
 Despite the attractive nature of the above mentioned limb-darkening laws, testing their performance at retrieving transit parameters from transit 
-lightcurves was a problem until recently for two reasons. First, there was no publicly available code capable of efficiently generating fast and accurate 
+lightcurves was problematic until recently for two reasons. First, there was no publicly available code capable of efficiently generating fast and accurate 
 transit lightcurves using all of these non-standard laws. However, recently \cite{batman2015} published an 
@@
 
-In this work, we test how well these non-standard laws perform at retrieving transit parameters from transit lightcurves. We follow \cite{kipping2013} in order to 
+In this work, we aim to test how well these non-standard laws perform at retrieving transit parameters from transit lightcurves. We follow \cite{kipping2013} in order to 
 derive an efficient sampling scheme for the standard form of the logarithmic and exponential laws, and show that the latter is actually \textit{always} non-physical 
 in the sense proposed by \cite{kipping2013}. Then, we simulate transit lightcurves and perform simulations studies which extend the one done in EJ15 in several ways. 
-First, we study not only the accuracy problem but also the precision issue on the retrieved parameters. Second, we study the mentioned non-standard limb-darkening laws by 
-using the derived sampling schemes for the logarithmic law derived in this work, the sampling schemes detailed in \cite{kipping2013} for the other two-parameter laws 
+First, we study not only the accuracy problem but also the precision issue on the retrieved parameters. Second, we study the non-standard limb-darkening laws by 
+using a sampling scheme for the standard form of the logarithmic law derived in this work, the sampling schemes detailed in \cite{kipping2013} for the other two-parameter laws 
 and \cite{kipping2015} for the three-parameter law. In addition, we also study the performance of the linear law, which has been used in recent years by several authors 
 to parametrize the limb-darkening effect. We use our simulations to provide guidance as to when a particular law should be preferred, and provide code which, given the 
-precision of a given transit lightcurve and a set of transit and stellar parameters, helps to decide which law is the optimal (i.e., with the best bias/variance trade-off) one to use.
+precision of a transit lightcurve and a set of transit and stellar parameters, helps to decide which law is the optimal to use.
 
@@
 
-As explained in the introduction, an informative and efficient sampling of limb-darkening coefficients 
-in order to fit them to transit lightcurves is fundamental. Motivated by this, \cite{kipping2013} introduced 
-a procedure which first imposes physically motivated constrains on the intensity profiles, namely, an everywhere 
+An informative and efficient sampling of limb-darkening coefficients is desirable in order to fit them to transit lightcurves. Motivated by this, 
+\cite{kipping2013} introduced 
+a procedure which first imposes physically motivated constrains on the center to limb stellar intensity profiles $I(\mu)$, namely, an everywhere 
 positive intensity, $I(\mu)>0$,  and a decreasing intensity profile from center to limb, $\partial I(\mu)/\partial \mu>0$, 
-which in turn impose constraints on the two parameters of the law. With these constraints in hand, 
+which in turn impose constraints on the parameters of the law. With these constraints in hand, 
 \cite{kipping2013} devised a triangular sampling strategy which only requires sampling two uniformly distributed numbers between 
@@
 This was done in that work for the most popular two-parameter limb-darkening laws with the exceptions of the
-exponential limb-darkening law, whose derived constraints on the coefficients were not enough 
+exponential limb-darkening law, whose derived constraints on the coefficients were stated to be not enough 
 to use the triangular sampling technique, and the typical form of the logarithmic law, which is 
@@
 
-We now derive an informative and efficient sampling strategy for the more typical form of the logarithmic law and then 
+We derive here informative and efficient sampling strategy for the more typical form of the logarithmic law and then 
 we study the exponential law, for which we conclude that deriving an efficient sampling strategy is actually 
-impossible; this implies that the law is fundamentally non-physical and, therefore, should not be used.
+impossible. We find that the law is fundamentally non-physical and, therefore, should not be used.
 
@@
 square-root law and a three-parameter law. The dependence with the input values of $a_R$ are not shown as the bias seems to be almost independent of 
-this parameter in this case (this can be also seen by looking at the lower panels of Figure~10 in EJ15, which give the same results as the ones shown here for 
+this parameter in this case\footnote{This can be also seen by looking at the lower panels of Figure~10 in EJ15, which give the same results as the ones shown here for 
 the quadratic law. We note that this implies good agreement between the simulations done with our implementation of the \cite{ma2002} codes for the transit light 
-curve generation and the \texttt{batman} code).
+curve generation and the \texttt{batman} code}.
 
@@
 expected from its very simple form, the biases on the retrieved transit parameters are larger than the ones observed on the two and three-parameter laws for 
-almost all the stellar temperatures except for $T_\textnormal{eff}\sim 4500$, where the profile seems to be a decent (yet poorer than the ones provided by the 
-other laws) approximation to the real intensity profile. A second feature to note on our results is that the logarithmic law does a very good job at retrieving the 
+almost all the stellar temperatures except for $T_\textnormal{eff}\sim 4500$, where the profile seems to be a decent  approximation to the real intensity profile (yet poorer than the ones provided by the
+other laws). A second feature to note on our results is that the logarithmic law does a very good job at retrieving the 
 parameters of small planet-to-star radius ratios, even at the level of the three-parameter law for stars with $T_\textnormal{eff}<6000$ K, and also for medium 
-and large planet-to-star radius ratios with host-stars with $T_\textnormal{eff}<4000$ K (which makes this law a good choice for present and future transit 
-detection and characterisation around M-dwarfs). The quadratic law, on the other hand, is only the best among the options for host-stars between 
+and large planet-to-star radius ratios with host-stars with $T_\textnormal{eff}<4000$ K.
+This makes this law a very good choice for present and future transit characterisation around M-dwarfs.
+The quadratic law, on the other hand, is only the best for host-stars between
 $4250<T_\textnormal{eff}<5500$ K, with the logarithmic law being the best in the $5500<T_\textnormal{eff}<6250$ K range, and the square-root law 
@@
 the parameter $\theta$ is depicted in red, while the real, underlying value of the parameter $\theta$ is depicted with a black solid line. Ideally, one would 
-want a low bias, high precision estimator.}
+want a low bias, high precision estimator.{\bf TBD Here under sqrt(variance) it should say 1/precision}}
 \label{bias-variance-plot}
@@
 biases in the retrieved transit parameters from the transit light curve. However, an interesting question is whether the precision of a given lightcurve can 
-actually provide one with enough precision in order to use a more complex parametrization of the limb-darkening effect and, depending on the answer, what is 
-the cost. Fitting a complex law to a noisy light curve will definitely lower the precision on the retrieved transit parameters due to the high flexibility of the 
-model (i.e., the large parameter space that it can explore), while fitting a law that is too simple for a very precise lightcurve will most definitely lead to larger 
-biases, due to the strictness of the chosen model. This problem is known as the bias-variance trade-off, i.e., the problem of choosing the right amount of bias 
-and variance for a given dataset. Probabilistically, for a given estimator $\hat{\theta}$ of the parameter $\theta$, we will be interested in its variance (whose 
+actually provide enough precision in order to use a more complex parametrization of the limb-darkening effect and, depending on the answer, what is 
+the cost. Fitting a complex law to a noisy light curve will definitely lower the precision of the retrieved transit parameters due to the high flexibility of the 
+model, while fitting a law that is too simple for a very precise lightcurve will most definitely lead to larger 
+biases, due to the strictness of the chosen model.
+This problem is known as the bias-variance trade-off.
+Probabilistically, for a given estimator $\hat{\theta}$ of the parameter $\theta$, we will be interested in its variance (whose
 square-root defines the precision), $\textnormal{Var}[\hat{\theta}]$, and its bias, defined as $\mathbb{E}[\hat{\theta}]-\theta$, where 
@@
 the estimator from the parameters' true value, while the variance defines the spread around the expected value of the estimator (see Figure \ref{bias-variance-plot}). 
-In this sense, one would ideally want a low-bias and high-precision (i.e. low variance) estimator, which is both close to the real value of the parameter on average and, 
+One ideally wants a low-bias and high-precision estimator, which is both close to the real value of the parameter on average and, 
 at the same time, has a low spread around such value. The problem is that in real applications one has the possibility to choose from various estimators with different 
@@
 \end{eqnarray*}
-From the definition of the MSE, it can be seen that it is a measure of the distance from the estimator to the parameters' ``true" value. As such, this provides an 
-excellent metric among a given suite of estimators for a given parameter: for a given set of estimators, the one that gives the minimum mean-squared error 
-provides, on average, the one that is closer to the underlying ``true" value on a mean-square sense. Furthermore, it is easy to shown that the MSE can be written 
+From the definition of the MSE, it can be seen that it is a measure of the square of the distance from the estimator to the parameters' ``true" value.
+This provides a metric among a given suite of estimators for a given parameter: the one that gives the minimum mean-squared error
+provides, on average, the one that is closer to the underlying ``true" value on a mean-square sense. Furthermore, it is easy to show that the MSE can be written 
 as
@@
 This implies that given the bias and the variance of an estimator, the MSE can be easily calculated. In our specific application, in the past sub-section we have already 
-shown and studied the biases that each limb-darkening law (i.e., different estimators) imply on the retrieved transit parameters through simulation. We now estimate 
-the variances implied by those limb-darkening laws.
+shown and studied the biases that each limb-darkening law (i.e., different estimators) imply on the retrieved transit parameters through simulation. We have thus already
+calculated the floor of the MSE for each law, and it only remains to study the variances implied by those limb-darkening laws, which is a function of the noise of the lightcurve 
+used to retrieve the transit parameters.
 
@@
 
-Given that the study of the mean-squared error is complex from a mathematical point of view in this case, we study it through simulations similar to the ones done in the past sub-section, 
-but this time also adding different amounts of noise to the lightcurves in order to estimate the variances of the estimators. In this sense, we take a Monte Carlo approach in order to study 
+Given that the study of the mean-squared error is complex from a mathematical point of view for our case, we study it through simulations similar to the ones done in the past sub-section, 
+but this time also adding different amounts of noise to the lightcurves in order to derive the variances of the estimators for a given level of noise. We take a Monte Carlo approach in order to study 
 the MSE. As a case study, we take that of a typical Hot-Jupiter ($p=0.1$, $a_R = 10$) around a Solar-type star ($T_\textnormal{eff}= 5500$ K) on a low impact-parameter orbit ($b=0.3$), 
 and we focus specifically on the retrieval of the planet-to-star radius ratio, which is one of the most interesting parameters retrieved from transit lightcurves. We simulate a suite of 
-lightcurves with noise levels ranging from $10$ ppm to $3000$ ppm with different amount of in-transit points; here, however, we show our results for $N=100$ and $N=1000$ in-transit 
-points for clarity, which span a range of possible scenarios for both space based (e.g., \textit{Kepler}) and ground-based observations. For each case, $300$ lightcurves are generated, 
+lightcurves with noise levels ranging from $10$ ppm to $3000$ ppm with different amount of in-transit points. We show our results for $N=100$ and $N=1000$ in-transit 
+points, which span a range of possible scenarios for both space based (e.g., \textit{Kepler}) and ground-based observations. For each case, $300$ lightcurves are generated, 
 and all of them are fitted in the same way as it was done for their noiseless counterparts in the past sub-section. From the fit to each of the $300$ lightcurves on each case, 
-we take all the estimated planet-to-star radius ratios and estimate the variance of the sample. The results of our simulations are shown on Figure \ref{biasvariance}, where we plot the 
-MSE as a function of the noise in the simulated lightcurves.
+we take all the estimated planet-to-star radius ratios and estimate the variance of the sample. The results of our simulations are shown on Figure~\ref{biasvariance}, where we plot the 
+MSE as a function of the noise of the simulated lightcurves for each of the limb-darkening law used to retrieve the parameter.
 
-In our results, it can be seen that the optimal law in terms of the MSE at each noise level can be selected easily. For example, in our simulation, for $N=100$ in-transit points, 
-the logarithmic law is the best for the retrieval of the planet-to-star radius ratio in a MSE sense from lightcurves with noise levels of $\sim3000$ ppm up to $\sim 1000$ ppm. 
-At this last noise level, it can be seen that the square-root law crosses the line of the logarithmic law, and this law attains the lowest MSE until $\sim 200$ ppm, where the line 
-quadratic law starts to get the lowest MSE. The quadratic law is thus the best law to use from $\sim 200$ ppm until lightcurves with precisions of $\sim25$ ppm, precision at 
-which the three-parameter law takes over and attains the lowest MSE. Note that the number of in-transit points changes where the transition among different limb-darkening 
-laws occur. For example, the transition between the quadratic and three-parameter laws occurs with lower precision lightcurves for the case of $1000$ in-transit points 
-(at $\sim 75$ ppm).
+It is evident from our results how the MSE evolves from being variance-dominated for low-noise lightcurves (rightmost part of the plot) to bias-dominated for high-noise 
+lightcurves (leftmost part of the plot). This evolution is most evident for the linear law: for $N=100$ in-transit points, for example, the linear law attains the bias floor around 
+$\approx100$ ppm. From here and for more precise lightcurves, the MSE of this law attains the constant value $\sim 10^{-6}$, which corresponds to the bias floor of 
+$10^{-3}$, which for $p=0.1$ corresponds to the $1\%$ bias observed on our simulations on the past sub-section (see Figure~\ref{small_b_sims}). 
+Note that from this plot, the optimal law in terms of the MSE at each noise level can be selected with easse. For example, in our simulation, for $N=100$ in-transit points, 
+the logarithmic law is the best for the retrieval of the planet-to-star radius ratio in a MSE sense for lightcurves with noise levels between $\approx3000$ ppm to $\approx 1000$ ppm. 
+At this last noise level, we see that the square-root law crosses the line of the logarithmic law, and this latter law attains the lowest MSE until $\approx 200$ ppm, where the 
+quadratic law starts to get the lowest MSE. The quadratic law is thus the best law to use from $\approx 200$ ppm until lightcurves with precisions of $\approx25$ ppm, a noise level at 
+which the three-parameter law takes over and attains the lowest MSE. Note that the number of in-transit points changes the  points at which the transition among different limb-darkening 
+laws occur due to the fact that the bias floor is attained faster as a consequence of the increased number of points. For example, the transition between the quadratic and three-parameter 
+laws occurs for lower precision lightcurves for the case of $1000$ in-transit points (at $\approx 75$ ppm).
 
-From our case study, it can be seen that the selection of the optimal limb-darkening law in a MSE sense can be estimated by simple simulation; however, we note that different 
-transit geometries will give rise to different optimal limb-darkening laws at a given lightcurve precision and, thus, these simulations must be performed on a case-by-case basis. 
-We provide code at Github with which this can be easily done for a given set of transit and stellar parameters, along with a given lightcurve noise level and number of in-transit points.
+From our case study, we propose that the selection of the optimal limb-darkening law in a MSE sense can be estimated by simple simulation:  for a given observational setup in terms of cadence and noise, simply calculate the MSE obtained
+by all the laws and select the one that gives the minimum MSE. However, we note that different transit geometries will give rise to different optimal limb-darkening laws at a given 
+lightcurve precision and, thus, these simulations must be performed on a case-by-case basis. Of course, for this case-by-case study a set of transit parameters are needed as 
+inputs, which is a bit circular as this is what we are trying to extract from a transit lightcurve. However, as we learned from our results on this and the past sub-sections, it is important 
+to remember that the functional relation of the transit parameters and the biases/variances is smooth and slow.
+Therefore, one can first fit with one favourites' law, obtain a set of transit parameters, and use those as inputs in order to calculate the MSE of
+different limb-darkening laws in order to then retrieve the final transit parameters from the law that gives the lowest MSE. We provide code at Github with which this process be easily done 
+for a given set of transit and stellar parameters, along with a given lightcurve noise level and number of in-transit points.
 
@@
 in which they perform at the same level or even better than the three-parameter law and, because of this, we encourage their use. We also discourage the usage of the exponential 
-law which, as shown in \S2.2 is unphysical, and can lead to numerical errors if used on real data where sampling of points close to the limb (where the law diverges) is not uncommon.
+law which, as shown in \S2.2 is unphysical, and can lead to numerical errors if used on real data where sampling of points close to the limb is not uncommon.
 
@@
 transit parameters, the stellar host properties and the bias/variance on the retrieved transit parameters. We have stated no specific rule regarding when to use each 
-law, but rather provided only guidelines based on our simulations. This is a choice made on purpose, as the selection of which law to use has to be done in a 
-case-by-case basis, reason for which we provide code with which one can obtain the results of the same simulations performed on our work for specific 
-cases and with different resolutions\footnote{\url{http://www.github.com/nespinoza/ld-exosim/}}. It is important to note that in this work we have used the 
+law, but rather provided guidelines based on our simulations. This is a choice made on purpose, as the selection of which law to use has to be done in a 
+case-by-case basis, a task for which we provide code with which one can obtain the results of the same simulations performed on our work for specific 
+cases \footnote{\url{http://www.github.com/nespinoza/ld-exosim/}}. It is important to note that in this work we have used the 
 {\em Kepler} bandpass to study the relation between the biases/variances on the retrieved transit parameters and the stellar host properties, but different bandpasses should give 
-rise to  different functional relations because they give rise to different model intensity profiles, which are used in those simulations to approximate the 
-expected intensity profile and the adequacy of each limb-darkening law at following it. Limb-darkening coefficients have to be calculated for each 
-particular case, which is straightforward to do using the algorithms described in EJ15\footnote{\url{http://www.github.com/nespinoza/limb-darkening/}}.
+rise to  different functional relations because they give rise to different model intensity profiles.
+Limb-darkening coefficients have to be calculated for each  particular case, which is straightforward to do using the algorithms described in EJ15\footnote{\url{http://www.github.com/nespinoza/limb-darkening/}}.
 
@@
 
-N.E. is supported by CONICYT-PCHA/Doctorado Nacional. A.J. acknowledges 
+We thank the referee for insightful comments that greatly improved 
+this work. N.E. is supported by CONICYT-PCHA/Doctorado Nacional. A.J. acknowledges 
 support from FONDECYT project 1130857, the Ministry

### 2016-01-19 which_law_2_use.tex
Corrected minor typos

@@
 the parameter $\theta$ is depicted in red, while the real, underlying value of the parameter $\theta$ is depicted with a black solid line. Ideally, one would 
-want a low bias, high precision estimator.{\bf TBD Here under sqrt(variance) it should say 1/precision}}
+want a low bias, high precision estimator.}
 \label{bias-variance-plot}
@@
 we take all the estimated planet-to-star radius ratios and estimate the variance of the sample. The results of our simulations are shown on Figure~\ref{biasvariance}, where we plot the 
-MSE as a function of the noise of the simulated lightcurves for each of the limb-darkening law used to retrieve the parameter.
+MSE as a function of the noise of the simulated lightcurves for each of the limb-darkening laws used to retrieve the parameter.
 
@@
 inputs, which is a bit circular as this is what we are trying to extract from a transit lightcurve. However, as we learned from our results on this and the past sub-sections, it is important 
-to remember that the functional relation of the transit parameters and the biases/variances is smooth and slow.
-Therefore, one can first fit with one favourites' law, obtain a set of transit parameters, and use those as inputs in order to calculate the MSE of
-different limb-darkening laws in order to then retrieve the final transit parameters from the law that gives the lowest MSE. We provide code at Github with which this process be easily done 
-for a given set of transit and stellar parameters, along with a given lightcurve noise level and number of in-transit points.
+to remember that the functional relation of the transit parameters and the biases/variances is smooth and slow. Therefore, one can first fit with one favourites' law, obtain a set of 
+transit parameters, and use those as inputs in order to calculate the MSE of different limb-darkening laws in order to then retrieve the final transit parameters from the law that gives 
+the lowest MSE. We provide code at Github with which this process can be easily done for a given set of transit and stellar parameters, along with a given lightcurve noise level and 
+number of in-transit points.
 

### 2016-01-19 which_law_to_use/analysis_mse.py
Modified Figure 6.

@@ -125,6 +125,11 @@ for i in range(len(ld_laws)):
                                        style.linestyle.solid,\
                                        style.linewidth.THick])])
 
+    print 'ld_law     : ',ld_law
+    print 'lc precs   : ',precisions
+    print 'biases     : ',data[ld_law]['100']['bias_p']
+    print 'precisions : ',data[ld_law]['100']['precision_p']
+
     text_pyx(g, np.sqrt(precisions[0]*precisions[1]), data[ld_law]['100']['bias_p'][1]**2+data[ld_law]['100']['precision_p'][1]**2+delta_y[i], names[i], \
              text_size = -1, color = colors[i], rotation = rotation[i])
 

### 2016-01-19 which_law_to_use/bias_variance_plot.py

@@ -111,7 +111,7 @@ draw_arrow(g,mu+0.15,(1./np.sqrt(2.*np.pi*sigma))*np.exp(-(sigma)**2/(2.*sigma**
                 (1./np.sqrt(2.*np.pi*sigma))*np.exp(-(sigma)**2/(2.*sigma**2)),1.0,color.cmyk.Red)
 
 text_pyx(g,mu+(sigma/2.),(1./np.sqrt(2.*np.pi*sigma))*np.exp(-(sigma)**2/(2.*sigma**2))+0.01,r'$\sqrt{\textnormal{Var}[\hat{\theta}]}$',color=color.cmyk.Red)
-text_pyx(g,mu+(sigma/2.),(1./np.sqrt(2.*np.pi*sigma))*np.exp(-(sigma)**2/(2.*sigma**2))-0.01,r'(Precision)',color=color.cmyk.Red)
+text_pyx(g,mu+(sigma/2.),(1./np.sqrt(2.*np.pi*sigma))*np.exp(-(sigma)**2/(2.*sigma**2))-0.01,r'(1/Precision)',color=color.cmyk.Red)
 text_pyx(g,mu/2.,0.25 + 0.01,r'$\mathbb{E}[\hat{\theta}]-\theta$')
 text_pyx(g,mu/2.,0.25 - 0.01,r'(Bias)')
 

### 2016-01-20 first_response_to_referee.txt
final edit before resub

--- 2016-01-11 first_response_to_referee.txt
@@
 
+     - Changed the title of the manuscript to reflect the additional study 
+       proposed by the referee on the precision of the retrieved transit 
+       parameters, which implies we now not only help to decide the law 
+       that provide minimum bias, but also the one that is optimal in a mean squared error sense.
+
+     - Added extra text on the Abstract, Introduction and Section 3 to reflect 
+       these changes in the study. This includes a change of the name of Section 3, and an additional sub-section explaining the procedures used to study the bias/variance trade-off.
+
+     - Modified the Acknowledgments.
+
 ########################################################################################
@@
 
-RESPONSE
+We thank the referee for this very insightful suggestion. We have made a whole suite of 
+simulations which exactly answers this question, and provide code so future researchers 
+can decide which is the best law both in terms of bias and precision for their specific 
+application; in this way, researchers can decide the optimal limb-darkening law for the 
+lightcurve at hand. These simulations are shown and discussed both on Section 3.4 and 
+Section 4.
 

### 2016-01-20 which_law_2_use.tex
final edit before resub

@@
 This strategy has been shown to give better results, as fixing the coefficients to theoretical values can give rise to important systematic 
-errors, which directly impact the physical properties of the system derived from such lightcurves such as the exoplanet's radius, scaled 
-semi-major axis and inclination. However, studies of the effect of limb darkening assumptions on the retrieved parameters 
-have mostly focused on the widely used quadratic limb-darkening law, leaving out other proposed laws that are either simpler (e.g., the linear law) or 
+errors which directly impact the physical properties of the system derived from such lightcurves such as the planetary radius.
+However, studies of the effect of limb darkening assumptions on the retrieved parameters
+have mostly focused on the widely used quadratic limb-darkening law, leaving out other proposed laws that are either simpler or 
 better descriptions of model intensity profiles. In this work, we show that laws such as the 
@@
 thanks to the exquisite precision allowed mainly by space-based observatories such as the {\em Hubble Space Telescope} ({\em HST}) and the {\em Kepler} mission \citep{koch2010}.
-This has allowed the study of precise mass-radius diagrams \citep[see, e.g.,][]{wm2014,dressing2015,WL2015b}, and in turn  allow the possibility of  obtaining a precise determination of the internal composition of small, rocky exoplanets based on mass-radius
+This has allowed the study of precise mass-radius diagrams \citep[see, e.g.,][]{wm2014,dressing2015,WL2015b}, and in turn  allow the possibility of  obtaining a precise determination of the internal composition of small, rocky exoplanets based on mass and radius
 measurements \citep{dorn2015} and of their atmospheric fractions from radius measurements alone \citep{WL2015}. In addition, precise transit lightcurves enable the determination of
@@
 estimation} $26\%$ of the planet candidates (from which, e.g., population studies, which rely on averaging out \textit{random} and not \textit{systematic} 
-uncertainties like the ones introduced by limb-darkening) and almost half of the confirmed exoplanets (from which, e.g., characterization studies are 
-based on) have significant systematic errors.
+uncertainties like the ones introduced by limb-darkening) and almost half of the confirmed exoplanets have significant systematic errors.
 
@@
 no constrains for this law could be derived. We note that the form of the logarithmic law used in \cite{kipping2013} differs from the standard one proposed by 
-\cite{klinglesmith1970}. Thus, in order to  efficiently sample coefficients from the latter limb-darkening law one has to derive an efficient  informative sampling scheme for it.
+\cite{klinglesmith1970}. Thus, in order to  efficiently sample coefficients from the latter limb-darkening law one needs to derive an efficient  informative sampling scheme for it.
 
@@
 \section{Optimal selection of limb-darkening laws}
+
 Having dealt with the sampling of limb-darkening coefficients from the 
@@
 \subsection{Biases in the retrieval of transit parameters}
+
 In order to study the biases introduced by different parametrizations of the limb-darkening effect, we perform a similar study 
@@
 \subsubsection{The case of central transits}
+
 \begin{figure*}
@@
 \subsubsection{The case of non-central transits}
+
 \begin{figure*}
@@
 \subsection{The bias-variance trade-off}
+
 \begin{figure}
@@
 Probabilistically, for a given estimator $\hat{\theta}$ of the parameter $\theta$, we will be interested in its variance (whose
-square-root defines the precision), $\textnormal{Var}[\hat{\theta}]$, and its bias, defined as $\mathbb{E}[\hat{\theta}]-\theta$, where 
+square-root defines the inverse precision), $\textnormal{Var}[\hat{\theta}]$, and its bias, defined as $\mathbb{E}[\hat{\theta}]-\theta$, where 
 $\mathbb{E}[\cdot]$ defines the expectation value and $\textnormal{Var}[\cdot]$ is the variance operator. The bias, on one hand, defines how far on average is 
@@
 $10^{-3}$, which for $p=0.1$ corresponds to the $1\%$ bias observed on our simulations on the past sub-section (see Figure~\ref{small_b_sims}). 
-Note that from this plot, the optimal law in terms of the MSE at each noise level can be selected with easse. For example, in our simulation, for $N=100$ in-transit points, 
+Note that from this plot, the optimal law in terms of the MSE at each noise level can be selected with ease. For example, in our simulation, for $N=100$ in-transit points, 
 the logarithmic law is the best for the retrieval of the planet-to-star radius ratio in a MSE sense for lightcurves with noise levels between $\approx3000$ ppm to $\approx 1000$ ppm. 
@@
 inputs, which is a bit circular as this is what we are trying to extract from a transit lightcurve. However, as we learned from our results on this and the past sub-sections, it is important 
-to remember that the functional relation of the transit parameters and the biases/variances is smooth and slow. Therefore, one can first fit with one favourites' law, obtain a set of 
-transit parameters, and use those as inputs in order to calculate the MSE of different limb-darkening laws in order to then retrieve the final transit parameters from the law that gives 
+to remember that the functional relation of the transit parameters and the biases/variances is smooth and slow. Therefore, one can first fit with one's favourite law, obtain a set of 
+transit parameters, and use those as input in order to calculate the MSE of different limb-darkening laws and then retrieve the final transit parameters using the law that gives 
 the lowest MSE. We provide code at Github with which this process can be easily done for a given set of transit and stellar parameters, along with a given lightcurve noise level and 
@@
 
-The question of when to use each of those laws is an important one. In particular, we have explored the relation between the real, underlying 
+The question of when to use each of those laws is an important one. In particular, we have explored the relation between the ``real", underlying 
 transit parameters, the stellar host properties and the bias/variance on the retrieved transit parameters. We have stated no specific rule regarding when to use each 

### 2016-01-21 which_law_to_use/bias_variance_plot.py
Final (really) changes before resubmission.

@@ -111,7 +111,7 @@ draw_arrow(g,mu+0.15,(1./np.sqrt(2.*np.pi*sigma))*np.exp(-(sigma)**2/(2.*sigma**
                 (1./np.sqrt(2.*np.pi*sigma))*np.exp(-(sigma)**2/(2.*sigma**2)),1.0,color.cmyk.Red)
 
 text_pyx(g,mu+(sigma/2.),(1./np.sqrt(2.*np.pi*sigma))*np.exp(-(sigma)**2/(2.*sigma**2))+0.01,r'$\sqrt{\textnormal{Var}[\hat{\theta}]}$',color=color.cmyk.Red)
-text_pyx(g,mu+(sigma/2.),(1./np.sqrt(2.*np.pi*sigma))*np.exp(-(sigma)**2/(2.*sigma**2))-0.01,r'(1/Precision)',color=color.cmyk.Red)
+text_pyx(g,mu+(sigma/2.),(1./np.sqrt(2.*np.pi*sigma))*np.exp(-(sigma)**2/(2.*sigma**2))-0.01,r'(1/$\sqrt{\textnormal{Precision}}$)',color=color.cmyk.Red)
 text_pyx(g,mu/2.,0.25 + 0.01,r'$\mathbb{E}[\hat{\theta}]-\theta$')
 text_pyx(g,mu/2.,0.25 - 0.01,r'(Bias)')
 

### 2016-01-21 second_submission/which_law_2_use.tex
Corrected typo.

--- 2016-01-20 which_law_2_use.tex
@@
 model, while fitting a law that is too simple for a very precise lightcurve will most definitely lead to larger 
-biases, due to the strictness of the chosen model.
-This problem is known as the bias-variance trade-off.
-Probabilistically, for a given estimator $\hat{\theta}$ of the parameter $\theta$, we will be interested in its variance (whose
-square-root defines the inverse precision), $\textnormal{Var}[\hat{\theta}]$, and its bias, defined as $\mathbb{E}[\hat{\theta}]-\theta$, where 
-$\mathbb{E}[\cdot]$ defines the expectation value and $\textnormal{Var}[\cdot]$ is the variance operator. The bias, on one hand, defines how far on average is 
-the estimator from the parameters' true value, while the variance defines the spread around the expected value of the estimator (see Figure \ref{bias-variance-plot}). 
-One ideally wants a low-bias and high-precision estimator, which is both close to the real value of the parameter on average and, 
+biases, due to the strictness of the chosen model. This problem is known as the bias-variance trade-off. Probabilistically, for a given estimator $\hat{\theta}$ of 
+the parameter $\theta$, we will be interested in its variance (whose inverse defines the precision), $\textnormal{Var}[\hat{\theta}]$, and its bias, defined as 
+$\mathbb{E}[\hat{\theta}]-\theta$, where $\mathbb{E}[\cdot]$ defines the expectation value and $\textnormal{Var}[\cdot]$ is the variance operator. The bias, on 
+one hand, defines how far on average is the estimator from the parameters' true value, while the variance defines the spread around the expected value of the 
+estimator (see Figure \ref{bias-variance-plot}). One ideally wants a low-bias and high-precision estimator, which is both close to the real value of the parameter on average and, 
 at the same time, has a low spread around such value. The problem is that in real applications one has the possibility to choose from various estimators with different 

### 2016-01-21 second_submission/bias_transit_params/all_laws/b_0.0/old_plot_simulation_data.py

@@ -1,0 +1,275 @@
+from pyx import *
+import numpy as np
+
+import numpy as np
+
+def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
+
+    x0,y0 = g.pos(x_coord_init , y_coord_init)
+    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
+
+    x = x0
+    y = y0
+    w = np.abs(x0-xf)
+    h = np.abs(y0-yf)
+
+    g.fill(path.rect(x,y,w,h), [band_color])
+
+def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
+    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
+    x0,y0 = g.pos(x_coord, y_coord)
+    g.text(x0,y0,text_input,textattrs)
+
+b = 0.0
+ytext = 0.35
+p_scale = 0.1
+p_scale2 = 2.5
+p_show = [0.01,0.07,0.13]
+fit_option = 'float'
+
+# Get the results:
+grid_num_log, p_log, a_log, input_teff_log, p_fixed_log, sigma_p_fixed_log, p_float_log, sigma_p_float_log, \
+                a_fixed_log, sigma_a_fixed_log, a_float_log, sigma_a_float_log,i_fixed_log, sigma_i_fixed_log, i_float_log, sigma_i_float_log \
+                = np.loadtxt('logarithmic_results/final_results.dat',unpack=True)
+
+grid_num_sqrt, p_sqrt, a_sqrt, input_teff_sqrt, p_fixed_sqrt, sigma_p_fixed_sqrt, p_float_sqrt, sigma_p_float_sqrt, \
+                a_fixed_sqrt, sigma_a_fixed_sqrt, a_float_sqrt, sigma_a_float_sqrt,i_fixed_sqrt, sigma_i_fixed_sqrt, i_float_sqrt, sigma_i_float_sqrt \
+                = np.loadtxt('squareroot_results/final_results.dat',unpack=True)
+
+grid_num_quad, p_quad, a_quad, input_teff_quad, p_fixed_quad, sigma_p_fixed_quad, p_float_quad, sigma_p_float_quad, \
+                a_fixed_quad, sigma_a_fixed_quad, a_float_quad, sigma_a_float_quad,i_fixed_quad, sigma_i_fixed_quad, i_float_quad, sigma_i_float_quad \
+                = np.loadtxt('quadratic_results/final_results.dat',unpack=True)
+
[…]

### 2016-01-21 second_submission/bias_transit_params/all_laws/b_0.0/plot_simulation_data.py

@@ -1,0 +1,329 @@
+from pyx import *
+import numpy as np
+
+import numpy as np
+
+def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
+
+    x0,y0 = g.pos(x_coord_init , y_coord_init)
+    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
+
+    x = x0
+    y = y0
+    w = np.abs(x0-xf)
+    h = np.abs(y0-yf)
+
+    g.fill(path.rect(x,y,w,h), [band_color])
+
+def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
+    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
+    x0,y0 = g.pos(x_coord, y_coord)
+    g.text(x0,y0,text_input,textattrs)
+
+b = 0.0
+ytext = 0.35
+p_scale = 0.1
+p_scale2 = 2.5
+p_show = [0.01,0.07,0.13]
+fit_option = 'float'
+
+# Get the results:
+grid_num_tpl, p_tpl, a_tpl, input_teff_tpl, p_fixed_tpl, sigma_p_fixed_tpl, p_float_tpl, sigma_p_float_tpl, \
+                a_fixed_tpl, sigma_a_fixed_tpl, a_float_tpl, sigma_a_float_tpl,i_fixed_tpl, sigma_i_fixed_tpl, i_float_tpl, sigma_i_float_tpl \
+                = np.loadtxt('threeparam_results/final_results.dat',unpack=True)
+
+grid_num_log, p_log, a_log, input_teff_log, p_fixed_log, sigma_p_fixed_log, p_float_log, sigma_p_float_log, \
+                a_fixed_log, sigma_a_fixed_log, a_float_log, sigma_a_float_log,i_fixed_log, sigma_i_fixed_log, i_float_log, sigma_i_float_log \
+                = np.loadtxt('logarithmic_results/final_results.dat',unpack=True)
+
+grid_num_sqrt, p_sqrt, a_sqrt, input_teff_sqrt, p_fixed_sqrt, sigma_p_fixed_sqrt, p_float_sqrt, sigma_p_float_sqrt, \
+                a_fixed_sqrt, sigma_a_fixed_sqrt, a_float_sqrt, sigma_a_float_sqrt,i_fixed_sqrt, sigma_i_fixed_sqrt, i_float_sqrt, sigma_i_float_sqrt \
[…]

### 2016-01-21 second_submission/bias_transit_params/all_laws/b_0.3/old_plot_simulation_data.py

@@ -1,0 +1,327 @@
+from pyx import *
+import numpy as np
+
+import numpy as np
+
+def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
+
+    x0,y0 = g.pos(x_coord_init , y_coord_init)
+    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
+
+    x = x0
+    y = y0
+    w = np.abs(x0-xf)
+    h = np.abs(y0-yf)
+
+    g.fill(path.rect(x,y,w,h), [band_color])
+
+def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
+    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
+    x0,y0 = g.pos(x_coord, y_coord)
+    g.text(x0,y0,text_input,textattrs)
+
+b = 0.3
+ytext = 0.65
+p_scale = 0.1
+p_scale2 = 3.
+p_show = [0.01,0.07,0.13]
+fit_option = 'float'
+
+# Get the results:
+grid_num_tpl, p_tpl, a_tpl, input_teff_tpl, p_fixed_tpl, sigma_p_fixed_tpl, p_float_tpl, sigma_p_float_tpl, \
+                a_fixed_tpl, sigma_a_fixed_tpl, a_float_tpl, sigma_a_float_tpl,i_fixed_tpl, sigma_i_fixed_tpl, i_float_tpl, sigma_i_float_tpl \
+                = np.loadtxt('threeparam_results/final_results.dat',unpack=True)
+
+grid_num_log, p_log, a_log, input_teff_log, p_fixed_log, sigma_p_fixed_log, p_float_log, sigma_p_float_log, \
+                a_fixed_log, sigma_a_fixed_log, a_float_log, sigma_a_float_log,i_fixed_log, sigma_i_fixed_log, i_float_log, sigma_i_float_log \
+                = np.loadtxt('logarithmic_results/final_results.dat',unpack=True)
+
+grid_num_sqrt, p_sqrt, a_sqrt, input_teff_sqrt, p_fixed_sqrt, sigma_p_fixed_sqrt, p_float_sqrt, sigma_p_float_sqrt, \
+                a_fixed_sqrt, sigma_a_fixed_sqrt, a_float_sqrt, sigma_a_float_sqrt,i_fixed_sqrt, sigma_i_fixed_sqrt, i_float_sqrt, sigma_i_float_sqrt \
[…]

### 2016-01-21 second_submission/bias_transit_params/all_laws/b_0.3/plot_simulation_data.py

@@ -1,0 +1,356 @@
+from pyx import *
+import numpy as np
+
+import numpy as np
+
+def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
+
+    x0,y0 = g.pos(x_coord_init , y_coord_init)
+    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
+
+    x = x0
+    y = y0
+    w = np.abs(x0-xf)
+    h = np.abs(y0-yf)
+
+    g.fill(path.rect(x,y,w,h), [band_color])
+
+def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
+    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
+    x0,y0 = g.pos(x_coord, y_coord)
+    g.text(x0,y0,text_input,textattrs)
+
+b = 0.3
+ytext = 0.65
+p_scale = 0.1
+p_scale2 = 3.
+p_show = [0.01,0.07,0.13]
+fit_option = 'float'
+
+# Get the results:
+grid_num_tpl, p_tpl, a_tpl, input_teff_tpl, p_fixed_tpl, sigma_p_fixed_tpl, p_float_tpl, sigma_p_float_tpl, \
+                a_fixed_tpl, sigma_a_fixed_tpl, a_float_tpl, sigma_a_float_tpl,i_fixed_tpl, sigma_i_fixed_tpl, i_float_tpl, sigma_i_float_tpl \
+                = np.loadtxt('threeparam_results/final_results.dat',unpack=True)
+
+grid_num_log, p_log, a_log, input_teff_log, p_fixed_log, sigma_p_fixed_log, p_float_log, sigma_p_float_log, \
+                a_fixed_log, sigma_a_fixed_log, a_float_log, sigma_a_float_log,i_fixed_log, sigma_i_fixed_log, i_float_log, sigma_i_float_log \
+                = np.loadtxt('logarithmic_results/final_results.dat',unpack=True)
+
+grid_num_sqrt, p_sqrt, a_sqrt, input_teff_sqrt, p_fixed_sqrt, sigma_p_fixed_sqrt, p_float_sqrt, sigma_p_float_sqrt, \
+                a_fixed_sqrt, sigma_a_fixed_sqrt, a_float_sqrt, sigma_a_float_sqrt,i_fixed_sqrt, sigma_i_fixed_sqrt, i_float_sqrt, sigma_i_float_sqrt \
[…]

### 2016-01-21 second_submission/bias_transit_params/all_laws/b_0.8/plot_simulation_data.py

@@ -1,0 +1,356 @@
+from pyx import *
+import numpy as np
+
+import numpy as np
+
+def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
+
+    x0,y0 = g.pos(x_coord_init , y_coord_init)
+    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
+
+    x = x0
+    y = y0
+    w = np.abs(x0-xf)
+    h = np.abs(y0-yf)
+
+    g.fill(path.rect(x,y,w,h), [band_color])
+
+def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
+    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
+    x0,y0 = g.pos(x_coord, y_coord)
+    g.text(x0,y0,text_input,textattrs)
+
+b = 0.8
+ytext = 0.65
+p_scale = 0.1
+p_scale2 = 3.
+p_show = [0.01,0.07,0.13]
+fit_option = 'float'
+
+# Get the results:
+grid_num_tpl, p_tpl, a_tpl, input_teff_tpl, p_fixed_tpl, sigma_p_fixed_tpl, p_float_tpl, sigma_p_float_tpl, \
+                a_fixed_tpl, sigma_a_fixed_tpl, a_float_tpl, sigma_a_float_tpl,i_fixed_tpl, sigma_i_fixed_tpl, i_float_tpl, sigma_i_float_tpl \
+                = np.loadtxt('threeparam_results/final_results.dat',unpack=True)
+
+grid_num_log, p_log, a_log, input_teff_log, p_fixed_log, sigma_p_fixed_log, p_float_log, sigma_p_float_log, \
+                a_fixed_log, sigma_a_fixed_log, a_float_log, sigma_a_float_log,i_fixed_log, sigma_i_fixed_log, i_float_log, sigma_i_float_log \
+                = np.loadtxt('logarithmic_results/final_results.dat',unpack=True)
+
+grid_num_sqrt, p_sqrt, a_sqrt, input_teff_sqrt, p_fixed_sqrt, sigma_p_fixed_sqrt, p_float_sqrt, sigma_p_float_sqrt, \
+                a_fixed_sqrt, sigma_a_fixed_sqrt, a_float_sqrt, sigma_a_float_sqrt,i_fixed_sqrt, sigma_i_fixed_sqrt, i_float_sqrt, sigma_i_float_sqrt \
[…]

### 2016-01-21 second_submission/bias_transit_params/quadratic_fine_grid/b_0.3/plot_simulation_data.py

@@ -1,0 +1,252 @@
+from pyx import *
+import numpy as np
+
+import numpy as np
+
+def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
+
+    x0,y0 = g.pos(x_coord_init , y_coord_init)
+    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
+
+    x = x0
+    y = y0
+    w = np.abs(x0-xf)
+    h = np.abs(y0-yf)
+
+    g.fill(path.rect(x,y,w,h), [band_color])
+
+def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
+    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
+    x0,y0 = g.pos(x_coord, y_coord)
+    g.text(x0,y0,text_input,textattrs)
+
+b = 0.3
+ytext = 0.65
+p_scale = 0.2
+p_scale2 = 2.
+p_min = 0.10
+p_max = 0.12
+fit_option = 'float'
+
+# Get the results:
+grid_num_quad, p_quad, a_quad, input_teff_quad, p_fixed_quad, sigma_p_fixed_quad, p_float_quad, sigma_p_float_quad, \
+                a_fixed_quad, sigma_a_fixed_quad, a_float_quad, sigma_a_float_quad,i_fixed_quad, sigma_i_fixed_quad, i_float_quad, sigma_i_float_quad \
+                = np.loadtxt('quadratic_results/final_results.dat',unpack=True)
+
+# Order the results from largest to smallest p (in order to have the smallest points on top of larger ones):
+variables = ['grid_num_', 'p_', 'a_', 'input_teff_', 'p_'+fit_option+'_', 'sigma_p_'+fit_option+'_', 
+                                'a_'+fit_option+'_', 'sigma_a_'+fit_option+'_', 'i_'+fit_option+'_', 'sigma_i_'+fit_option+'_']
+
+################################# PLOTTING ######################################################
+# Now plot. First, some options:
+pheight = 3#5
+pwidth = 4#6.5
+delta_x = 5.0#9
+delta_y = 1.0
+unit.set(xscale = 0.8)
+text.set(mode="latex")
+text.preamble(r"\usepackage{color}")
+text.preamble(r"\usepackage{wasysym}")
+legend_text_size = -3
+# More options on the legend:
[…]

### 2016-01-21 second_submission/coefficients_check_exp/plot_check2.py

@@ -1,0 +1,184 @@
+from pyx import *
+import numpy as np
+import matplotlib.pyplot as plt
+
+def draw_arrow(g, x_coord_init, y_coord_init, x_coord_final, y_coord_final, size, line_color, stroke_color = None, fill_color = None):
+
+    if stroke_color is None:
+       stroke_color = line_color
+    if fill_color is None:
+       fill_color = line_color
+
+    x0,y0 = g.pos(x_coord_init , y_coord_init)
+    xf,yf = g.pos(x_coord_final, y_coord_final)
+    g.stroke(path.line(x0,y0,xf,yf),\
+         [style.linewidth.normal, style.linestyle.solid, line_color,
+          deco.earrow([deco.stroked([stroke_color]),
+                       deco.filled([fill_color])], size=0.1)])
+
+def draw_text(g, x_coord, y_coord, text_input, text_size = -2):
+    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
+    x0,y0 = g.pos(x_coord, y_coord)
+    g.text(x0,y0,text_input,textattrs)
+
+def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
+
+    x0,y0 = g.pos(x_coord_init , y_coord_init)
+    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
+
+    x = x0
+    y = y0
+    w = np.abs(x0-xf)
+    h = np.abs(y0-yf)
+
+    g.fill(path.rect(x,y,w,h), [band_color])
+
+def get_color(teff,i,half_val,m,n):
+    if teff[i] < half_val:
+        c_color = 2.0*(m*(teff[i])+n)
+        m_color = 1.-2.0*(m*(teff[i])+n)
+        y_color = 1.0
+        k_color = 0.
+    else:
+        c_color = 1.0
+        m_color = (m*(teff[i])+n) - 0.5
+        y_color = 2.0-2.0*(m*(teff[i])+n)
+        k_color = 0.
+
+    return color.cmyk(c_color,m_color,y_color,k_color)        
+
+teff,logg,mh,vturb,c1,c2 = np.loadtxt('all_atlas_lds_kepler.dat',unpack=True,usecols = (3,4,5,6,19,20))
+
+idx = np.where((teff<9000.))[0]
+mh = mh[idx]
+vturb = vturb[idx]
+logg = logg[idx]
+teff = teff[idx]
[…]

### 2016-01-21 second_submission/nasa_exoplanet_query/analyze_query.py

@@ -1,0 +1,36 @@
+import numpy as np
+
+data = np.genfromtxt('data.tab',usecols=(4,22,23,24),\
+                dtype=None,delimiter='\t')
+
+error_treshold = 0.01 # percent
+all_candidates = 0
+all_confirmed = 0
+candidate_count = 0
+confirmed_count = 0
+for i in range(len(data)):
+    status,depth,depth_err_up,depth_err_down = data[i]
+    if not np.isnan(depth) and not np.isnan(depth_err_up) and not np.isnan(depth_err_down):
+        # Get planet-to-star radius ratio as sqrt(depth):
+        p = np.sqrt(depth*1e-6)
+        # Estimate error on this via delta method:
+        perr = np.max([depth_err_up*1e-6,np.abs(depth_err_down*1e-6)])/(2.*np.sqrt(np.sqrt(depth*1e-6)))
+        # Get quoted precision:
+        precision = (perr/p)*100
+        if precision < error_treshold:
+                if status == 'CANDIDATE':
+                   candidate_count = candidate_count + 1
+                if status == 'CONFIRMED':
+                   confirmed_count = confirmed_count + 1
+        if status == 'CANDIDATE':
+                all_candidates = all_candidates + 1
+        if status == 'CONFIRMED':
+                all_confirmed = all_confirmed + 1
+print '\t Out of '+str(all_candidates)+' planet candidates:'
+print '\t > A total of '+str(candidate_count)+' have precision better than '+str(error_treshold)+'%.'
+print '\t Out of '+str(all_confirmed)+' confirmed exoplanets:'
+print '\t > A total of '+str(confirmed_count)+' have precision better than '+str(error_treshold)+'%.'
+
+#print depth
+#print depth_err_up
+#print len(depth)

### 2016-01-21 second_submission/which_law_to_use/analysis.py

@@ -1,0 +1,142 @@
+# -*- coding: utf-8 -*-
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+import numpy as np
+from pyx import text as pyx_text
+from pyx import trafo
+def text_pyx(g, x_coord, y_coord, text_input, text_size = -2, color = None, rotation = 0.):
+    """
+    Function that draws text in a given plot
+    INPUTS:
+        g       (Object) A graph-type object to which you want to add the text
+        x_coord     (Double) x-coordinate (in plot units) at which you want to place
+                the text
+        y_coord     (Double) y-coordinate (in plot units) at which you want to place
+                the text
+        text_input  (String) Text that you want to add.
+        text_size   (int, optional) Text size of the text added to the plot. Default is -2.
+        color       (instance) Color instance that defines the color that you want the 
+                text to have. Default is black.
+    """
+
+    # First define the text attributes:
+    textattrs = [pyx_text.size(text_size),pyx_text.halign.center, pyx_text.vshift.middlezero, trafo.rotate(rotation)]
+
+    # Now convert plot positions to pyx's:
+    x0,y0 = g.pos(x_coord, y_coord)
+
+    # If no color is given, draw black text. If color is given, draw text with the input color:
+    if color is None:
+        g.text(x0,y0,text_input,textattrs)
+    else:
+        # First, check which was the input color palette:
+        color_dict = color.color
+        if len(color_dict.keys()) == 4:
+            color_string = str(color_dict['c'])+','+str(color_dict['m'])+','+str(color_dict['y'])+','+str(color_dict['k'])
+            color_palette = 'cmyk'
+        else:
+                        color_string = str(color_dict['r'])+','+str(color_dict['g'])+','+str(color_dict['b'])
+                        color_palette = 'rgb'
+        # Now draw the text:
+        g.text(x0, y0, r"\textcolor["+color_palette+"]{"+color_string+"}{"+text_input+"}",textattrs)
+
+from pyx import *
+results = '/Users/nespinoza/github/ld-exosim/results/sic/'
+ld_laws = ['linear','quadratic','squareroot','logarithmic','three-param']
[…]

### 2016-01-21 second_submission/which_law_to_use/analysis_mse.py

@@ -1,0 +1,143 @@
+# -*- coding: utf-8 -*-
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+import numpy as np
+from pyx import text as pyx_text
+from pyx import trafo
+def text_pyx(g, x_coord, y_coord, text_input, text_size = -2, color = None, rotation = 0.):
+    """
+    Function that draws text in a given plot
+    INPUTS:
+        g       (Object) A graph-type object to which you want to add the text
+        x_coord     (Double) x-coordinate (in plot units) at which you want to place
+                the text
+        y_coord     (Double) y-coordinate (in plot units) at which you want to place
+                the text
+        text_input  (String) Text that you want to add.
+        text_size   (int, optional) Text size of the text added to the plot. Default is -2.
+        color       (instance) Color instance that defines the color that you want the 
+                text to have. Default is black.
+    """
+
+    # First define the text attributes:
+    textattrs = [pyx_text.size(text_size),pyx_text.halign.center, pyx_text.vshift.middlezero, trafo.rotate(rotation)]
+
+    # Now convert plot positions to pyx's:
+    x0,y0 = g.pos(x_coord, y_coord)
+
+    # If no color is given, draw black text. If color is given, draw text with the input color:
+    if color is None:
+        g.text(x0,y0,text_input,textattrs)
+    else:
+        # First, check which was the input color palette:
+        color_dict = color.color
+        if len(color_dict.keys()) == 4:
+            color_string = str(color_dict['c'])+','+str(color_dict['m'])+','+str(color_dict['y'])+','+str(color_dict['k'])
+            color_palette = 'cmyk'
+        else:
+                        color_string = str(color_dict['r'])+','+str(color_dict['g'])+','+str(color_dict['b'])
+                        color_palette = 'rgb'
+        # Now draw the text:
+        g.text(x0, y0, r"\textcolor["+color_palette+"]{"+color_string+"}{"+text_input+"}",textattrs)
+
+from pyx import *
+results = '/Users/nespinoza/github/ld-exosim/results/sic/'
[…]

### 2016-01-21 second_submission/which_law_to_use/bias_variance_plot.py

@@ -1,0 +1,119 @@
+# -*- coding: utf-8 -*-
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+import numpy as np
+from pyx import text as pyx_text
+from pyx import trafo
+def text_pyx(g, x_coord, y_coord, text_input, text_size = -2, color = None, rotation = 0.):
+    """
+    Function that draws text in a given plot
+    INPUTS:
+        g       (Object) A graph-type object to which you want to add the text
+        x_coord     (Double) x-coordinate (in plot units) at which you want to place
+                the text
+        y_coord     (Double) y-coordinate (in plot units) at which you want to place
+                the text
+        text_input  (String) Text that you want to add.
+        text_size   (int, optional) Text size of the text added to the plot. Default is -2.
+        color       (instance) Color instance that defines the color that you want the 
+                text to have. Default is black.
+    """
+
+    # First define the text attributes:
+    textattrs = [pyx_text.size(text_size),pyx_text.halign.center, pyx_text.vshift.middlezero, trafo.rotate(rotation)]
+
+    # Now convert plot positions to pyx's:
+    x0,y0 = g.pos(x_coord, y_coord)
+
+    # If no color is given, draw black text. If color is given, draw text with the input color:
+    if color is None:
+        g.text(x0,y0,text_input,textattrs)
+    else:
+        # First, check which was the input color palette:
+        color_dict = color.color
+        if len(color_dict.keys()) == 4:
+            color_string = str(color_dict['c'])+','+str(color_dict['m'])+','+str(color_dict['y'])+','+str(color_dict['k'])
+            color_palette = 'cmyk'
+        else:
+                        color_string = str(color_dict['r'])+','+str(color_dict['g'])+','+str(color_dict['b'])
+                        color_palette = 'rgb'
+        # Now draw the text:
[…]

### 2016-01-26 which_law_2_use.tex
Corrected typo in abstract. Will be uploaded to arXiv.

@@
 better descriptions of model intensity profiles. In this work, we show that laws such as the 
-logarithmic, square-root and three-parameter law do a better job that the quadratic and linear laws when deriving parameters from transit lightcurves, both in terms of 
+logarithmic, square-root and three-parameter law do a better job than the quadratic and linear laws when deriving parameters from transit lightcurves, both in terms of 
 bias and precision, for a wide range of situations. We therefore recommend to study which law to 
@@
 
-It is evident from our results how the MSE evolves from being variance-dominated for low-noise lightcurves (rightmost part of the plot) to bias-dominated for high-noise 
+It is evident from our results how the MSE evolves from being variance-dominated for high-noise lightcurves (rightmost part of the plot) to bias-dominated for low-noise 
 lightcurves (leftmost part of the plot). This evolution is most evident for the linear law: for $N=100$ in-transit points, for example, the linear law attains the bias floor around 

### 2016-01-26 which_law_to_use/analysis_mse.py
Added data from simulations.

@@ -41,7 +41,7 @@ def text_pyx(g, x_coord, y_coord, text_input, text_size = -2, color = None, rota
         g.text(x0, y0, r"\textcolor["+color_palette+"]{"+color_string+"}{"+text_input+"}",textattrs)
 
 from pyx import *
-results = '/Users/nespinoza/github/ld-exosim/results/sic/'
+results = 'results/sic/'
 ld_laws = ['linear','quadratic','squareroot','logarithmic','three-param']
 names = ['Linear law', 'Quadratic law', 'Square-root law', 'Logarithmic law','Three-parameter law']
 rotation = [0.0,11.,3.0,9.,35]

### 2016-01-26 second_submission/bias_transit_params/all_laws/b_0.0/explore_sims.py
Left only the final submission.

@@ -1,299 +1,0 @@
-from pylab import *
-
-import numpy as np
-
-import numpy as np
-
-def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
-
-    x0,y0 = g.pos(x_coord_init , y_coord_init)
-    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
-
-    x = x0
-    y = y0
-    w = np.abs(x0-xf)
-    h = np.abs(y0-yf)
-
-    g.fill(path.rect(x,y,w,h), [band_color])
-
-def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
-    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
-    x0,y0 = g.pos(x_coord, y_coord)
-    g.text(x0,y0,text_input,textattrs)
-
-b = 0.0
-ytext = 0.35
-p_scale = 0.1
-p_scale2 = 2.5
-p_show = [0.01,0.07,0.13]
-fit_option = 'float'
-
-# Get the results:
-grid_num_tpl, p_tpl, a_tpl, input_teff_tpl, p_fixed_tpl, sigma_p_fixed_tpl, p_float_tpl, sigma_p_float_tpl, \
-                a_fixed_tpl, sigma_a_fixed_tpl, a_float_tpl, sigma_a_float_tpl,i_fixed_tpl, sigma_i_fixed_tpl, i_float_tpl, sigma_i_float_tpl \
-                = np.loadtxt('threeparam_results/final_results.dat',unpack=True)
-
-grid_num_log, p_log, a_log, input_teff_log, p_fixed_log, sigma_p_fixed_log, p_float_log, sigma_p_float_log, \
-                a_fixed_log, sigma_a_fixed_log, a_float_log, sigma_a_float_log,i_fixed_log, sigma_i_fixed_log, i_float_log, sigma_i_float_log \
-                = np.loadtxt('logarithmic_results/final_results.dat',unpack=True)
-
-grid_num_sqrt, p_sqrt, a_sqrt, input_teff_sqrt, p_fixed_sqrt, sigma_p_fixed_sqrt, p_float_sqrt, sigma_p_float_sqrt, \
-                a_fixed_sqrt, sigma_a_fixed_sqrt, a_float_sqrt, sigma_a_float_sqrt,i_fixed_sqrt, sigma_i_fixed_sqrt, i_float_sqrt, sigma_i_float_sqrt \
[…]

### 2016-01-26 second_submission/bias_transit_params/all_laws/b_0.0/old_plot_simulation_data.py

@@ -1,275 +1,0 @@
-from pyx import *
-import numpy as np
-
-import numpy as np
-
-def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
-
-    x0,y0 = g.pos(x_coord_init , y_coord_init)
-    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
-
-    x = x0
-    y = y0
-    w = np.abs(x0-xf)
-    h = np.abs(y0-yf)
-
-    g.fill(path.rect(x,y,w,h), [band_color])
-
-def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
-    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
-    x0,y0 = g.pos(x_coord, y_coord)
-    g.text(x0,y0,text_input,textattrs)
-
-b = 0.0
-ytext = 0.35
-p_scale = 0.1
-p_scale2 = 2.5
-p_show = [0.01,0.07,0.13]
-fit_option = 'float'
-
-# Get the results:
-grid_num_log, p_log, a_log, input_teff_log, p_fixed_log, sigma_p_fixed_log, p_float_log, sigma_p_float_log, \
-                a_fixed_log, sigma_a_fixed_log, a_float_log, sigma_a_float_log,i_fixed_log, sigma_i_fixed_log, i_float_log, sigma_i_float_log \
-                = np.loadtxt('logarithmic_results/final_results.dat',unpack=True)
-
-grid_num_sqrt, p_sqrt, a_sqrt, input_teff_sqrt, p_fixed_sqrt, sigma_p_fixed_sqrt, p_float_sqrt, sigma_p_float_sqrt, \
-                a_fixed_sqrt, sigma_a_fixed_sqrt, a_float_sqrt, sigma_a_float_sqrt,i_fixed_sqrt, sigma_i_fixed_sqrt, i_float_sqrt, sigma_i_float_sqrt \
-                = np.loadtxt('squareroot_results/final_results.dat',unpack=True)
-
-grid_num_quad, p_quad, a_quad, input_teff_quad, p_fixed_quad, sigma_p_fixed_quad, p_float_quad, sigma_p_float_quad, \
-                a_fixed_quad, sigma_a_fixed_quad, a_float_quad, sigma_a_float_quad,i_fixed_quad, sigma_i_fixed_quad, i_float_quad, sigma_i_float_quad \
-                = np.loadtxt('quadratic_results/final_results.dat',unpack=True)
-
[…]

### 2016-01-26 second_submission/bias_transit_params/all_laws/b_0.0/plot_simulation_data.py

@@ -1,329 +1,0 @@
-from pyx import *
-import numpy as np
-
-import numpy as np
-
-def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
-
-    x0,y0 = g.pos(x_coord_init , y_coord_init)
-    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
-
-    x = x0
-    y = y0
-    w = np.abs(x0-xf)
-    h = np.abs(y0-yf)
-
-    g.fill(path.rect(x,y,w,h), [band_color])
-
-def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
-    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
-    x0,y0 = g.pos(x_coord, y_coord)
-    g.text(x0,y0,text_input,textattrs)
-
-b = 0.0
-ytext = 0.35
-p_scale = 0.1
-p_scale2 = 2.5
-p_show = [0.01,0.07,0.13]
-fit_option = 'float'
-
-# Get the results:
-grid_num_tpl, p_tpl, a_tpl, input_teff_tpl, p_fixed_tpl, sigma_p_fixed_tpl, p_float_tpl, sigma_p_float_tpl, \
-                a_fixed_tpl, sigma_a_fixed_tpl, a_float_tpl, sigma_a_float_tpl,i_fixed_tpl, sigma_i_fixed_tpl, i_float_tpl, sigma_i_float_tpl \
-                = np.loadtxt('threeparam_results/final_results.dat',unpack=True)
-
-grid_num_log, p_log, a_log, input_teff_log, p_fixed_log, sigma_p_fixed_log, p_float_log, sigma_p_float_log, \
-                a_fixed_log, sigma_a_fixed_log, a_float_log, sigma_a_float_log,i_fixed_log, sigma_i_fixed_log, i_float_log, sigma_i_float_log \
-                = np.loadtxt('logarithmic_results/final_results.dat',unpack=True)
-
-grid_num_sqrt, p_sqrt, a_sqrt, input_teff_sqrt, p_fixed_sqrt, sigma_p_fixed_sqrt, p_float_sqrt, sigma_p_float_sqrt, \
-                a_fixed_sqrt, sigma_a_fixed_sqrt, a_float_sqrt, sigma_a_float_sqrt,i_fixed_sqrt, sigma_i_fixed_sqrt, i_float_sqrt, sigma_i_float_sqrt \
[…]

### 2016-01-26 second_submission/bias_transit_params/all_laws/b_0.0/plot_simulation_data_all.py

@@ -1,293 +1,0 @@
-from pyx import *
-import numpy as np
-
-import numpy as np
-
-def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
-
-    x0,y0 = g.pos(x_coord_init , y_coord_init)
-    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
-
-    x = x0
-    y = y0
-    w = np.abs(x0-xf)
-    h = np.abs(y0-yf)
-
-    g.fill(path.rect(x,y,w,h), [band_color])
-
-def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
-    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
-    x0,y0 = g.pos(x_coord, y_coord)
-    g.text(x0,y0,text_input,textattrs)
-
-b = 0.0
-ytext = 0.35
-p_scale = 0.1
-p_scale2 = 2.5
-p_show = [0.01,0.07,0.13]
-fit_option = 'float'
-
-# Get the results:
-grid_num_tpl, p_tpl, a_tpl, input_teff_tpl, p_fixed_tpl, sigma_p_fixed_tpl, p_float_tpl, sigma_p_float_tpl, \
-                a_fixed_tpl, sigma_a_fixed_tpl, a_float_tpl, sigma_a_float_tpl,i_fixed_tpl, sigma_i_fixed_tpl, i_float_tpl, sigma_i_float_tpl \
-                = np.loadtxt('threeparam_results/final_results.dat',unpack=True)
-
-grid_num_log, p_log, a_log, input_teff_log, p_fixed_log, sigma_p_fixed_log, p_float_log, sigma_p_float_log, \
-                a_fixed_log, sigma_a_fixed_log, a_float_log, sigma_a_float_log,i_fixed_log, sigma_i_fixed_log, i_float_log, sigma_i_float_log \
-                = np.loadtxt('logarithmic_results/final_results.dat',unpack=True)
-
-grid_num_sqrt, p_sqrt, a_sqrt, input_teff_sqrt, p_fixed_sqrt, sigma_p_fixed_sqrt, p_float_sqrt, sigma_p_float_sqrt, \
-                a_fixed_sqrt, sigma_a_fixed_sqrt, a_float_sqrt, sigma_a_float_sqrt,i_fixed_sqrt, sigma_i_fixed_sqrt, i_float_sqrt, sigma_i_float_sqrt \
[…]

### 2016-01-26 second_submission/bias_transit_params/all_laws/b_0.3/old_plot_simulation_data.py

@@ -1,327 +1,0 @@
-from pyx import *
-import numpy as np
-
-import numpy as np
-
-def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
-
-    x0,y0 = g.pos(x_coord_init , y_coord_init)
-    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
-
-    x = x0
-    y = y0
-    w = np.abs(x0-xf)
-    h = np.abs(y0-yf)
-
-    g.fill(path.rect(x,y,w,h), [band_color])
-
-def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
-    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
-    x0,y0 = g.pos(x_coord, y_coord)
-    g.text(x0,y0,text_input,textattrs)
-
-b = 0.3
-ytext = 0.65
-p_scale = 0.1
-p_scale2 = 3.
-p_show = [0.01,0.07,0.13]
-fit_option = 'float'
-
-# Get the results:
-grid_num_tpl, p_tpl, a_tpl, input_teff_tpl, p_fixed_tpl, sigma_p_fixed_tpl, p_float_tpl, sigma_p_float_tpl, \
-                a_fixed_tpl, sigma_a_fixed_tpl, a_float_tpl, sigma_a_float_tpl,i_fixed_tpl, sigma_i_fixed_tpl, i_float_tpl, sigma_i_float_tpl \
-                = np.loadtxt('threeparam_results/final_results.dat',unpack=True)
-
-grid_num_log, p_log, a_log, input_teff_log, p_fixed_log, sigma_p_fixed_log, p_float_log, sigma_p_float_log, \
-                a_fixed_log, sigma_a_fixed_log, a_float_log, sigma_a_float_log,i_fixed_log, sigma_i_fixed_log, i_float_log, sigma_i_float_log \
-                = np.loadtxt('logarithmic_results/final_results.dat',unpack=True)
-
-grid_num_sqrt, p_sqrt, a_sqrt, input_teff_sqrt, p_fixed_sqrt, sigma_p_fixed_sqrt, p_float_sqrt, sigma_p_float_sqrt, \
-                a_fixed_sqrt, sigma_a_fixed_sqrt, a_float_sqrt, sigma_a_float_sqrt,i_fixed_sqrt, sigma_i_fixed_sqrt, i_float_sqrt, sigma_i_float_sqrt \
[…]

### 2016-01-26 second_submission/bias_transit_params/all_laws/b_0.3/plot_simulation_data.py

@@ -1,356 +1,0 @@
-from pyx import *
-import numpy as np
-
-import numpy as np
-
-def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
-
-    x0,y0 = g.pos(x_coord_init , y_coord_init)
-    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
-
-    x = x0
-    y = y0
-    w = np.abs(x0-xf)
-    h = np.abs(y0-yf)
-
-    g.fill(path.rect(x,y,w,h), [band_color])
-
-def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
-    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
-    x0,y0 = g.pos(x_coord, y_coord)
-    g.text(x0,y0,text_input,textattrs)
-
-b = 0.3
-ytext = 0.65
-p_scale = 0.1
-p_scale2 = 3.
-p_show = [0.01,0.07,0.13]
-fit_option = 'float'
-
-# Get the results:
-grid_num_tpl, p_tpl, a_tpl, input_teff_tpl, p_fixed_tpl, sigma_p_fixed_tpl, p_float_tpl, sigma_p_float_tpl, \
-                a_fixed_tpl, sigma_a_fixed_tpl, a_float_tpl, sigma_a_float_tpl,i_fixed_tpl, sigma_i_fixed_tpl, i_float_tpl, sigma_i_float_tpl \
-                = np.loadtxt('threeparam_results/final_results.dat',unpack=True)
-
-grid_num_log, p_log, a_log, input_teff_log, p_fixed_log, sigma_p_fixed_log, p_float_log, sigma_p_float_log, \
-                a_fixed_log, sigma_a_fixed_log, a_float_log, sigma_a_float_log,i_fixed_log, sigma_i_fixed_log, i_float_log, sigma_i_float_log \
-                = np.loadtxt('logarithmic_results/final_results.dat',unpack=True)
-
-grid_num_sqrt, p_sqrt, a_sqrt, input_teff_sqrt, p_fixed_sqrt, sigma_p_fixed_sqrt, p_float_sqrt, sigma_p_float_sqrt, \
-                a_fixed_sqrt, sigma_a_fixed_sqrt, a_float_sqrt, sigma_a_float_sqrt,i_fixed_sqrt, sigma_i_fixed_sqrt, i_float_sqrt, sigma_i_float_sqrt \
[…]

### 2016-01-26 second_submission/bias_transit_params/all_laws/b_0.8/plot_simulation_data.py

@@ -1,356 +1,0 @@
-from pyx import *
-import numpy as np
-
-import numpy as np
-
-def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
-
-    x0,y0 = g.pos(x_coord_init , y_coord_init)
-    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
-
-    x = x0
-    y = y0
-    w = np.abs(x0-xf)
-    h = np.abs(y0-yf)
-
-    g.fill(path.rect(x,y,w,h), [band_color])
-
-def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
-    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
-    x0,y0 = g.pos(x_coord, y_coord)
-    g.text(x0,y0,text_input,textattrs)
-
-b = 0.8
-ytext = 0.65
-p_scale = 0.1
-p_scale2 = 3.
-p_show = [0.01,0.07,0.13]
-fit_option = 'float'
-
-# Get the results:
-grid_num_tpl, p_tpl, a_tpl, input_teff_tpl, p_fixed_tpl, sigma_p_fixed_tpl, p_float_tpl, sigma_p_float_tpl, \
-                a_fixed_tpl, sigma_a_fixed_tpl, a_float_tpl, sigma_a_float_tpl,i_fixed_tpl, sigma_i_fixed_tpl, i_float_tpl, sigma_i_float_tpl \
-                = np.loadtxt('threeparam_results/final_results.dat',unpack=True)
-
-grid_num_log, p_log, a_log, input_teff_log, p_fixed_log, sigma_p_fixed_log, p_float_log, sigma_p_float_log, \
-                a_fixed_log, sigma_a_fixed_log, a_float_log, sigma_a_float_log,i_fixed_log, sigma_i_fixed_log, i_float_log, sigma_i_float_log \
-                = np.loadtxt('logarithmic_results/final_results.dat',unpack=True)
-
-grid_num_sqrt, p_sqrt, a_sqrt, input_teff_sqrt, p_fixed_sqrt, sigma_p_fixed_sqrt, p_float_sqrt, sigma_p_float_sqrt, \
-                a_fixed_sqrt, sigma_a_fixed_sqrt, a_float_sqrt, sigma_a_float_sqrt,i_fixed_sqrt, sigma_i_fixed_sqrt, i_float_sqrt, sigma_i_float_sqrt \
[…]

### 2016-01-26 second_submission/bias_transit_params/quadratic_fine_grid/b_0.3/plot_simulation_data.py

@@ -1,252 +1,0 @@
-from pyx import *
-import numpy as np
-
-import numpy as np
-
-def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
-
-    x0,y0 = g.pos(x_coord_init , y_coord_init)
-    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
-
-    x = x0
-    y = y0
-    w = np.abs(x0-xf)
-    h = np.abs(y0-yf)
-
-    g.fill(path.rect(x,y,w,h), [band_color])
-
-def draw_text(g, x_coord, y_coord, text_input, text_size = 1):
-    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
-    x0,y0 = g.pos(x_coord, y_coord)
-    g.text(x0,y0,text_input,textattrs)
-
-b = 0.3
-ytext = 0.65
-p_scale = 0.2
-p_scale2 = 2.
-p_min = 0.10
-p_max = 0.12
-fit_option = 'float'
-
-# Get the results:
-grid_num_quad, p_quad, a_quad, input_teff_quad, p_fixed_quad, sigma_p_fixed_quad, p_float_quad, sigma_p_float_quad, \
-                a_fixed_quad, sigma_a_fixed_quad, a_float_quad, sigma_a_float_quad,i_fixed_quad, sigma_i_fixed_quad, i_float_quad, sigma_i_float_quad \
-                = np.loadtxt('quadratic_results/final_results.dat',unpack=True)
-
-# Order the results from largest to smallest p (in order to have the smallest points on top of larger ones):
-variables = ['grid_num_', 'p_', 'a_', 'input_teff_', 'p_'+fit_option+'_', 'sigma_p_'+fit_option+'_', 
-                                'a_'+fit_option+'_', 'sigma_a_'+fit_option+'_', 'i_'+fit_option+'_', 'sigma_i_'+fit_option+'_']
-
-################################# PLOTTING ######################################################
-# Now plot. First, some options:
-pheight = 3#5
-pwidth = 4#6.5
-delta_x = 5.0#9
-delta_y = 1.0
-unit.set(xscale = 0.8)
-text.set(mode="latex")
-text.preamble(r"\usepackage{color}")
-text.preamble(r"\usepackage{wasysym}")
-legend_text_size = -3
-# More options on the legend:
[…]

### 2016-01-26 second_submission/coefficients_check_exp/plot_check.py

@@ -1,184 +1,0 @@
-from pyx import *
-import numpy as np
-import matplotlib.pyplot as plt
-
-def draw_arrow(g, x_coord_init, y_coord_init, x_coord_final, y_coord_final, size, line_color, stroke_color = None, fill_color = None):
-
-    if stroke_color is None:
-       stroke_color = line_color
-    if fill_color is None:
-       fill_color = line_color
-
-    x0,y0 = g.pos(x_coord_init , y_coord_init)
-    xf,yf = g.pos(x_coord_final, y_coord_final)
-    g.stroke(path.line(x0,y0,xf,yf),\
-         [style.linewidth.normal, style.linestyle.solid, line_color,
-          deco.earrow([deco.stroked([stroke_color]),
-                       deco.filled([fill_color])], size=0.1)])
-
-def draw_text(g, x_coord, y_coord, text_input, text_size = -2):
-    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
-    x0,y0 = g.pos(x_coord, y_coord)
-    g.text(x0,y0,text_input,textattrs)
-
-def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
-
-    x0,y0 = g.pos(x_coord_init , y_coord_init)
-    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
-
-    x = x0
-    y = y0
-    w = np.abs(x0-xf)
-    h = np.abs(y0-yf)
-
-    g.fill(path.rect(x,y,w,h), [band_color])
-
-def get_color(teff,i,half_val,m,n):
-    if teff[i] < half_val:
-        c_color = 2.0*(m*(teff[i])+n)
-        m_color = 1.-2.0*(m*(teff[i])+n)
-        y_color = 1.0
-        k_color = 0.
-    else:
-        c_color = 1.0
-        m_color = (m*(teff[i])+n) - 0.5
-        y_color = 2.0-2.0*(m*(teff[i])+n)
-        k_color = 0.
-
-    return color.cmyk(c_color,m_color,y_color,k_color)        
-
-teff,logg,mh,vturb,c1,c2 = np.loadtxt('all_atlas_lds_kepler.dat',unpack=True,usecols = (3,4,5,6,19,20))
-
-idx = np.where((teff<9000.))[0]
-mh = mh[idx]
-vturb = vturb[idx]
-logg = logg[idx]
-teff = teff[idx]
[…]

### 2016-01-26 second_submission/coefficients_check_exp/plot_check2.py

@@ -1,184 +1,0 @@
-from pyx import *
-import numpy as np
-import matplotlib.pyplot as plt
-
-def draw_arrow(g, x_coord_init, y_coord_init, x_coord_final, y_coord_final, size, line_color, stroke_color = None, fill_color = None):
-
-    if stroke_color is None:
-       stroke_color = line_color
-    if fill_color is None:
-       fill_color = line_color
-
-    x0,y0 = g.pos(x_coord_init , y_coord_init)
-    xf,yf = g.pos(x_coord_final, y_coord_final)
-    g.stroke(path.line(x0,y0,xf,yf),\
-         [style.linewidth.normal, style.linestyle.solid, line_color,
-          deco.earrow([deco.stroked([stroke_color]),
-                       deco.filled([fill_color])], size=0.1)])
-
-def draw_text(g, x_coord, y_coord, text_input, text_size = -2):
-    textattrs = [text.size(text_size),text.halign.center, text.vshift.middlezero]
-    x0,y0 = g.pos(x_coord, y_coord)
-    g.text(x0,y0,text_input,textattrs)
-
-def draw_rectangular_band(g, x_coord_init, y_coord_init, w, h, band_color):
-
-    x0,y0 = g.pos(x_coord_init , y_coord_init)
-    xf,yf = g.pos(x_coord_init+w, y_coord_init+h)
-
-    x = x0
-    y = y0
-    w = np.abs(x0-xf)
-    h = np.abs(y0-yf)
-
-    g.fill(path.rect(x,y,w,h), [band_color])
-
-def get_color(teff,i,half_val,m,n):
-    if teff[i] < half_val:
-        c_color = 2.0*(m*(teff[i])+n)
-        m_color = 1.-2.0*(m*(teff[i])+n)
-        y_color = 1.0
-        k_color = 0.
-    else:
-        c_color = 1.0
-        m_color = (m*(teff[i])+n) - 0.5
-        y_color = 2.0-2.0*(m*(teff[i])+n)
-        k_color = 0.
-
-    return color.cmyk(c_color,m_color,y_color,k_color)        
-
-teff,logg,mh,vturb,c1,c2 = np.loadtxt('all_atlas_lds_kepler.dat',unpack=True,usecols = (3,4,5,6,19,20))
-
-idx = np.where((teff<9000.))[0]
-mh = mh[idx]
-vturb = vturb[idx]
-logg = logg[idx]
-teff = teff[idx]
[…]

### 2016-01-26 second_submission/nasa_exoplanet_query/analyze_query.py

@@ -1,36 +1,0 @@
-import numpy as np
-
-data = np.genfromtxt('data.tab',usecols=(4,22,23,24),\
-                dtype=None,delimiter='\t')
-
-error_treshold = 0.01 # percent
-all_candidates = 0
-all_confirmed = 0
-candidate_count = 0
-confirmed_count = 0
-for i in range(len(data)):
-    status,depth,depth_err_up,depth_err_down = data[i]
-    if not np.isnan(depth) and not np.isnan(depth_err_up) and not np.isnan(depth_err_down):
-        # Get planet-to-star radius ratio as sqrt(depth):
-        p = np.sqrt(depth*1e-6)
-        # Estimate error on this via delta method:
-        perr = np.max([depth_err_up*1e-6,np.abs(depth_err_down*1e-6)])/(2.*np.sqrt(np.sqrt(depth*1e-6)))
-        # Get quoted precision:
-        precision = (perr/p)*100
-        if precision < error_treshold:
-                if status == 'CANDIDATE':
-                   candidate_count = candidate_count + 1
-                if status == 'CONFIRMED':
-                   confirmed_count = confirmed_count + 1
-        if status == 'CANDIDATE':
-                all_candidates = all_candidates + 1
-        if status == 'CONFIRMED':
-                all_confirmed = all_confirmed + 1
-print '\t Out of '+str(all_candidates)+' planet candidates:'
-print '\t > A total of '+str(candidate_count)+' have precision better than '+str(error_treshold)+'%.'
-print '\t Out of '+str(all_confirmed)+' confirmed exoplanets:'
-print '\t > A total of '+str(confirmed_count)+' have precision better than '+str(error_treshold)+'%.'
-
-#print depth
-#print depth_err_up
-#print len(depth)

### 2016-01-26 second_submission/sampling_simulation_log/sample.py

@@ -1,55 +1,0 @@
-import sys
-import numpy as np
-import matplotlib.pyplot as plt
-
-mu = np.array([1e-70,1-1e-70])#np.append(np.arange(step,1,step),1.)
-
-def check_kipping(A,B):
-        I = 1. - A*(1.-mu)-B*mu*(1.-np.log(mu))
-        dI = A+B*np.log(mu)
-        if len(np.where(I<=0)[0])>0:
-                return False
-        else:
-                if len(np.where(dI<=0)[0])>0:
-                        return False
-                else:
-                        return True
-
-def check_espinoza(l1,l2):
-        I = 1. - l1*(1.-mu)-l2*mu*np.log(mu)
-        dI = l1-l2*(1.+np.log(mu))
-        if len(np.where(I<=0)[0])>0: 
-                return False
-        else:
-                if len(np.where(dI<=0)[0])>0:
-                        return False
-                else:
-                        return True
-
-N = 10000
-lims = 0.1
-c1,c2 = np.random.uniform(0-lims,1+lims,N),np.random.uniform(0-lims,lims+1,N)
-
-final_c1 = []
-final_c2 = []
-for i in range(N):
-        if check_espinoza(c1[i],c2[i]):
-                final_c1.append(c1[i])
-                final_c2.append(c2[i])
-
-import matplotlib.pyplot as plt
-plt.xlabel('$l_1$')
-plt.ylabel('$l_2$')
-plt.style.use('ggplot')
-plt.plot([-lims,1+lims],[-lims,1+lims],'-',label='$l_1>l_2$')
-#plt.plot([-lims,lims],[-lims-2,lims-2],'-',label='$l_1-2<l_2$')
-plt.plot([1,1],[-lims,lims+1],'-',label='$l_1<1$')
-plt.plot([-lims,lims+1],[0,0],'-',label='$0<l_2$')
-plt.plot([-lims,lims+1],[0,0],'-',label='$l_2>1$')
-plt.plot(c1,c2,'r.',alpha=0.01)
-plt.plot(np.array(final_c1),np.array(final_c2),'b.')
-plt.legend()
-plt.show()
-
-
-        

### 2016-01-26 second_submission/sampling_simulation_log/sample_cute_plot.py

@@ -1,103 +1,0 @@
-from pyx import *
-import numpy as np
-import matplotlib.pyplot as plt
-
-mu = np.array([1e-70,1-1e-70])#np.append(np.arange(step,1,step),1.)
-
-def check_kipping(A,B):
-        I = 1. - A*(1.-mu)-B*mu*(1.-np.log(mu))
-        dI = A+B*np.log(mu)
-        if len(np.where(I<=0)[0])>0:
-                return False
-        else:
-                if len(np.where(dI<=0)[0])>0:
-                        return False
-                else:
-                        return True
-
-def check_espinoza(l1,l2):
-        if l1<1 and l2>0 and l1>l2:
-                return True
-        return False
-
-def check_espinoza2(l1,l2):
-        I = 1. - l1*(1.-mu)-l2*mu*np.log(mu)
-        dI = l1-l2*(1.+np.log(mu))
-        if len(np.where(I<=0)[0])>0: 
-                return False
-        else:
-                if len(np.where(dI<=0)[0])>0:
-                        return False
-                else:
-                        return True
-
-N = 1000000
-lims = 1
-c1,c2 = np.random.uniform(0-lims,1+lims,N),np.random.uniform(0-lims,lims+1,N)
-
-final_c1 = []
-final_c2 = []
-for i in range(N):
-        if check_espinoza(c1[i],c2[i]):
-                final_c1.append(c1[i])
-                final_c2.append(c2[i])
-
-print len(final_c1)
-print len(c1)
-print 100*(np.double(len(final_c1))/np.double(len(c1)))
-######## PLOTTING ###########
-# Now plot. First, some options:
-unit.set(xscale = 0.8)
-text.set(mode="latex")
-text.preamble(r"\usepackage{color}")
-text.preamble(r"\usepackage{wasysym}")
-legend_text_size = -2
-min_x = 0-lims
-max_x = 1+lims#0.55
-min_y= 0-lims
-max_y= 1+lims#0.75#1.05
-# More options on the legend:
-legend_pos = 'br'
-xaxis = r'$l_1$'
-yaxis = r'$l_2$'
-outname = 'triangular_sampling'
-
-c = canvas.canvas()
-g = c.insert(graph.graphxy(height=7,width=7, 
-        key=graph.key.key(pos=legend_pos,textattrs=[text.size(legend_text_size)]),\
-        x = graph.axis.linear(min=min_x,max=max_x,title = xaxis, 
[…]

### 2016-01-26 second_submission/which_law_to_use/analysis.py

@@ -1,142 +1,0 @@
-# -*- coding: utf-8 -*-
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-import numpy as np
-from pyx import text as pyx_text
-from pyx import trafo
-def text_pyx(g, x_coord, y_coord, text_input, text_size = -2, color = None, rotation = 0.):
-    """
-    Function that draws text in a given plot
-    INPUTS:
-        g       (Object) A graph-type object to which you want to add the text
-        x_coord     (Double) x-coordinate (in plot units) at which you want to place
-                the text
-        y_coord     (Double) y-coordinate (in plot units) at which you want to place
-                the text
-        text_input  (String) Text that you want to add.
-        text_size   (int, optional) Text size of the text added to the plot. Default is -2.
-        color       (instance) Color instance that defines the color that you want the 
-                text to have. Default is black.
-    """
-
-    # First define the text attributes:
-    textattrs = [pyx_text.size(text_size),pyx_text.halign.center, pyx_text.vshift.middlezero, trafo.rotate(rotation)]
-
-    # Now convert plot positions to pyx's:
-    x0,y0 = g.pos(x_coord, y_coord)
-
-    # If no color is given, draw black text. If color is given, draw text with the input color:
-    if color is None:
-        g.text(x0,y0,text_input,textattrs)
-    else:
-        # First, check which was the input color palette:
-        color_dict = color.color
-        if len(color_dict.keys()) == 4:
-            color_string = str(color_dict['c'])+','+str(color_dict['m'])+','+str(color_dict['y'])+','+str(color_dict['k'])
-            color_palette = 'cmyk'
-        else:
-                        color_string = str(color_dict['r'])+','+str(color_dict['g'])+','+str(color_dict['b'])
-                        color_palette = 'rgb'
-        # Now draw the text:
-        g.text(x0, y0, r"\textcolor["+color_palette+"]{"+color_string+"}{"+text_input+"}",textattrs)
-
-from pyx import *
-results = '/Users/nespinoza/github/ld-exosim/results/sic/'
-ld_laws = ['linear','quadratic','squareroot','logarithmic','three-param']
[…]

### 2016-01-26 second_submission/which_law_to_use/analysis_mse.py

@@ -1,143 +1,0 @@
-# -*- coding: utf-8 -*-
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-import numpy as np
-from pyx import text as pyx_text
-from pyx import trafo
-def text_pyx(g, x_coord, y_coord, text_input, text_size = -2, color = None, rotation = 0.):
-    """
-    Function that draws text in a given plot
-    INPUTS:
-        g       (Object) A graph-type object to which you want to add the text
-        x_coord     (Double) x-coordinate (in plot units) at which you want to place
-                the text
-        y_coord     (Double) y-coordinate (in plot units) at which you want to place
-                the text
-        text_input  (String) Text that you want to add.
-        text_size   (int, optional) Text size of the text added to the plot. Default is -2.
-        color       (instance) Color instance that defines the color that you want the 
-                text to have. Default is black.
-    """
-
-    # First define the text attributes:
-    textattrs = [pyx_text.size(text_size),pyx_text.halign.center, pyx_text.vshift.middlezero, trafo.rotate(rotation)]
-
-    # Now convert plot positions to pyx's:
-    x0,y0 = g.pos(x_coord, y_coord)
-
-    # If no color is given, draw black text. If color is given, draw text with the input color:
-    if color is None:
-        g.text(x0,y0,text_input,textattrs)
-    else:
-        # First, check which was the input color palette:
-        color_dict = color.color
-        if len(color_dict.keys()) == 4:
-            color_string = str(color_dict['c'])+','+str(color_dict['m'])+','+str(color_dict['y'])+','+str(color_dict['k'])
-            color_palette = 'cmyk'
-        else:
-                        color_string = str(color_dict['r'])+','+str(color_dict['g'])+','+str(color_dict['b'])
-                        color_palette = 'rgb'
-        # Now draw the text:
-        g.text(x0, y0, r"\textcolor["+color_palette+"]{"+color_string+"}{"+text_input+"}",textattrs)
-
-from pyx import *
-results = '/Users/nespinoza/github/ld-exosim/results/sic/'
[…]

### 2016-01-26 second_submission/which_law_to_use/bias_variance_plot.py

@@ -1,119 +1,0 @@
-# -*- coding: utf-8 -*-
-import matplotlib.pyplot as plt
-from scipy.interpolate import interp1d
-import numpy as np
-from pyx import text as pyx_text
-from pyx import trafo
-def text_pyx(g, x_coord, y_coord, text_input, text_size = -2, color = None, rotation = 0.):
-    """
-    Function that draws text in a given plot
-    INPUTS:
-        g       (Object) A graph-type object to which you want to add the text
-        x_coord     (Double) x-coordinate (in plot units) at which you want to place
-                the text
-        y_coord     (Double) y-coordinate (in plot units) at which you want to place
-                the text
-        text_input  (String) Text that you want to add.
-        text_size   (int, optional) Text size of the text added to the plot. Default is -2.
-        color       (instance) Color instance that defines the color that you want the 
-                text to have. Default is black.
-    """
-
-    # First define the text attributes:
-    textattrs = [pyx_text.size(text_size),pyx_text.halign.center, pyx_text.vshift.middlezero, trafo.rotate(rotation)]
-
-    # Now convert plot positions to pyx's:
-    x0,y0 = g.pos(x_coord, y_coord)
-
-    # If no color is given, draw black text. If color is given, draw text with the input color:
-    if color is None:
-        g.text(x0,y0,text_input,textattrs)
-    else:
-        # First, check which was the input color palette:
-        color_dict = color.color
-        if len(color_dict.keys()) == 4:
-            color_string = str(color_dict['c'])+','+str(color_dict['m'])+','+str(color_dict['y'])+','+str(color_dict['k'])
-            color_palette = 'cmyk'
-        else:
-                        color_string = str(color_dict['r'])+','+str(color_dict['g'])+','+str(color_dict['b'])
-                        color_palette = 'rgb'
-        # Now draw the text:
[…]
